### 2016-04-14 jpbs_template/tBPSguide.tex
Migrate Dropbox back to Github
Created to a repository that does not require the use of git-lfs

% tBPSguide.tex
% v2.1 released November 2014

\documentclass{tBPS2e}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

%\jvol{00} \jnum{00} \jyear{2014} \jmonth{November}

\articletype{GUIDE}

\title{\textit{Journal of Building Performance Simulation} \LaTeX\ guide for authors \break (Style 4 + Chicago author-date reference style)}

\author{
\name{A.N. Author\textsuperscript{a}$^{\ast}$\thanks{$^\ast$Corresponding author. Email: latex.helpdesk@tandf.co.uk}
and I.T. Consultant\textsuperscript{b}}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, UK;
\textsuperscript{b}Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
\received{v2.1 released November 2014}
}

\maketitle

\begin{abstract}
This guide is for authors who are preparing papers for the Taylor \& Francis journal \textit{Journal of Building Performance Simulation}
(\textit{tBPS}) using the \LaTeX\ document preparation system and the class file \texttt{tBPS2e.cls}, which is available via the journal's home page on the Taylor \& Francis website.
\end{abstract}

\begin{keywords}
submission instructions; source file coding; environments; references citation; fonts; numbering
\bf{(Please provide three to six keywords taken from terms used in your manuscript)}
\end{keywords}

{\abstractfont\centerline{\bfseries Index to information contained in this guide}\vspace{12pt}
\hbox to \textwidth{\hsize\textwidth\vbox{\hsize19pc
\hspace*{-12pt} {1.}    Introduction\\
\hspace*{7pt} {1.1.}  The \textit{tBPS} document class\\
\hspace*{7pt} {1.2.}  Submission of \LaTeX\ articles\\
\hspace*{24pt}        to the journal\\
{2.}    Using the \textit{tBPS} class file\\
{3.}    Additional features\\
\hspace*{10pt}{3.1.}  Title, authors' names, abstract \\
\hspace*{24pt}        and keywords\\
\hspace*{10pt}{3.2.}  Additional footnotes to the title \\
\hspace*{24pt}        or authors' names\\
\hspace*{10pt}{3.3.}  Lists\\
{4.}    Some guidelines for using standard\\
\hspace*{6pt}         features\\
\hspace*{10pt}{4.1.}   Sections\\
\hspace*{10pt}{4.2.}   Illustrations (figures)\\
\hspace*{10pt}{4.3.}   Tables\\
\hspace*{10pt}{4.4.}   Landscape pages\\
\hspace*{10pt}{4.5.}   Theorem-like environments\\
\noindent \hspace*{7pt} {4.6.}   Typesetting mathematics\\
\hspace*{24pt} {4.6.1.}   Displayed mathematics\\
\hspace*{24pt} {4.6.2.}   Bold math italic symbols\\
\hspace*{24pt} {4.6.3.}   Bold Greek\\
\hspace*{24pt} {4.6.4.}   Upright Greek characters  \\
\hspace*{50pt}            and the upright partial \\
\hspace*{50pt}            derivative sign  \\}
\hspace{-24pt}\vbox{\noindent\hsize19pc
\hspace*{7pt} {4.7.}   Acknowledgements \\
\hspace*{7pt} {4.8.}   Funding \\
\hspace*{7pt} {4.9.}   Notes \\
\hspace*{7pt} {4.10.}   Supplemental material \\
\hspace*{7pt} {4.11.}   References \\
\hspace*{24pt} {4.11.1.}  References cited in the \\
\hspace*{54pt}            text \\
\hspace*{24pt} {4.11.2.}   The list of references\\
\hspace*{7pt} {4.12.}   Appendices \\
{5.}    Example of a section heading \\*
\hspace*{7pt}   including \textsc{small caps}, \textit{italic}, \\*
\hspace*{7pt}   and bold Greek such as ${\bm\kappa}$ \\
{6.}   {\em tBPS} journal style \\
\hspace*{10pt}{6.1.}   Hyphens, en rules, em rules \\ \hspace*{27pt}and minus signs\\
\hspace*{10pt}{6.2.}   References \\
\hspace*{10pt}{6.3.}   Maths fonts\\
\noindent   {7.}   Troubleshooting\\
{8.}   Fixes for coding problems\\
{9.}   Obtaining the tBPS2e class file\\
\hspace*{10pt}{9.1}  Via the Taylor \& Francis \\
\hspace*{24pt}       website \\
\hspace*{10pt}{9.2}  Via e-mail\\ }}}

\section{Introduction}

In order to assist authors in the process of preparing a manuscript for the \textit{Journal of Building Performance Simulation} (\textit{tBPS}), the journal's layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class. A \textsc{Bib}\TeX\ style file is also provided to assist with the formatting of your references in a style appropriate to that of the journal.

Commands that differ from or are provided in addition to the standard \LaTeXe\ interface are explained in this guide. The guide alone is not intended as a substitute for an appropriate \LaTeXe\ manual.

The \texttt{tBPSguide.tex} file can also be used as a template for composing an article for submission by cutting, pasting, inserting and
deleting text as appropriate, using the \LaTeX\ environments provided (e.g. \verb"\begin{equation}", \verb"\begin{enumerate}").

\textbf{Please note that the index following the abstract in this guide is provided for information only. An index is not required in submitted papers.}

\subsection{The \textit{tBPS} document class}\label{class}

The \textit{tBPS} class file preserves the standard \LaTeXe\ interface such that any document that can
be produced using \texttt{article.cls} can also be produced using the \textit{tBPS} document class.
However, the measure (the width of the text on a page) differs from the default for \texttt{article.cls}, therefore line breaks
will change and some long equations may need to be reformatted accordingly.

If your article is accepted for publication in the journal, it will be typeset in Monotype Times. As most authors do not own this font, the page make-up would inevitably alter with the change of font. Moreover, the class file produces single-column format, which is preferred for peer review and will be converted to two-column format by the typesetter. This also reduces formatting problems during preparation of papers by authors due to long lines and equations spanning more than one column. Line endings would change anyway during preparation of proofs from two-column format manuscripts because typesetters' character sets differ slightly in size from those available on most PCs and laptops. Please therefore ignore details such as slightly long lines of text, page stretching, figures or tables not appearing in exact synchronization with their citations in the text: these details will be dealt with by the typesetter. Similarly, it is unnecessary to spend time addressing warnings in the log file -- if your .tex file compiles to produce a PDF document that correctly shows how you wish your paper to appear, such warnings will not prevent your source files being imported into the typesetter's program.

\subsection{Submission of \LaTeX\ articles to the journal}\label{submission}

Manuscripts for possible publication in the journal should be submitted to the Editors for review as directed in the journal's Instructions for Authors, which may be found at \texttt{http://www.tandf.co.uk/journals/authors/tbpsauth.asp}.

Manuscripts created using \LaTeX\ should be converted to PDF format prior to submission. The \LaTeX\ source files and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.

`Open-source' \LaTeXe\ should be used in preference to proprietary systems such as TCILaTeX or Scientific WorkPlace; similarly, class files such as REVTeX that produce a document in the style of a different publisher and journal should not be used for preference.

Please ensure that any author-defined macros are gathered together in the preamble of your .tex file, just before the
\verb"\begin{document}" command. Note that if serious problems are encountered with the coding of a paper (missing author-defined macros,
for example), it may prove necessary to divert the paper to conventional typesetting, i.e. it will be re-keyed.

\section{Using the \textit{tBPS} class file}

If the \texttt{tBPS2e} class file is not already in the appropriate system directory for \LaTeXe\ files, either
arrange for it to be put there, or copy it to your working folder. In order to use the \textit{tBPS} document class, replace the command
\verb"\documentclass{article}" at the beginning of your document with the command \verb"\documentclass{tBPS2e}".

The following document-class options should \emph{not} be used with the \textit{tBPS} class file:
\begin{itemize}
  \item \texttt{10pt}, \texttt{11pt}, \texttt{12pt} -- unavailable;
  \item \texttt{oneside}, \texttt{twoside} -- not necessary, oneside is the default;
  \item \texttt{leqno}, \texttt{titlepage} -- should not be used;
  \item \texttt{twocolumn} -- should not be used (see Section~\ref{class});
  \item \texttt{onecolumn} -- not necessary as it is the default style.
\end{itemize}
The \texttt{geometry} package and commands associated with it should also not be used to adjust the page dimensions.

\section{Additional features}

\subsection{Title, authors' names, abstract and keywords}

The title should be generated at the beginning of your article using the \verb"\maketitle" command.
In the final version, the author name(s) and affiliation(s) must be followed immediately by \verb"\maketitle" as shown below in order for them to be displayed in your PDF document.
To prepare an anonymous version for peer review, you can put the \verb"\maketitle" between the \verb"\title" and the \verb"\author" in order to conceal the authors' identities from the reviewers.
Next you should include an abstract, which should be enclosed within an \texttt{abstract} environment.
For example, the titles for this guide begin with the following source code:
\begin{verbatim}
\title{\textit{Journal of Building Performance Simulation} \LaTeX\
guide for authors (Style 4 + Chicago author-date reference style)}

\author{
\name{A.N. Author\textsuperscript{a}$^{\ast}$\thanks{$^\ast$Corresponding
author. Email: latex.helpdesk@tandf.co.uk}
and I.T. Consultant\textsuperscript{b}}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park,
Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik,
Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
\received{v2.1 released November 2014} }

\maketitle

\begin{abstract}
This guide is for authors who are preparing papers for \textit{Journal
of Building Performance Simulation} (\textit{tBPS}) using the \LaTeX\
document preparation system and the class file \texttt{tBPS2e.cls},
which is available via the journal's home page on the Taylor \&
Francis website.
\end{abstract}
\end{verbatim}
A list of keywords should follow the abstract as required by the journal, enclosed within a \texttt{keywords} environment.

\subsection{Additional footnotes to the title or authors' names}

The \verb"\thanks" command may be used to produce additional footnotes to the title or authors' names if required.
Footnote symbols for this purpose should be used in the order:
$\dagger$ (coded as \verb"\dagger"), $\ddagger$ (\verb"\ddagger"), $\S$ (\verb"\S"), $\P$ (\verb"\P"), $\|$ (\verb"\|"),
$\dagger\dagger$ (\verb"\dagger\dagger"), $\ddagger\ddagger$ (\verb"\ddagger\ddagger"), $\S\S$ (\verb"\S\S"),\break
$\P\P$ (\verb"\P\P"), $\|\|$ (\verb"\|\|").
Note that any \verb"footnote"s to the \emph{main text} will automatically be assigned the superscript
 symbols 1, 2, 3, etc. by the class file.\footnote{If preferred, the \texttt{endnotes} package
 may be used to set the notes at the end of your text, before the bibliography.
 The symbols will be changed to match the style of the journal if necessary by the typesetter.}

\subsection{Lists}

The \textit{tBPS} class file provides numbered and unnumbered lists using the \texttt{enumerate} environment and bulleted
lists using the \texttt{itemize} environment.

The enumerated list will number each list item with arabic numerals by default. For example,
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
\end{verbatim}
Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each \verb"\item", e.g. \verb"\item[(i)] first item" to create a list numbered with roman numerals.

Unnumbered lists can also be produced using the \texttt{enumerate} environment. For example,
\begin{enumerate}
  \item[] First unnumbered item
  \item[] Second unnumbered item
  \item[] Third unnumbered item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item[] First unnumbered item
  \item[] Second unnumbered item
  \item[] Third unnumbered item
\end{enumerate}
\end{verbatim}

Bulleted lists are provided using the \texttt{itemize} environment. For example,
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
was produced by
\begin{verbatim}
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
\end{verbatim}

\section{Some guidelines for using standard features}

The following notes are intended to help you achieve the best effects with the \texttt{tBPS2e} class file.

\subsection{Sections}

\LaTeXe\ provides five levels of section heading, all of which are defined in the \texttt{tBPS2e} class file:
\begin{enumerate}
  \item[(A)] \verb"\section"
  \item[(B)] \verb"\subsection"
  \item[(C)] \verb"\subsubsection"
  \item[(D)] \verb"\paragraph"
  \item[(E)] \verb"\subparagraph"
\end{enumerate}
Numbering is automatically generated for section, subsection, subsubsection and paragraph headings. If you need
additional text styles in the headings, see the examples given in Section~\ref{headings}.

\subsection{Illustrations (figures)}

See `Instructions for Authors' in the journal's home page on the Taylor \& Francis website for how to submit artwork (note that requests to supply figures and tables separately from text are for the benefit of authors using Microsoft Word; authors using \LaTeX\ may incorporate these at the appropriate locations). The source files of any illustrations will be required when the final, revised version is submitted. Authors should ensure that their figures are suitable (in terms of lettering size, etc.) for the reductions they intend.

The \textit{tBPS} class file will cope with most positioning of your illustrations and you should not normally need to use the optional placement specifiers of the \texttt{figure} environment.
Figure captions should appear below the figure itself, therefore the \verb"\caption" command should appear after the figure.
For example, Figure~\ref{sample-figure} with caption and sub-captions is produced using the following commands:
\begin{verbatim}
\begin{figure}
\begin{center}
\begin{minipage}{130mm}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{6cm}{!}{\includegraphics{senu_gr1.eps}}}\hspace{6pt}
\subfigure[A slightly shorter sub-caption.]{
\resizebox*{6cm}{!}{\includegraphics{senu_gr2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line.} \label{sample-figure}
\end{minipage}
\end{center}
\end{figure}
\end{verbatim}

\begin{figure}
\begin{center}
\begin{minipage}{130mm}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{6cm}{!}{\includegraphics{senu_gr1.eps}}}\hspace{6pt}
\subfigure[A slightly shorter sub-caption.]{
\resizebox*{6cm}{!}{\includegraphics{senu_gr2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line.} \label{sample-figure}
\end{minipage}
\end{center}
\end{figure}

The \verb"\subfigure{}" and \verb"\includegraphics{}" commands require subfigure.sty and graphicx.sty.
The former is called in the preamble of the \texttt{tBPSguide.tex} file (in order to allow your choice of an alternative package if preferred)
and the latter by the \texttt{tBPS2e} class file; both are included with the \LaTeX\ style guide package for this journal for convenience.
Please supply any additional figure macros you use with your article in the preamble of your .tex file before \verb"\begin{document}".

To ensure that figures are correctly numbered automatically, the \verb"\label{}" command should be inserted just
after the \verb"\caption{}" command, or in its argument.

The \texttt{epstopdf} package can be used to incorporate Encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc.
Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.

\subsection{Tables}

The \textit{tBPS} class file will cope with most positioning of your tables and you should not normally need to use the optional
placement specifiers of the \texttt{table} environment.

The \texttt{tabular} environment can be used as illustrated here to produce tables with appropriately spaced single thick and thin
horizontal rules, which are allowed, if desired. Thick rules should be used at the head and foot only, and thin rules elsewhere as appropriate.
Commands to redefine quantities such as \verb"\arraystretch" should be omitted.

The table caption appears above the body of the table in \textit{tBPS} style, therefore the \verb"\tbl" command should be used before the body of the table.
For example, Table~\ref{sample-table} is produced using the following commands. Note that \verb"\rm" will produce a roman character in math mode.
There are also \verb"\bf" and \verb"\it", which produce bold face and text italic in math mode.

\begin{table}
\tbl{Example of a table showing that its caption is as wide as the
  table itself and justified.}
{\begin{tabular}[l]{@{}lcccccc}\toprule
  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
         & $\langle \gamma \rangle$ & $G$ & $|{\bm f}|$ & $\theta _{c}$ \\
\colrule
  BL Lacs & 5 & 36 & 7 & $-4.0$ & $1.0\times 10^{-2}$ & 10$^\circ$ \\
  FSRQs & 5 & 40 & 11 & $-2.3$ & $0.5\times 10^{-2}$ & 14$^\circ$ \\
\botrule
\end{tabular}}
\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
\tabnote{$^{\rm b}$This footnote shows the text turning over when a long footnote is added.}
\label{sample-table}
\end{table}

\begin{verbatim}
\begin{table}
\tbl{Example of a table showing that its caption is as wide as the
 table itself and justified.}
{\begin{tabular}[l]{@{}lcccccc}\toprule
   Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
         & $\langle \gamma \rangle$ & $G$ & $|{\bm f}|$ & $\theta _{c}$ \\
\colrule
   BL Lacs & 5 & 36 & 7 & $-4.0$ & $1.0\times 10^{-2}$ & 10$^\circ$ \\
   FSRQs & 5 & 40 & 11 & $-2.3$ & $0.5\times 10^{-2}$ & 14$^\circ$ \\
\botrule
\end{tabular}}
\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
\tabnote{$^{\rm b}$This footnote shows the text turning over when
 a long footnote is added.}
\label{sample-table}
\end{table}
\end{verbatim}

To ensure that tables are correctly numbered automatically, the \verb"\label{}" command should be inserted just before \verb"\end{table}".
Tables produced using the \texttt{booktabs} package of macros for typesetting tables are also compatible with the \textit{tBPS} class file.

\subsection{Landscape pages}\label{landscape}

If a table or illustration is too wide to fit the measure it will need to be turned, along with its caption, through 90$^{\circ}$ anticlockwise.
Landscape illustrations and/or tables can be produced using the \verb"rotating" package, which is called by the \textit{tBPS} class file.
The following commands (for example) can be used to produce such pages.
\begin{verbatim}
\setcounter{figure}{0}
\begin{sidewaysfigure}
\centerline{\epsfbox{figname.eps}}
\caption{Example landscape figure caption.}
\label{landfig}
\end{sidewaysfigure}
\end{verbatim}

\begin{verbatim}
\setcounter{table}{0}
\begin{sidewaystable}
 \tbl{Example landscape table caption.}
  {\begin{tabular}{@{}llllcll}
    .
    .
    .
  \end{tabular}}\label{landtab}
\end{sidewaystable}
\end{verbatim}
Before any such float environment, use the \verb"\setcounter" command as above to fix the numbering of the caption. Subsequent captions will then be automatically renumbered accordingly.

The \verb"\epsfbox{}" command requires epsfig.sty, which is called by the \texttt{tBPS2e} class file and included with the \LaTeX\ style guide package for this journal for convenience.

\subsection{Theorem-like environments}

A predefined \verb"proof" environment is provided by the \texttt{amsthm} package (which is called by the class file), as follows:

\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\noindent This was produced by simply typing:
\begin{verbatim}
\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\end{verbatim}
Other theorem-like environments (theorem, lemma, corollary, etc.) need to be defined as required, e.g. using \verb"\newtheorem{theorem}{Theorem}[section]"
in the preamble of your .tex file before \verb"\begin{document}". Theorem-like structures in \textit{tBPS} are generally numbered as per the following examples:

\begin{theorem}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{theorem}
\begin{lemma}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{lemma}
\begin{corollary}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{corollary}
\begin{proposition}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proposition}
\begin{definition}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{definition}
\begin{remark}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{remark}

\noindent These were defined as shown in detail in the preamble of the \texttt{tBPSguide}.tex file, and produced by typing, for example:
\begin{verbatim}
\begin{theorem}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{theorem}
\end{verbatim}
The format of the text in these environments may be changed if necessary to match the style of the journal by the typesetter during preparation of your proofs.

\subsection{Typesetting mathematics}\label{TMth}

\subsubsection{Displayed mathematics}

The \textit{tBPS} class file will set displayed mathematics centred on the measure without equation numbers if the \LaTeX\ standard commands open (\verb"\[") and close (\verb"\]") square brackets are used as
delimiters. The equation
\[
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\]
\normalfont was typeset using the commands
\begin{verbatim}
\[
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\]
\end{verbatim}

For those of your equations that you wish to be automatically numbered sequentially throughout the text, use the \texttt{equation} environment, e.g.
\begin{equation}
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\end{equation}
was typeset using the commands
\begin{verbatim}
\begin{equation}
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})quad
  i\in {\mathbb R}
\end{equation}
\end{verbatim}

Part numbers for sets of equations may be generated using the \texttt{subequations} environment, e.g.
\begin{subequations} \label{subeqnexample}
\begin{equation}
        \varepsilon \rho w_{tt}(s,t)
        =
        N[w_{s}(s,t),w_{st}(s,t)]_{s},
        \label{subeqnpart}
\end{equation}
\begin{equation}
        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
\end{equation}
\end{subequations}
which was generated using the commands
\begin{verbatim}
\begin{subequations} \label{subeqnexample}
\begin{equation}
        \varepsilon \rho w_{tt}(s,t)
        =
        N[w_{s}(s,t),w_{st}(s,t)]_{s},
        \label{subeqnpart}
\end{equation}
\begin{equation}
        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
\end{equation}
\end{subequations}
\end{verbatim}
This is made possible by the \texttt{subeqn} package, which is called by the class file.
If you put the \verb"\label{}" just after the \verb"\begin{subequations}" line, references will be to the
collection of equations, `(\ref{subeqnexample})' in the example above.
Or, like the example code above, you can reference each equation individually -- e.g. `(\ref{subeqnpart})'.

Displayed mathematics should be given end-of-line punctuation appropriate to the running text sentence of which it forms a part, if required.

\subsubsection{Bold math italic symbols}

To get bold math italic you can use \verb"\bm", which works for all sizes, e.g.
\begin{verbatim}
\sffamily
\begin{equation}
   {\rm d}({\bm s_{t_{\bm u}}) = \langle{\bm\alpha({\sf{\textbf L}})}
   [RM({\bm X}_y + {\bm s}_t) - RM({\bm x}_y)]^2 \rangle
\end{equation}
\normalfont
\end{verbatim}
produces\sffamily
\begin{equation}
   {\rm d}({\bm s_{t_{\bm u}}}) = \langle {\bm\alpha({\sf{\textbf L}})}[RM({\bm X}_y
   + {\bm s}_t) - RM({\bm x}_y)]^2 \rangle
\end{equation}\normalfont
Note that subscript, superscript, subscript to subscript, etc.
sizes will take care of themselves and are italic, not bold,
unless coded individually. \verb"\bm" produces the same effect as
\verb"\boldmath". \verb"\sffamily"...\verb"\normalfont" allows
upright sans serif fonts to be created in math mode by using the
control sequence `\verb"\sf"'.

\subsubsection{Bold Greek}\label{boldgreek}

Bold lowercase as well as uppercase Greek characters can be
obtained by \verb"{\bm \gamma}", which gives ${\bm \gamma}$, and
\verb"{\bm \Gamma}", which gives ${\bm \Gamma}$.

\subsubsection{Upright lowercase Greek characters and the upright partial derivative sign}\label{upgreek}

Upright lowercase Greek characters can be obtained with the \textit{tBPS} class file by inserting the letter `u' in the control
code for the character, e.g. \verb"\umu" and \verb"\upi" produce $\umu$ (used, for example, in the symbol for the
unit microns -- $\umu{\rm m}$) and $\upi$ (the ratio of the circumference to the diameter of a circle). Similarly,
the control code for the upright partial derivative $\upartial$ is \verb"\upartial".

\subsection{Acknowledgements}

An unnumbered section, e.g. \verb"\section*{Acknowledgement(s)}", should be used for thanks, etc.
and placed \emph{in the non-anonymous version} before any Notes or References sections.

\subsection{Funding}

An unnumbered section, e.g. \verb"\section*{Funding}", should be used for grant details, etc.
and placed \emph{in the non-anonymous version} before any Notes or References sections.

\subsection{Notes}

An unnumbered Notes section may be placed before the References section. If using the \verb"endnotes" package, use the command \verb"\theendnotes" to create this section.

\subsection{Supplemental material}

Supplemental material should be referenced within your article where appropriate. An unnumbered section, e.g. \verb"\section*{Supplemental material}", detailing the supplemental material available should be placed immediately before the list of references, and should include a brief description of each supplemental file.

\subsection{References}\label{refs}

\subsubsection{References cited in the text}

References should be cited in the text in `Chicago author-date' style, separated by semi-colons, e.g. (Green 2002; Harlow 1983; Wegener and Petty 1994) or `...~see Smith (1985,~75)'. If there are two authors with the same surname, use the first initials with the surnames, e.g. (E.~Johnson 2001; L.~Johnson 1998). If there are three authors, list them all in every citation, e.g. (Kernis, Cornell, and Harlow 1993). For more than three authors, cite the first author's name followed by et al. For two or more sources by the same author(s) in the same year, use lower-case letters (a, b, c,...) with the year to order the entries in the Reference list and use these letters with the year in the in-text citations, e.g. (Green 1981a,b). Further details on this reference style can be found in the journal's Instructions for Authors.

Each bibliographical entry has a key, which is assigned by the author and used to refer to that entry in the text. In this document, the key \verb"ev94" in the citation form \verb"\citep{ev94}" produces `\citep{ev94}', and the keys in the citation \verb"\citep{Eri1984,GloRib51,PeaEtAl76}" produce `\citep{Eri1984,GloRib51,PeaEtAl76}'. The appropriate citation style for different situations can be obtained, for example, by \verb"\citet{hk97}" for `\citet{hk97}', \verb"\citet{Bar91,Mil93,Maz91}" for `\citet{Bar91,Mil93,Maz91}', or \verb"\citealt{Holl04}" for `\citealt{Holl04}'. Optional notes may be included at the beginning and end of a citation by the use of square brackets, e.g. \verb"\citep[see][123]{Agu95}" produces `\citep[see][123]{Agu95}'. Citation of the year alone may be produced by \verb"\citeyear{cwm73}", i.e. `\citeyear{cwm73}', or \verb"\citeyearpar{glov86}", i.e. `\citeyearpar{glov86}'.

\subsubsection{The list of references}

References should be listed at the end of the main text in alphabetical order, then chronologically (earliest first), with full page ranges (where appropriate) and issue numbers (for journals paginated by issue). If a reference has more than ten named authors, list only the first seven, followed by `et al.'. The following list shows some sample references prepared in the style of the journal.

\begin{thebibliography}{99}

\bibitem[Agutter(1995)]{Agu95}
Agutter, A.~J. 1995. ``The Linguistic Significance of Current {B}ritish
 Slang.'' Unpublished doctoral dissertation, Edinburgh University, UK.

\bibitem[Barlow(1991)]{Bar91}
Barlow, D.~H. 1991. ``Diagnoses, Dimensions, and {DSM-IV} [Special issue].''
 \emph{Journal of Abnormal Psychology} 100 (3).

\bibitem[Ericsson and Simon(1984)]{Eri1984}
Ericsson, K.~Anders, and Herbert~A. Simon. 1984. \emph{Protocol Analysis:
 Verbal Reports as Data}. Cambridge, MA: MIT Press.

\bibitem[Evans(1994)]{ev94}
Evans, W.~A. 1994. ``Approaches to Intelligent Information Retrieval.''
 \emph{Information Processing and Management} 7 (2): 147--168.

\bibitem[Glover(1986)]{glov86}
Glover, Fred. 1986. ``Hilbert Modular Forms and the {G}alois Representations
 Associated to {H}ilbert--{B}lumenthal Abelian Varieties.'' Ph.D. thesis,
 Harvard University, Cambridge, MA.

\bibitem[Glover, Smith, and Ribeiro(1951)]{GloRib51}
Glover, Fred, Raymond Smith, and C.~C. Ribeiro, eds. 1951. \emph{Lessons of the {B}ritish War
 Economy}. vol.~5. 2nd ed. Westport, CT: Greenwood Press.

\bibitem[Holland(2004)]{Holl04}
Holland, M. 2004. ``Guide to Citing Internet Sources.'' Accessed~November 4,
 2012.
 http://www.bournemouth.ac.uk/library/using/guide\_to\_citing\_internet\_sourc.html.

\bibitem[Kern(1997)]{hk97}
Kern, Hudson. 1997. ``The Resurgent {J}apanese Economy and a {J}apan--{U}nited
 {S}tates Free Trade Agreement.'' In \emph{4th International Conference on the
 Restructuring of the Economic and Political System in {J}apan and {E}urope},
 edited by C.~Lambert and G.~Holst. Milan, Italy, 21--25 May 1996. 147--156.
 Singapore: World Scientific.

\bibitem[Mazzeo(1991)]{Maz91}
Mazzeo, J. 1991. \emph{Comparability of Computer and Paper-and-Pencil Scores}
 (College Board Rep. No. 91). Princeton, NJ: Educational Testing Service.

\bibitem[Miller(1993)]{Mil93}
Miller, M.~E. 1993. \emph{The Interactive Tester (Version 4.0) [Computer
 software]}. Westminster, CA: Psytek Services.

\bibitem[Misner(1973)]{cwm73}
Misner, Charles~W. 1973. ``Efficient Algorithms for Layer Assignment
 Problems.'' In \emph{Gravitation in a Collapsing {U}niverse}, Vol.~5 of
 \emph{Einstein's Legacy}, edited by Ignatius Gottlob. 2nd ed. 63--83. San
 Francisco, CA: Freeman.

\bibitem[Pierce et~al.(1976)]{PeaEtAl76}
Pierce, Ian~F., Fred Glover, A.~T. Ogilvy, and A.~R.~S. Clements. 1976.
 ``A Model of Output, Employment, Wages and Prices in the {UK}.'' In
 \emph{Computing Tools for Modeling, Optimization and Simulation: Interfaces
 in Computer Science and Operations Research}, edited by Manuel Laguna and
 Jos\'{e}~Luis Gonz\'{a}les-Velarde. 2nd ed. 1--24. Boston, MA:
 Cambridge University Press.

\end{thebibliography}
\bigskip
\noindent This was produced by typing:
\begin{verbatim}
\begin{thebibliography}{99}

\bibitem[Agutter(1995)]{Agu95}
Agutter, A.~J. 1995. ``The Linguistic Significance of Current {B}ritish 
 Slang.'' Unpublished doctoral dissertation, Edinburgh University, UK.

\bibitem[Barlow(1991)]{Bar91}
Barlow, D.~H. 1991. ``Diagnoses, Dimensions, and {DSM-IV} [Special
 issue].'' \emph{Journal of Abnormal Psychology} 100 (3).

\bibitem[Ericsson and Simon(1984)]{Eri1984}
Ericsson, K.~Anders, and Herbert~A. Simon. 1984. \emph{Protocol
 Analysis: Verbal Reports as Data}. Cambridge, MA: MIT Press.

\bibitem[Evans(1994)]{ev94}
Evans, W.~A. 1994. ``Approaches to Intelligent Information Retrieval.''
 \emph{Information Processing and Management} 7 (2): 147--168.

\bibitem[Glover(1986)]{glov86}
Glover, Fred. 1986. \emph{Hilbert Modular Forms and the {G}alois 
 Representations Associated to {H}ilbert--{B}lumenthal Abelian 
 Varieties}. Ph.D. thesis, Harvard University, Cambridge, MA.

\bibitem[Glover, Smith, and Ribeiro(1951)]{GloRib51}
Glover, Fred, Raymond Smith, and C.~C. Ribeiro, eds. 1951.
 \emph{Lessons of the {B}ritish War Economy}. vol.~5. 2nd ed.
 Westport, CT: Greenwood Press.

\bibitem[Holland(2004)]{Holl04}
Holland, M. 2004. ``Guide to Citing Internet Sources.'' Accessed
 November 4, 2012.
 http://www.bournemouth.ac.uk/library/using/guide\_to\_citing\_internet\_sourc.html.

\bibitem[Kern(1997)]{hk97}
Kern, Hudson. 1997. ``The Resurgent {J}apanese Economy and a
 {J}apan--{U}nited {S}tates Free Trade Agreement.'' In \emph{4th
 International Conference on the Restructuring of the Economic and
 Political System in {J}apan and {E}urope}, edited by C.~Lambert
 and G.~Holst. Milan, Italy, 21--25 May 1996. 147--156. Singapore:
 World Scientific.

\bibitem[Mazzeo(1991)]{Maz91}
Mazzeo, J. 1991. \emph{Comparability of Computer and Paper-and-Pencil
 Scores} (College Board Rep. No. 91). Princeton, NJ: Educational
 Testing Service.

\bibitem[Miller(1993)]{Mil93}
Miller, M.~E. 1993. \emph{The Interactive Tester (Version 4.0)
 [Computer software]}. Westminster, CA: Psytek Services.

\bibitem[Misner(1973)]{cwm73}
Misner, Charles~W. 1973. ``Efficient Algorithms for Layer Assignment
 Problems.'' In \emph{Gravitation in a Collapsing {U}niverse},
 Vol.~5 of \emph{Einstein's Legacy}, edited by Ignatius Gottlob.
 2nd ed. 63--83. San Francisco, CA: Freeman.

\bibitem[Pierce et~al.(1976)]{PeaEtAl76}
Pierce, Ian~F., Fred Glover, A.~T. Ogilvy, and A.~R.~S. Clements. 1976.
 ``A Model of Output, Employment, Wages and Prices in the {UK}.''
 In \emph{Computing Tools for Modeling, Optimization and Simulation:
 Interfaces in Computer Science and Operations Research}, edited
 by Manuel Laguna and Jos\'{e}~Luis Gonz\'{a}les-Velarde. 2nd ed.
 1--24. Boston, MA: Cambridge University Press.

\end{thebibliography}
\end{verbatim}
\medskip
\noindent Each entry takes the form:
\begin{verbatim}
\bibitem[authors' names(date of publication)]{key}
Bibliography entry
\end{verbatim}
\noindent where `\texttt{authors' names}' is the list of names to appear where the \verb"bibitem" is cited in the text, and `\texttt{key}' is the tag that is to be used as an argument for the \verb"\cite{}" commands in the text of the article. \texttt{Bibliography entry} should be the material that is to appear in the list of references, suitably formatted.

Instead of typing the bibliography by hand, you may prefer to create the list of references using a \textsc{Bib}\TeX\ database. Include the lines
\begin{verbatim}
\bibliographystyle{tBPS}
\bibliography{tBPSguide}
\end{verbatim}
where the list of references should appear, where \texttt{tBPS.bst} is the name of the \textsc{Bib}\TeX\ style file for this journal and \texttt{tBPSguide.bib} is the database of bibliographic details for the references section included with the \textit{tBPS} \LaTeX\ style guide package (to be replaced with the name of your own \textsc{Bib}\TeX\ database). The \LaTeX\ source file of your paper will extract from your .bib file only those references that are cited in that paper and list them in the References section of it.

Please include a copy of your .bib file and/or the final generated .bbl file among your source files if your .tex file does not contain a reference list in a \texttt{thebibliography} environment.

\subsection{Appendices}\label{appendices}

Any appendices should be placed after the list of references, beginning with the
command \verb"\appendices" followed by the command \verb"\section" for each appendix title, e.g.
\begin{verbatim}
\appendices
\section{This is the title of the first appendix}
\section{This is the title of the second appendix}
\end{verbatim}
\noindent produces:\medskip

\noindent\textbf{Appendix A. This is the title of the first appendix}\vspace{12pt}

\noindent\textbf{Appendix B. This is the title of the second appendix}

\medskip
\noindent Subsections, equations, figures, tables, etc. within appendices will then be automatically numbered as appropriate.

\section{Example of a section heading including {\fontencoding{T1}\scshape{small caps}},
   {\bi italic}, and bold Greek such as ${\bm\kappa}$}\label{headings}

The following code shows how to achieve this section heading:
\begin{verbatim}
\section{Example of a section heading including
 {\fontencoding{T1}\scshape{small caps}}, {\bi italic},
 and bold Greek such as ${\bm\kappa}$}\label{headings}
\end{verbatim}

\section{\textit{tBPS} journal style}

The notes given here relate to common style errors found in manuscripts, but are \emph{not} intended to be exhaustive.

\subsection{Hyphens, en rules, em rules and minus signs}\label{dashes}

\begin{enumerate}
\item[(i)] Hyphens (one dash in \TeX/\LaTeX). \textit{tBPS} uses hyphens for compound adjectives (e.g.\ low-density gas, least-squares fit,
two-component model) but not for complex units or ranges, which could become cumbersome (e.g.\ 15~km~s$^{-1}$
feature, 100--200~$\umu$m observations).

\item[(ii)] en rules (two dashes in \TeX/\LaTeX). These are used (a) to denote a range (e.g.\ 1.6--2.2~$\umu$m);
(b) to denote the joining of two words of equal standing (e.g.\ Kolmogorov--Smirnov  test, Herbig--Haro object);
(c) with spaces, as an alternative to parentheses (e.g.\ `the results -- assuming no temperature gradient -- are indicative of \ldots').

\item[(iii)] The em rule (three dashes in \TeX/\LaTeX) has no specified use in \textit{tBPS}.

\item[(iv)] The minus sign is produced automatically in math mode by the use of a single dash, e.g.
\begin{equation}
y_{i} \in \{-1, 1 \} \quad \forall i \in V,
\end{equation}
\noindent where $|-V|=A^2+B^2.$\medskip

\noindent is produced by
\begin{verbatim}
\begin{equation}
y_{i} \in \{-1, 1 \} \quad \forall i \in V,
\end{equation}
\noindent where $|-V|=A^2+B^2.$
\end{verbatim}

\end{enumerate}

\subsection{References}

It is important to use the correct reference style, details of which can be found in Section~\ref{refs}.

\subsection{Maths fonts}

Scalar variables should be mediumface italic (e.g.\ $s$ for speed); vectors 
should be bold italic (e.g.\ $\bm v$ for velocity); matrices should be bold 
roman (upright) (e.g.\ $\bf A$), and tensors should be bold upright sans serif
(e.g.\ {\sffamily{\textbf L}}). Differential d, partial differential $\upartial$, 
complex i, exponential e, superscript T for `transpose', sin, cos, tan, log,
etc., should all be roman. Openface, or `blackboard', fonts can be used, for 
example, for the integers $\mathbb Z$ and the reals $\mathbb R$. 
Sub/superscripts that are physical variables should be italic, while those 
that are labels should be roman (e.g.\ $C_p$, $T_{\rm eff}$).

\section{Troubleshooting}

Authors may from time to time encounter problems with the preparation of a
paper in \LaTeX. The appropriate action to take will depend on the nature of
the problem -- the following is intended as a guide.

\begin{enumerate}
\item[(i)] If the problem is with \LaTeX\ itself, rather than with the
actual macros, please refer to an appropriate handbook for
initial advice. If the solution cannot be found, or if you
suspect that the problem lies with the macros, then please contact
Taylor \& Francis for assistance (\texttt{latex.helpdesk@tandf.co.uk}).

\item[(ii)] Problems with page make-up (e.g.\ large spaces between paragraphs,
above headings, or below figures; figures/tables appearing out of order):
please do not attempt to remedy these using `hard' page make-up
commands -- the typesetter will deal with such problems. (You may, if you
wish, draw attention to particular problems when submitting the final version
of your paper.)

\item[(iii)] If a required font is not available at your site, allow \TeX\
to substitute the font and specify which font you require in a
covering letter accompanying your file(s).
\end{enumerate}

\section{Fixes for coding problems}

This guide has been designed to minimize the need for user-defined macros to create special symbols. Authors
are urged, wherever possible, to use the following coding rather than to create their own. This will minimize
the danger of author-defined macros being accidentally `overridden' when the paper is typeset (see
Section~\ref{TMth}, `Typesetting mathematics'). In cases where it is essential to create your own macros,
these should be displayed in the preamble of the source file before \verb"\begin{document}".
%
\begin{enumerate}
\item[(i)] Fonts in section headings and paper titles. The following are examples
of styles that sometimes prove difficult to code.

\subsection*{Paper titles:}

\hsize380pt\bf{\noindent Generalized Flory theory at ${\bm\delta >
{\bf 50}^\circ}$}\\

    \noindent\normalfont is produced by
\begin{verbatim}
\title{Generalized Flory theory at
        ${\bm\delta > {\bfseries 50}^\circ}$}
\end{verbatim}
\bigskip

{\bf{\noindent Ion--ion correlations in H\,{\sc ii} regions}}\\

\noindent\normalfont is produced by
\begin{verbatim}
\title{Ion--ion correlations in H\,{\sc ii} regions}
\end{verbatim}

\stepcounter{enumi}

\item[(ii)] en rules, em rules, hyphens and minus signs (see Section~\ref{dashes} for
correct usage). To create the correct symbols in the sentence
\begin{quote}
The high-resolution observations were made along a line at an
angle of $-15^\circ$ (East from North) from the axis of the
jet -- which runs North--South
\end{quote}
you would use the following code:
\begin{verbatim}
The high-resolution observations were made along a line at an
angle of $-15^\circ$ (East from North) from the axis of the
jet -- which runs North--South
\end{verbatim}

\item[(iii)] Fonts in superscripts and subscripts. Subscripts and superscripts will automatically come out in the correct font
and size in a math environment (e.g.\ enclosed by `\verb"$"'
delimiters in running text or within \verb"\[...\]" or the
`\texttt{equation}' environment for displayed equations). You can create
the output ${\bm k_x}$ by typing \verb"${\bm k_x}$". If the
subscripts or superscripts need to be other than italic, they
should be coded individually -- see (vi) below.

\item[(iv)] Calligraphic letters ($\mathcal{UPPER\ CASE\ ONLY}$).
Normal calligraphic can be produced with \verb"\mathcal" as usual (in
math mode).

\item[(v)] Automatic scaling of brackets. The codes \verb"\left" and
\verb"\right" should  be used to scale brackets automatically to
fit the equation being set. For example, to get
\[
   v = x \left( \frac{N+2}{N} \right)
\]
use the code
\begin{verbatim}
\[
   v = x \left( \frac{N+2}{N} \right)
\]
\end{verbatim}

\item[(vi)] Roman font in equations. It is often necessary to make some
symbols roman in an equation (e.g.\ units, non-variable
subscripts). For example, to get
\[
   \sigma \simeq (r/13~h^{-1}~{\rm Mpc})^{-0.9},
   \qquad \omega = \frac{N-N_{\rm s}}{N_{\rm R}}
\]
\noindent use the code
\begin{verbatim}
\[
   \sigma \simeq (r/13~h^{-1}
   ~{\rm Mpc})^{-0.9}, \qquad \omega
   =\frac{N-N_{{\rm s}}}{N_{{\rm R}}}
\]
\end{verbatim}
The \texttt{siunits} package of macros for typesetting units is also compatible with the \textit{tBPS} class file.
\end{enumerate}

\section{Obtaining the tBPS2e class file}\label{FTP}

\subsection{Via the Taylor \& Francis website}

This Guide for Authors and the \verb"tBPS2e" class file may be obtained via the Instructions for Authors
on the Taylor \& Francis homepage for the journal.

Please note that the class file calls up the following open-source \LaTeX\ packages, which will, for convenience,
unpack with the downloaded Guide for Authors and class file: amsbsy.sty; amsfonts.sty; amsmath.sty; amssymb.sty; epsfig.sty; graphicx.sty; natbib.sty; rotating.sty. 
The Guide for Authors calls for subfigure.sty, which is also supplied for convenience.

\subsection{Via e-mail}

This Guide for Authors, the class file and the associated open-source \LaTeX\ packages are also available by
e-mail. Requests should be addressed to \texttt{latex.helpdesk@tandf.co.uk} clearly stating for which journal you
require the Guide for Authors and/or class file.

\end{document}

### 2016-04-14 latex/UMEM_CoSim.tex
Migrate Dropbox back to Github
Created to a repository that does not require the use of git-lfs

% tBPSguide.tex
% v2.1 released November 2014

\documentclass{tBPS2e}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
\usepackage{lmodern}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{float}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\begin{document}

%\jvol{00} \jnum{00} \jyear{2014} \jmonth{November}

\articletype{Research Article}

\title{\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}}

\author{Clayton Miller\textsuperscript{a}%
$^{\ast}$\thanks{$^\ast$Corresponding author. Email: miller.clayton@arch.ethz.ch}, 
Daren Thomas\textsuperscript{a},
J\'er\^ome K\"ampf\textsuperscript{b},
and Arno Schlueter\textsuperscript{a}\\
\vspace{6pt}
\textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
\textsuperscript{b}{\em Solar Energy and Building Physics Laboratory (LESO-PB), Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland}
\received{v0.1 released January 2015}
}

\maketitle

\begin{abstract}
This paper describes the co-simulation process of the building and urban scale models of two campuses of higher education buildings in Switzerland. The campuses are modeled at both the building scale using the EnergyPlus simulation engine and at the urban scale using the CitySim engine. A co-simulation framework is used to execute simulations from both engines concurrently with an exchange of information to leverage the various strengths of each. In the first case study, on-site weather and measured performance data is then compared to the output from two modeling scenarios: building-scale simulation using EnergyPlus and co-simulation of the engines. A partial calibration process is implemented to reconcile the simulations with the measured data a targeted office building on campus. In the second case study, the co-simulation results are compared to the both the CitySim simulation and EnergyPlus engines. The results show that {\color{red}insert results here}. A discussion is included of the challenges encountered with the urban scale calibration and the strengths and weaknesses of the developed process.
\end{abstract}

%Taken out of the abstract: A significant amount of model input information was extracted for the creation of both models from a building information model (BIM) of the campus.

\begin{keywords}
Building-scale simulation, Calibrated energy models, CitySim, Co-simulation, EnergyPlus, Urban-scale simulation 
\end{keywords}

% {\abstractfont\centerline{\bfseries Index to information contained in this guide}\vspace{12pt}
% \hbox to \textwidth{\hsize\textwidth\vbox{\hsize19pc
% \hspace*{-12pt} {1.}    Introduction\\
% \hspace*{7pt} {1.1.}  The \textit{tBPS} document class\\
% \hspace*{7pt} {1.2.}  Submission of \LaTeX\ articles\\
% \hspace*{24pt}        to the journal\\
% {2.}    Using the \textit{tBPS} class file\\
% {3.}    Additional features\\
% \hspace*{10pt}{3.1.}  Title, authors' names, abstract \\
% \hspace*{24pt}        and keywords\\
% \hspace*{10pt}{3.2.}  Additional footnotes to the title \\
% \hspace*{24pt}        or authors' names\\
% \hspace*{10pt}{3.3.}  Lists\\
% {4.}    Some guidelines for using standard\\
% \hspace*{6pt}         features\\
% \hspace*{10pt}{4.1.}   Sections\\
% \hspace*{10pt}{4.2.}   Illustrations (figures)\\
% \hspace*{10pt}{4.3.}   Tables\\
% \hspace*{10pt}{4.4.}   Landscape pages\\
% \hspace*{10pt}{4.5.}   Theorem-like environments\\
% \noindent \hspace*{7pt} {4.6.}   Typesetting mathematics\\
% \hspace*{24pt} {4.6.1.}   Displayed mathematics\\
% \hspace*{24pt} {4.6.2.}   Bold math italic symbols\\
% \hspace*{24pt} {4.6.3.}   Bold Greek\\
% \hspace*{24pt} {4.6.4.}   Upright Greek characters  \\
% \hspace*{50pt}            and the upright partial \\
% \hspace*{50pt}            derivative sign  \\}
% \hspace{-24pt}\vbox{\noindent\hsize19pc
% \hspace*{7pt} {4.7.}   Acknowledgements \\
% \hspace*{7pt} {4.8.}   Funding \\
% \hspace*{7pt} {4.9.}   Notes \\
% \hspace*{7pt} {4.10.}   Supplemental material \\
% \hspace*{7pt} {4.11.}   References \\
% \hspace*{24pt} {4.11.1.}  References cited in the \\
% \hspace*{54pt}            text \\
% \hspace*{24pt} {4.11.2.}   The list of references\\
% \hspace*{7pt} {4.12.}   Appendices \\
% {5.}    Example of a section heading \\*
% \hspace*{7pt}   including \textsc{small caps}, \textit{italic}, \\*
% \hspace*{7pt}   and bold Greek such as ${\bm\kappa}$ \\
% {6.}   {\em tBPS} journal style \\
% \hspace*{10pt}{6.1.}   Hyphens, en rules, em rules \\ \hspace*{27pt}and minus signs\\
% \hspace*{10pt}{6.2.}   References \\
% \hspace*{10pt}{6.3.}   Maths fonts\\
% \noindent   {7.}   Troubleshooting\\
% {8.}   Fixes for coding problems\\
% {9.}   Obtaining the tBPS2e class file\\
% \hspace*{10pt}{9.1}  Via the Taylor \& Francis \\
% \hspace*{24pt}       website \\
% \hspace*{10pt}{9.2}  Via e-mail\\ }}}

\section{Introduction}

Urban scale building performance simulation is a process that empowers the analysis and optimization of cities. Urban populations are growing around the world at an unprecedented rate. A shift from urban to rural is underway and 2.5 billion people are expected to join urban centers throughout the world \citep{UnitedNations:2014vn}. Expansions of entire districts and even cities is not an uncommon phenomenon, especially in East Asia and Africa. Urban scale modeling is in the midst of a strong focus within the research community with six key areas of practice: technology design, building design, urban climate, systems design, policy assessment, and land use and transportation \citep{Keirstead:2012ct}. The ability to simulate the interaction between large collections of buildings enables the development and testing of optimization and planning scenarios for this new development \citep{Dorer:2013vt}.

The CitySim simulation engine is an example of such a program designed and optimized for urban-scale simulation. CitySim is an urban performance simulation engine that comprises a Solver module as well as a graphical user interface. It focuses on the energy flows of multiple simplified building models and their interdependent relationship with their urban climate \citep{Robinson:2009tm}. CitySim includes building thermal, urban radiation, occupant behavior, and plant/equipment models integrated as a single simulation engine. CitySim simulates multiple buildings up to city scale using simplified models in order to achieve a good compromise between modeling accuracy, computational overheads and data availability. Each building's thermal behavior is based on an electrical analogy using a two node resistor-capacitor network. The internal lighting, people, and miscellaneous loads are modeled using a simplified occupancy-based approximation. The heating, ventilation, and air-conditioning (HVAC) systems are modeled using a single equation that approximates the total mass flow rate required to meet the sensible and latent loads of each building as a whole. Each of these simplifying approximations empowers the urban-scale simulation to have reasonable execution times with respect to the number of buildings being simulated.

Building performance simulation is a mature domain of research relative to urban scale efforts. The use of whole building simulation engines originated in the 1960s with the US government's development of the BLAST and DOE-2 hourly energy simulation programs \citep{Lawrie:2001vf}. In 1996, development on a new simulation engine, EnergyPlus, began in order to combine the advantages of previous efforts in a single, modular program. EnergyPlus, as a result, has become a popular choice in detailed whole-building performance simulation due to the breadth of mechanical, renewable, and electrical systems that can be modeled. EnergyPlus specifically excels in its ability to model unique mechanical system types such as decoupled centralized cooling \citep{Miller:2010wa} and low exergy heating and cooling systems \citep{barbara:2015tz}. Additionally, EnergyPlus is designed to provide a high resolution in which internal loads and natural ventilation technologies can be modeled in detail at the building level.

Both building and urban-scale simulation domains have rightfully chosen boundary conditions that reflect their key goals while seeking to minimize the input parameters necessary and run-times of the engines themselves. This focus results in certain deficiencies with respect to modeling various phenomenon. For example, urban scale simulation highly simplifies the building systems and internal load models, thus making retrofit analysis at the systems level difficult. And whole building simulation neglects many of the various contextual consideration of the urban environment such as long wave radiation exchange with adjacent surfaces and localized urban weather effects.

In order to address the deficiencies of the individual engines, the current effort described seeks to couple building and urban scale simulation. The research in this paper is part of an larger coupling effort in which various engines are connected and co-simulated to create a more comprehensive analysis of the urban scale \citep{Dorer:2013vt}. The target is the computational interface between the building energy model, using EnergyPlus, and the urban energy model using CitySim. An overview of the larger scope is shown in Figure \ref{fig:UMEM} and the context of the coupling task is shown as the interface between the City Energy Simulation (CES) model and the Building Energy Simulation (BES) model.

The coupling and co-simulation process is implemented on two case studies in Switzerland. The first case study is the ETH Z\"urich Hoenggerberg campus in Z\"urich, Switzerland. The campus was modeled in the CitySim simulation engine and co-simulated using work-flow automation. The target of this case study is to evaluate the differences between the coupled and uncoupled EnergyPlus simulation results with a target on the use of these models for building retrofit analysis. This scenario includes the use of measured data for heating and cooling within their respective seasons to compare to the simulation results. The second case study is the EPFL campus in Lausanne, Switzerland. The objective of this scenario is to evaluate the differences between coupled and uncoupled versions of the CitySim simulation engine.

\begin{figure}
\centering
\includegraphics[scale=0.7]{figures/UMEM_overview_new}
\caption{EnergyPlus and CitySim coupling are part of the wider context. Each block in the diagram represents an environment, with the tool/engine name in italics (adapted from \citep{Dorer:2013vt})}
\label{fig:UMEM}
\end{figure}

This paper describes the achievement of several objectives:
\begin{enumerate}
  \item Automation of the process of simultaneous meta-data extraction from a building information model (BIM) for the creation of both building and urban-scale performance models for a real-world campus of buildings
  \item Co-simulate the urban and building scale models through concurrent information exchange
  \item Implement a simplified calibration procedure based on reconciling the co-simulation output results for a selected subset of buildings that have adequate measured energy performance data from the campus energy information system (EIS) 
\end{enumerate}

The first two objectives have been demonstrated in a simplified context in previous literature \citep{thomas2014multiscale,Miller:2015vk}. The novelty of the current publication is an extension to this research through the modelling and co-simulation of real-world case studies. The third objective is completely novel in that no previous study has compared the results of a building and urban-scale co-simulation procedure to measured data from a real-world campus.

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between simulation engines at various scales. EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi}. EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program
\citep{Yang:2012cr}.
% \subsection{Urban scale performance simulation}

\section{Methodology}\label{Methodology}
% A significant amount of the following methodology is developed in previous literature and is reiterated in this section in order to set the context for Section \ref{Implementation}. The previous published research is clearly outlined at the beginning of each subsection.

\subsection{Coupling process}
The coupling process of a simplified single zone model and contextual surrounding buildings is outlined previously \citep{thomas2014multiscale}. This effort is based on the utilization of the Design Performance Viewer (DPV) and associated work flow. The DPV is a tool written to extract and simulate an EnergyPlus input data file (IDF) from an Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM \citep{Schlueter2009}. The main philosophy behind the tool is rapid simulation of the building information model from the earliest design possible and can be used throughout the life-cycle of the building including retrofit analysis \citep{Miller:2014tu}. This process is achieved by augmenting the information in the BIM with default values and abstracting information not relevant for energy simulation. The tool already has a simplified notion of surrounding buildings, which are modeled in the BIM as simple mass objects without further information and are exported as shading surfaces to EnergyPlus. This functionality is used for creating the CitySim mass scene and leads to a crude model of the urban context of the building. The existing DPV philosophy of allowing the designer to iterate rapidly on early design decisions based on feedback about the performance of the design remains. This approach includes streamlining the process where running a simulation requires no effort from the designer due to automatic creation of input files, execution and analysis of the results.

The coupling process of EnergyPlus and CitySim is shown in Figure \ref{fig:OverallWorkflowProcess}. First, the DPV is used to extract an EnergyPlus simulation model from the BIM. The DPV utilizes the Revit API to extract geometrical information about the building and the physical properties of walls, windows, doors, roofs and floors. This information is encoded in the BIM model as wall types, roof types,
floor types as well as window and door families. Wherever possible, the tool uses the layering and materials of the construction types, enhancing them with physical attributes relevant to EnergyPlus. Where not defined, it assumes default values.

\begin{figure}[H]
\centering
\includegraphics[scale=0.7]{figures/UMEM_Workflow}
\caption{Overview diagram of the coupling process including tools and outputs}
\label{fig:OverallWorkflowProcess}
\end{figure}

Next, geometry is created to be used in both the CitySim and EnergyPlus models as buildings and surfaces surrounding the building targeted in the IDF. This feature of the DPV is used for including shading surfaces in the EnergyPlus simulation model: it uses so-called \emph{mass objects} in the BIM model as surrounding buildings. The DPV model views these buildings as a series of shading surfaces. A transformation is added on the DPV model that produces an input file for the CitySim solver. This file uses an XML format describing the buildings in a scene for simulation, including their construction types, geometry and systems for heating and cooling. The main BIM is extracted to the CitySim scene as one of the buildings to be simulated, with the properties of the construction types matching those in the DPV model. The glazing ratio is calculated based on the window and wall areas of the DPV model. Shading surfaces are grouped into buildings based on the mass object they were extracted from. These neighboring buildings use default construction properties for walls and roofs and we assign them a default glazing ratio. These defaults can be overridden by custom properties applied to the mass objects in the BIM much in the same way as the model elements of the main building are enriched with DPV information.

As of version 8.1.0, EnergyPlus supports exporting a simulation model as a Functional Mock-up Unit (FMU) \citep{Nouidui:2014hq}. This feature introduces new IDF objects to specify the interface such an FMU exposes. These objects define which output variables are exported by the FMU and which variables are imported. The FMU export functionality is closely linked to the Energy Management System (EMS) of EnergyPlus. Co-simulation exchange variables either mimic an EnergyPlus schedule, an EMS variable or drive an EMS actuator. It was determined that in order to export an output variable using the FMU export functionality, the variable itself must also be output with an IDF object of type \emph{Output:Variable} or \emph{EnergyManagementSystem:OutputVariable} in the IDF file as well. Since the model used by CitySim to simulate a building is more abstract than the model used by EnergyPlus, the EMS is used to aggregate certain values. CitySim does not model windows separately, therefore a weighted average of window and wall surface temperatures is calculated with EMS subroutines.

\begin{figure}[H]
\centering
\includegraphics[scale=0.7]{figures/UMEM_FMU_Overview}
\caption{Simulation information exchange between CitySim and EnergyPlus using FMI (adapted from \cite{thomas2014multiscale})}
\label{fig:FMUOverview}
\end{figure}

% The process of augmenting the IDF file is automated with the EMS subroutines and FMU export objects. The script \emph{addfmutoidf.py}, written in the Python programming language, uses the \emph{parseidf} module to read in the IDF file and add the new IDF objects based on those found in the model.  This script reads in the list of surfaces defined in the IDF file and produces EMS scripts to aggregate and output the surface temperatures of the wall and the windows as well as any other output objects necessary.

The FMU creation process is the basis for coupling the two models at each timestep in the simulation. Figure \ref{fig:FMUOverview} illustrates this process from both the EnergyPlus and CitySim perspective. The augmented IDF file is fed to the \emph{EnergyPlusToFMI} script \citep{Nouidui:2014bo}. Once configured, this script produces an FMU file based on the augmented IDF file and the weather file to be used as well as a DLL file implementing the Functional Mock-up Interface that can load the IDF file, locate EnergyPlus and run the simulation. Table \ref{FMUimports} and \ref{FMUexports} outline the variables exchanged between EnergyPlus and CitySim through the FMI.

% We used the \emph{fmilib} library from the JModelica project to test the FMU produced \citep{Anonymous:ZZTfF80-}. We altered one of the sample programs (\emph{fmi\_import\_cs\_test.c}) to load the FMU, run it and print out the values exported from EnergyPlus. This code was then used as a guide to extending the CitySim solver to load FMUs for co-simulation.

\subsection{Coupled variables}

On an hourly basis, CitySim performs a heating and cooling needs prediction step. The temperature determination step for the main building is replaced with the results of the EnergyPlus timestep as obtained through FMI library. The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus (see Table \ref{FMUimports}), and to receive data from EnergyPlus that are further used within CitySim for the next time steps (see Table \ref{FMUimports}).

\begin{table}[H]
\tbl{Values imported by EnergyPlus from CitySim by the FMU}
{\begin{tabular}[l]{@{}lcc}\toprule
  \bf{Object (ep\_id)} &  \bf{Variable Name} & \bf{Description} \\
\colrule
  Outdoor & Outdoor Drybulb & The outdoor dry-bulb temperature in $^{\circ}\mathrm{C}$ \\
 & Outdoor Dewpoint & The outdoor dewpoint temperature in $^{\circ}\mathrm{C}$ \\
 & Outdoor Relative Humidity & The outdoor relative humidity expressed in percent. \\
 & Diffuse Solar & Diffuse horizontal irradiance in W/m$^2$ \\
 & Direct Solar & Beam normal irradiance in W/m$^2$ \\
 & Wind Speed & The outdoor wind speed in m/s \\
 & Wind Direction & The wind direction in degrees\\&&  (N=0, E=90, S=180, W=270) \\
 \hline
 Long Wave Radiation & Environmental Radiant Temp. & Calculated $T_{env}$ from the sky,\\&& ground, and surrounding surfaces \\
 & Environmental Radiant Heat & Calculated $h_{env}$ from the sky,\\&& ground, and surrounding surfaces \\
 & Gain Coefficient \\
 \hline
Zone & Occupation & Fraction of the maximum occupation\\&& (0.0-1.0) overrides the EnergyPlus occupation schedule\\&&  with the CitySim stochastic schedule. \\
\botrule
\end{tabular}}
\label{FMUimports}
\end{table}

\begin{table}[H]
\tbl{Values exported by EnergyPlus to CitySim by the FMU}
{\begin{tabular}[l]{@{}lcc}\toprule
  \bf{Object (ep\_id)} &  \bf{Variable Name} & \bf{Description} \\
\colrule
Wall, Roof & Outside Surface Temperature & The temperature on the outside of the surface in $^{\circ}\mathrm{C}$ \\    
    \hline
Wall & Average Outside Surface Temperature & The (weighted) average temperature of \\
& & the surface on the outside in $^{\circ}\mathrm{C}$. \\
    \hline
Zone & Total Heating Energy & The heating energy in Joules used in this timestep. \\
& Total Cooling Energy & The cooling energy in Joules used in this timestep. \\
& Zone Mean Air Temperature & The mean air temperature in the zone in $^{\circ}\mathrm{C}$ \\
& Ventilation Volume Flow Rate & The flow rate in $\mathrm{m}^3/\mathrm{s}$ (standard density) \\
\botrule
\end{tabular}}
\label{FMUexports}
\end{table}

\subsection{Long wave radiation exchange}

Long wave radiation exchange in the urban scale environment is also coupled in the co-simulation process. However, it requires the development of a set of approximations to reduce the number of coupled variables between the engines and to account for differences in the methods by which each engine calculates this metric. A detailed description of Long Wave Radiation (LWR) variable exchange and approximation is found in a previously published study \citep{Miller:2015vk} on a simplified theoretical case.

In EnergyPlus, LWR exchange for a surface is calculated through the summation of radiation gain from the ground, sky, and air as seen in Equation \ref{EPlus_LWR_Ext} and Figure \ref{combinedLWR}a \citep{doe2010energyplus}. The radiant heat transfer coefficient for each of these environmental variables is calculated according to Equation \ref{EPlus_h} with $\sigma$ as the Stefan-Boltzmann constant and $\epsilon$ as the emissivity. A major assumption of this approach is that the modeled building's surfaces and those of adjacent buildings are at a uniform temperature and the LWR radiation exchange is negligible; a situation that is an oversimplification in an urban
scale domain \citep{Evins:2014cf}.
\begin{equation} \label{EPlus_LWR_Ext} 
Q_{LWR,EnergyPlus} = h_{r,grd}(T_{surf}-T_{grd}) + h_{r,sky}(T_{surf}-T_{sky}) + h_{r,air}(T_{surf}-T_{air})
\end{equation}
\begin{equation} \label{EPlus_h} 
h_{r,variable} = \frac{\epsilon\sigma(T^{4}_{surf}-T^{4}_{variable})}{T_{surf}-T_{variable}}
\end{equation}

In comparison, CitySim calculates LWR exchange by calculating an aggregated equivalent temperature, $T_{env}$, and radiative heat transfer coefficient, $h_{r,env}$, from surrounding urban surfaces in addition to ground, sky, and air \citep{Robinson:2009tm}. The calculation for $T_{env}$ is expressed in Equation \ref{CitySim_Tenv} with the $F$ values being view factors of the surrounding environment including adjacent surfaces $i=1..n$. $h_{r,env}$ is based on a first order Talyor development of the numerator of Equation \ref{EPlus_h} around $(T_{surf}+T_{variable})/2$ and therefore $Q_{LWR,CitySim}$ is calculated using Equation \ref{CitySim_LWR_Ext}.
\begin{equation} \label{CitySim_Tenv} 
\sigma T_{env}^4 = \sigma F_{sky}T_{sky}^4 +\sigma F_{grd}T_{grd}^4 + \sum_{i=1}^{n} \epsilon_i \sigma F_{i}T_{i}^4
\end{equation}
\begin{equation} \label{CitySim_LWR_Ext} 
Q_{LWR,CitySim} = h_{r,env}(T_{surf}-T_{env})
\end{equation}

In the coupled simulation, EnergyPlus uses the CitySim supplied equivalent $h_{r,env}$ and $T_{env}$ to calculate weighted $h_{r,sky}$, $h_{r,grd}$, and $h_{r,air}$ values using the view factors and the sky-to-air split ratio. Figure \ref{combinedLWR} illustrates the schematic differences between the solo and coupled simulations on a theoretical example of a target building with two adjacent buildings with surfaces available for radiation exchange.

\begin{figure}[H]
  \centering
  \includegraphics[width=1.0\textwidth]{figures/LWRCalc_Combined_V3}
  \caption{Comparison of the LWR components between a) Solo EnergyPlus and b) Coupled CitySim/EnergyPlus configuration (adapted from \citep{Miller:2015vk})
  \label{combinedLWR}}
\end{figure}

\subsection{Co-simulation simplified calibration}
In the first case study, one aspect of this analysis is the comparison of actual measured performance of a buildings on campus with the simulation results of the co-simulation. A simplified calibration procedure is adapted from previous research to compare the measured heating and cooling data available on campus with various simulation scenarios \citep{Samuelson:2015jg}. This calibration procedure was utilized in the performance reconciliation of 18 buildings that were built according to the LEED Canada protocol and were under review of actualized performance. This protocol is unique in its analysis process to uncover design model deficiencies in a step-wise manner, utilizing the most easily accessible knowledge first and working towards equilibrium between measured and simulated. An appropriate balance between effort of implementation and value generated through the calibration process. The following steps are the general procedure applied to the targeted buildings:

\begin{enumerate}
  \item Using the local weather conditions for the simulation period
  \item Update simulation based on custom lighting schedules and power densities extracted from the measured data
  \item Update simulation based on custom plug load schedules and power densities extracted from the measured data
  \item Account for \emph{unregulated} building loads such as experimental equipment and process loads
\end{enumerate}

\section{Implementation}\label{Implementation}
\subsection{Campus case study 1: EnergyPlus simulation vs. co-simulation}
% {\color{red}This section will describe the ETH Hoenggerberg case study}
The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland. The campus includes 32 higher education buildings with spaces allocated to laboratories, office space, lecture halls, cafeterias, data centers and other types of similar spaces. The campus has a centralized energy management system (EMS) that contains 807 energy and water measurement points from heating, cooling, electricity, city gas, domestic hot water, grey water, and general water consumption.

%Figure \ref{fig:pointgraph} illustrates the breakdown of these measurement system data points amongst the campus buildings.

% \begin{figure}
% \centering
% \includegraphics[scale=0.7]{figures/pointbreakdown_anon}
% \caption{Available performance measurement points}
% \label{fig:pointgraph}
% \end{figure}

The focus of the co-simulation process is that the performance of a targeted building is evaluated through solo and coupled methods. The HPI building on campus was chosen in this case study due to amount and quality of measured data available from the EMS for this building. The HPI building is indicated on a campus map shown in Figure \ref{fig:campusmap} and is shaded red.

% The coupling process outlined is applicable with regards to a targeted building that is surrounded by an adjacent array of buildings. 
% {\color{red}Insert the campus map illustrating the targeted buildings.}

\begin{figure}[H]
\centering
\includegraphics[scale=0.5]{figures/ETH_Hoenngerbergcamp_targetedbuildings_HPI}
\caption{ETH Hoenggerberg campus map with the HPI building shaded red}
\label{fig:campusmap}
\end{figure}

\subsection{Model development}
In order to perform a co-simulation of the targeted buildings, initially a CitySim model of the campus is developed as seen in Figure \ref{fig:campuscitysim}. 
% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.

\begin{figure}[H]
\centering
\includegraphics[scale=0.2]{figures/HPI_Campus.png}
\caption{The HPI building modeled with OpenStudio for Sketchup.}
\label{fig:HPIcampus}
\end{figure}

% \begin{figure}[H]
% \centering
% \includegraphics[scale=0.2]{figures/campuscitysim}
% \caption{Campus modeled in CitySim}
% \label{fig:campuscitysim}
% \end{figure}

\subsection{Measured data collection and processing}
% Energy data from each of the targeted buildings is collected and analyzed in the context of the simplified calibration procedures. The measured datasets are screened and aggregated into typical usage profiles to be used for the lighting, plug-loads, and HVAC equipment availability schedules and power densities. Figures \ref{fig:hpz_profiles}-\ref{fig:hit_profiles} illustrate the aggregation examples of the heating energy from the HPZ building and the electrical energy from HPK, HPI, and HIT. These profiles were created through a filtering and clustering process known as \emph{DayFilter} \cite{Miller:2015kr}. These profiles are used to set the availability schedules as inputs into the EnergyPlus simulation to emulate the way occupants inhabit the building and how the building management system (BMS) controls the lighting and HVAC systems. This approach is compared to the practice of interviews and site visits to determine such input parameters.

% \begin{figure}
% \centering
% \includegraphics[scale=0.45]{figures/HPZ_combinedclusterandcal_4}
% \caption{HPZ Heating Energy Typical Profiles}
% \label{fig:hpz_profiles}
% \end{figure}

% \begin{figure}
% \centering
% \includegraphics[scale=0.45]{figures/HPK_combinedclusterandcal_4}
% \caption{HPK Electrical Energy Typical Profiles}
% \label{fig:hpk_profiles}
% \end{figure}

% \begin{figure}
% \centering
% \includegraphics[scale=0.45]{figures/HPI_combinedclusterandcal_4}
% \caption{HPI Electrical Energy Typical Profiles}
% \label{fig:hpi_profiles}
% \end{figure}

% \begin{figure}
% \centering
% \includegraphics[scale=0.45]{figures/HIT_combinedclusterandcal_4}
% \caption{HIT Electrical Energy Typical Profiles}
% \label{fig:hit_profiles}
% \end{figure}

\subsection{Campus case study 2: CitySim simulation vs. co-simulation}
Quartier Nord is a whole new quarter of the École Polytechnique Fédérale de Lausanne (EPFL) campus located at its northwest corner. This complex includes a Convention Centre with an auditorium with a maximum capacity of 3000 (seated) people, housing for 516 students, retail and service areas and a hotel. As a public space, this ensemble is organized around a main plaza (see Figure \ref{fig:quartier_nord_1}).

\begin{figure}[H]
\centering
\includegraphics[]{figures/quartier_nord_1}
\caption{The Quartier Nord at EPFL in Lausanne}
\label{fig:quartier_nord_1}
\end{figure}

With a particularly strong visual and formal identity, the SwissTech Convention Centre (STCC) is clearly the key protagonist. Applied with important functions for the region, the building has definitely become the new landmark. Designed as a Minergie building, it includes modern energy conversion technologies to reduce its energy consumption. The focus of the co-simulation is realised on the STCC, simulated with the nearby buidings for housing, retail and service areas.

\subsection{Model development}
The information required in the simulation mainly comprises three parts: physical, geometrical and operational data. The geometry information including the building’s shape, dimension, structure and materials was obtained from the Real Estate and Infrastructure Department of École Polytechnique Fédérale de Lausanne (EPFL), which was responsible for carrying out the project from call to tender to construction. However, since the documents provided were full of details but also conflicting with what has been installed as compared to the documents before construction, the task to realise a precise model of the buildings itself is rather tedious. Besides, it is even more challenging to get the operational data (daily occupancy, lighting and electrical equipment usage level and ventilation rate) as the building has only recently been set in operation mode and as engineers and technicians have been working on improving the controls. Therefore, due to unreliable monitoring data, the calibration step of the model has been unfortunately abandoned.\\

Considering the lack of detailed information about the building, a so-called detailed reference case was modeled with EnergyPlus \citep{Mauree:2015} in which regulation standards applied in the design phase from the SIA norms were used to complete the missing information (see Figure \ref{fig:model_yang}).

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/model_yang}
\caption{The Quartier Nord modeled with OpenStudio for Sketchup. The STCC on the left is the main focus of the study and represented by two thermal zones.}
\label{fig:model_yang}
\end{figure}

The corresponding CitySim model was created by exporting a DXF file from EnergyPlus, and importing it into the Graphical User Interface of CitySim. Physical caracteristics of the building were added to complete the CitySim model. Finally, the same script as described in section XXX was used to export the model from CitySim to EnergyPlus, giving a simplified EnergyPlus model.\\
As a summary, three models are compared: a detailed EnergyPlus model, a simplified CitySim model and a simplified EnergyPlus model. In addition to what a coupled simplified CitySim and EnergyPlus model is realised and its results analysed with respect to the other three models.

% \section{Results}
% {\color{red}Here we show all of the data of the comparison between the simulation outputs and the measured data from the campus}

\section{Results}

\section{Conclusion}

\subsection{Acknowledgements}

The authors would like to acknowledge the ETH Z\"urich Campus Facilities Department and the EPFL Real Estate and Infrastructure Department. This research was funded by the Competence Center in Energy and Mobility (CCEM) under the UMEM project.

\bibliographystyle{tBPS}
\bibliography{UMEM_CoSim}

\end{document}

### 2016-04-14 ipy-notebooks/raw-data/hpz-dayfilter/cal-heatmap-master/test/test.js

@@ -1,0 +1,4178 @@
+/*! cal-heatmap v3.5.3 (Thu Jul 23 2015 01:27:26)
+ *  ---------------------------------------------
+ *  Cal-Heatmap is a javascript module to create calendar heatmap to visualize time series data
+ *  https://github.com/kamisama/cal-heatmap
+ *  Licensed under the MIT license
+ *  Copyright 2014 Wan Qi Chen
+ */
+
+CalHeatMap.prototype.svg = function() {
+	return this.root.selectAll(".graph-domain");
+};
+
+QUnit.testStart(function( details ) {
+	$("body").append("<div id='cal-heatmap' style='display:none;'></div>");
+});
+
+QUnit.testDone(function( details ) {
+	$("#cal-heatmap").remove();
+});
+
+function createCalendar(settings) {
+
+	var cal = new CalHeatMap();
+	if (!settings.hasOwnProperty("loadOnInit")) {
+		settings.loadOnInit = false;
+	}
+
+	settings.animationDuration = 0;
+
+	if (!settings.hasOwnProperty("paintOnLoad")) {
+		settings.paintOnLoad = false;
+	}
+
+	cal.init(settings);
+
+	return cal;
+}
+
+/**
+ * Mark a test as skipped
+ *
+ * @link http://stackoverflow.com/questions/13748129/skipping-a-test-in-qunit
+ * @return {[type]} [description]
+ */
+QUnit.testSkip = function() {
+	QUnit.test(arguments[0] + ' (SKIPPED)', function() {
+		var li = document.getElementById(QUnit.config.current.id);
+		QUnit.done(function() {
+			if (li !== null) {
+				li.style.background = '#FFFF99';
+			}
+		});
+		ok(true);
+	});
+};
+testSkip = QUnit.testSkip;
+
+/*
+	-----------------------------------------------------------------
+	API
+	-----------------------------------------------------------------
+ */
+
+module("API : destroy()");
+
+asyncTest("Destroying the calendar", function() {
+	expect(3);
+
+	var node = d3.select("body").append("div").attr("id", "test-destroy");
+	var cal = createCalendar({itemSelector: node[0][0], animationDuration: 0, paintOnLoad: true});
+
+	ok(cal !== null, "the instance is created");
+
+	cal = cal.destroy(function() {
+		ok("callback called");
+		start();
+	});
+
+	ok(cal === null, "the instance is deleted");
+});
+
+/*
+	-----------------------------------------------------------------
+	API
[…]

### 2016-04-14 latex/UMEM_CoSim.tex
Update paper with latest results graphics
Updated both case studies graphics from the python-notebook folders.
Right now this is manual, but soon the notebooks will dump their
graphics directly into the right folders

@@
 \usepackage{float}
+\usepackage{lineno}
 
@@
 
+\linenumbers
+
 \section{Introduction}
@@
 \includegraphics[scale=0.7]{figures/UMEM_Workflow}
-\caption{Overview diagram of the coupling process including tools and outputs}
+\caption{Overview diagram of the coupling process including tools and outputs (adapted from \cite{thomas2014multiscale})}
 \label{fig:OverallWorkflowProcess}
@@
 \subsection{Model development}
-In order to perform a co-simulation of the targeted buildings, initially a CitySim model of the campus is developed as seen in Figure \ref{fig:campuscitysim}. 
+In order to perform a co-simulation of the targeted buildings, initially a CitySim model of the campus is developed.
+Through the workflow automation process, this geometry was converted into an EnergyPlus input file as seen in Figure \ref{fig:HPIcampus}.
 % An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.
@@
 
-\subsection{Measured data collection and processing}
-% Energy data from each of the targeted buildings is collected and analyzed in the context of the simplified calibration procedures.
+\subsection{Measured data collection and calibration}
+
+Energy data from the HPI building was collected and analyzed in the context of the simplified calibration procedures.
 The measured datasets are screened and aggregated into typical usage profiles to be used for the lighting, plug-loads, and HVAC equipment availability schedules and power densities.
-Figures \ref{fig:hpz_profiles}-\ref{fig:hit_profiles} illustrate the aggregation examples of the heating energy from the HPZ building and the electrical energy from HPK, HPI, and HIT.
-These profiles were created through a filtering and clustering process known as \emph{DayFilter} \cite{Miller:2015kr}.
-These profiles are used to set the availability schedules as inputs into the EnergyPlus simulation to emulate the way occupants inhabit the building and how the building management system (BMS) controls the lighting and HVAC systems.
+Figure \ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical energy for the HPI building.
+This profile was created through a filtering and clustering process known as \emph{DayFilter} \cite{Miller:2015kr}.
+This profile is used to set the availability schedules as inputs into the EnergyPlus simulation to emulate the way occupants inhabit the building and how the building management system (BMS) controls the lighting and HVAC systems.
 This approach is compared to the practice of interviews and site visits to determine such input parameters.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{figures/HPI_combinedclusterandcal_4}
+\caption{HPI Electrical Energy Typical Profiles}
+\label{fig:hpi_elec_profiles}
+\end{figure}
+
+The measured and simulated data from both the co-simulation and EnergyPlus solo simulations is shown in Figure \ref{fig:hpi_measvssim}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.55]{figures/HPI_MeasvsSim}
+\caption{HPI Measured vs. Co-Simulation and EnergyPlus Solo for Heating and Cooling Seasons}
+\label{fig:hpi_measvssim}
+\end{figure}
+
+\subsection{EnergyPlus co-simulation results}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.55]{figures/HPI_EnergyPlus_Heating}
+\caption{HPI Co-Simulation vs. EnergyPlus Solo for Heating}
+\label{fig:hpi_energyplusheating}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.55]{figures/HPI_EnergyPlus_Cooling}
+\caption{HPI Co-Simulation vs. EnergyPlus Solo for Cooling}
+\label{fig:hpi_energypluscooling}
+\end{figure}
+
+% \ref{fig:hpz_profiles}-\ref{fig:hit_profiles}
 
@@
 % \label{fig:hpk_profiles}
-% \end{figure}
-
-% \begin{figure}
-% \centering
-% \includegraphics[scale=0.45]{figures/HPI_combinedclusterandcal_4}
-% \caption{HPI Electrical Energy Typical Profiles}
-% \label{fig:hpi_profiles}
 % \end{figure}
@@
 
-\section{Results}
+% \section{Results}
+\subsection{Comparison of EnergyPlus and CitySim}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.55]{figures/QN_Cooling}
+\caption{Quartier Nord CitySim vs. EnergyPlus Solo for Cooling}
+\label{fig:qn_eplusvscitysim_cooling}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.55]{figures/QN_Heating.pdf}
+\caption{Quartier Nord CitySim vs. EnergyPlus Solo for Heating}
+\label{fig:qn_eplusvscitysim_heating}
+\end{figure}
+
+\subsection{EnergyPlus Co-simulation results}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.55]{figures/QN_EnergyPlus_Cooling}
+\caption{Quartier Nord EnergyPlus Co-Simulation vs. Solo for Cooling}
+\label{fig:qn_eplus_cosimvssolo_cooling}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.55]{figures/QN_EnergyPlus_Heating}
+\caption{Quartier Nord EnergyPlus Co-Simulation vs. Solo for Heating}
+\label{fig:qn_eplus_cosimvssolo_heating}
+\end{figure}
+
+\subsection{CitySim Co-simulation results}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.55]{figures/QN_CitySim_Cooling}
+\caption{Quartier Nord CitySim Co-Simulation vs. Solo for Cooling}
+\label{fig:qn_citysim_cosimvssolo_cooling}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.55]{figures/QN_CitySim_Heating}
+\caption{Quartier Nord CitySim Co-Simulation vs. Solo for Heating}
+\label{fig:qn_citysim_cosimvssolo_heating}
+\end{figure}
 

### 2016-04-15 latex/UMEM_CoSim.tex
Fixed the Quartier Nord analysis
I reassigned the CitySim outputs to Q(s) and the EnergyPlus outputs to
incorporate both zones.

@@
 Previous attempts of information exchange have been implemented between simulation engines at various scales.
-EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi}.
-EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program
-\citep{Yang:2012cr}.
+Much of the initial co-simulation work is at the subsystem and building-scales.
+Previous studies have analyzed strong and loose coupling of engines at this scale \citep{Trcka:2010cr,Wetter:2011kh}.
+At the building and urban-scale, EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi}.
+EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program \citep{Yang:2012cr}.
 % \subsection{Urban scale performance simulation}
@@
 \subsection{Coupling process}
-The coupling process of a simplified single zone model and contextual surrounding buildings is outlined previously \citep{thomas2014multiscale}.
-This effort is based on the utilization of the Design Performance Viewer (DPV) and associated work flow.
+The coupling process of a simplified single zone model and contextual surrounding buildings is outlined in a previous study \citep{thomas2014multiscale}.
+This study forms the basis for the methodology in the current effort.
+This process utilizes the Design Performance Viewer (DPV) and associated work flow.
 The DPV is a tool written to extract and simulate an EnergyPlus input data file (IDF) from an Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM \citep{Schlueter2009}.
@@
 \section{Implementation}\label{Implementation}
-\subsection{Campus case study 1: EnergyPlus simulation vs. co-simulation}
+
+\subsection{Campus case study 1: HPI Building}
 % {\color{red}This section will describe the ETH Hoenggerberg case study}

### 2016-04-15 latex/UMEM_CoSim.tex
Updated graphics and added lit review content
- Changed the QN CitySim graphics by choosing a different zone
- Updated .bib and added some more co-simulation examples to lit review

@@
 Previous studies have analyzed strong and loose coupling of engines at this scale \citep{Trcka:2010cr,Wetter:2011kh}.
-At the building and urban-scale, EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi}.
+Coupling of building-scale simulation with urban-scale computational fluid dynamics (CFD) is attempted for modelling natural ventilation \citep{Zhang:2013vx} and to improve energy prediction \citep{Bouyer:2011eha}.
 EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program \citep{Yang:2012cr}.
+It was also coupled with simplified lumped parameter models in order to facilitate comparison with measured sensor data \citep{Martin:2015fj}.
+EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi}.
 % \subsection{Urban scale performance simulation}
@@
 
-\subsection{Co-simulation simplified calibration}
+\subsection{Simplified calibration}
 In the first case study, one aspect of this analysis is the comparison of actual measured performance of a buildings on campus with the simulation results of the co-simulation.
@@
 An appropriate balance between effort of implementation and value generated through the calibration process.
-The following steps are the general procedure applied to the targeted buildings:
 
-\begin{enumerate}
-  \item Using the local weather conditions for the simulation period
-  \item Update simulation based on custom lighting schedules and power densities extracted from the measured data
-  \item Update simulation based on custom plug load schedules and power densities extracted from the measured data
-  \item Account for \emph{unregulated} building loads such as experimental equipment and process loads
-\end{enumerate}
+% The following steps are the general procedure applied to the targeted buildings:
+
+% \begin{enumerate}
+%   \item Using the local weather conditions for the simulation period
+%   \item Update simulation based on custom lighting schedules and power densities extracted from the measured data
+%   \item Update simulation based on custom plug load schedules and power densities extracted from the measured data
+%   \item Account for \emph{unregulated} building loads such as experimental equipment and process loads
+% \end{enumerate}
 
 \section{Implementation}\label{Implementation}
+The co-simulation process is implemented on two case studies in Switzerland.
+The first is the ETH Z\"urich Hoenggerberg campus in Z\"urich, Switzerland.
+The focus of this case study is to compare the impact of the information exchange through co-simulation within the EnergyPlus engine.
+The intent on this campus was to develop techniques for retrofit analysis using EnergyPlus.
+The targeted building on this campus is the HPI Building.
+Raw measured data is available for many of the buildings on campus, thus a simplified calibration procedure is used to reconcile the simulation results.\\
 
-\subsection{Campus case study 1: HPI Building}
+The second case study is the EPFL campus in Lausanne, Switzerland.
+The targeted building in this case was the Quartier Nord complex.
+The focus of this study was to compare the output results of both CitySim and EnergyPlus.
+Reliable measured data for calibration is not currently available for this building.
+
+\subsection{Campus case study 1: ETHZ Hoenggerberg Campus}
 % {\color{red}This section will describe the ETH Hoenggerberg case study}
-The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland.
-The campus includes 32 higher education buildings with spaces allocated to laboratories, office space, lecture halls, cafeterias, data centers and other types of similar spaces.
+%The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland. 
+The ETH Z\"urich Hoenggerberg campus includes 32 higher education buildings with spaces allocated to laboratories, office space, lecture halls, cafeterias, data centers and other types of similar spaces.
 The campus has a centralized energy management system (EMS) that contains 807 energy and water measurement points from heating, cooling, electricity, city gas, domestic hot water, grey water, and general water consumption.
@@
 
-\subsection{Campus case study 2: CitySim simulation vs. co-simulation}
+\subsection{Campus case study 2: EPFL Quartier Nord}
 Quartier Nord is a whole new quarter of the École Polytechnique Fédérale de Lausanne (EPFL) campus located at its northwest corner.
@@
 Physical caracteristics of the building were added to complete the CitySim model.
-Finally, the same script as described in section XXX was used to export the model from CitySim to EnergyPlus, giving a simplified EnergyPlus model.\\
-As a summary, three models are compared: a detailed EnergyPlus model, a simplified CitySim model and a simplified EnergyPlus model.
+Finally, the same script as described in Section \ref{Methodology} was used to export the model from CitySim to EnergyPlus, giving a simplified EnergyPlus model.\\
+
+% As a summary, three models are compared: a detailed EnergyPlus model, a simplified CitySim model and a simplified EnergyPlus model.
 In addition to what a coupled simplified CitySim and EnergyPlus model is realised and its results analysed with respect to the other three models.

### 2016-04-15 latex/UMEM_CoSim.tex
Added some content

@@
 \textsuperscript{b}{\em Solar Energy and Building Physics Laboratory (LESO-PB), Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland}
-\received{v0.1 released January 2015}
+\received{Submission for review on April 30, 2016} %TARGETED!
 }
@@
   \item Co-simulate the urban and building scale models through concurrent information exchange
-  \item Implement a simplified calibration procedure based on reconciling the co-simulation output results for a selected subset of buildings that have adequate measured energy performance data from the campus energy information system (EIS)
+  \item Implement a simplified calibration procedure based on reconciling the co-simulation output results for a target building that have adequate measured energy performance data from the campus energy information system (EIS)
 \end{enumerate}
@@
 The first two objectives have been demonstrated in a simplified context in previous literature \citep{thomas2014multiscale,Miller:2015vk}.
-The novelty of the current publication is an extension to this research through the modelling and co-simulation of real-world case studies.
-The third objective is completely novel in that no previous study has compared the results of a building and urban-scale co-simulation procedure to measured data from a real-world campus.
+The innovation in the current publication is an extension to this research through the modelling and co-simulation of real-world case studies.
+With respect to the third contribution, to the best of the author's knowledge, no previous study has compared the results of a building and urban-scale co-simulation procedure to measured data from a real-world campus.
 
@@
 Figure \ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical energy for the HPI building.
-This profile was created through a filtering and clustering process known as \emph{DayFilter} \cite{Miller:2015kr}.
+This profile was created through a filtering and clustering process known as \emph{DayFilter} \citep{Miller:2015kr}.
 This profile is used to set the availability schedules as inputs into the EnergyPlus simulation to emulate the way occupants inhabit the building and how the building management system (BMS) controls the lighting and HVAC systems.
@@
 
-The measured and simulated data from both the co-simulation and EnergyPlus solo simulations is shown in Figure \ref{fig:hpi_measvssim}.
+The measured and simulated data from both the co-simulation and EnergyPlus solo simulation was compared in order to create a realistic scenario for comparison.
+The calibration process was undertaken through a series of steps such as including local weather conditions for the simulation period and adding custom lighting schedules and power densities extracted from the measured data.
+The models were calibrated to the summer season (May-September) for cooling and the winter season (Jan-April and October to December) for heating.
+This approach was taken as the data quality for the measurements were deemed most accurate during the appropriate seasons.
+Figure \ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the simulations after the tuning process.
+Daily data was used to calculated goodness of fit to determine calibration success.
 
@@
 
+After calibration, a comparison of co-simulation and solo EnergyPlus simulations are made.
+Figure \ref{fig:hpi_energyplusheating} illustates the difference in predicted heating energy consumption across the test year.
+A consistent offset exists across the time frame of days in January, the peak of the heating season.
+A more varied discrepancy across the heating months is noticed resulting and overall increase of heating prediction of 4.8\% due to co-simulation.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+For cooling, a more dramatic discrepancy can be seen between co-simulation and solo EnergyPlus. A 20.2\% decrease in predicted cooling energy is observed.
 
@@
 
+Both the CitySim and EnergyPlus engines are utilized in this case study. The first comparison to observe are the differences between the two engines when focused on the Quartier Nord building.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+When simulated in isolation, the CitySim engine predicts a 28.8\% higher heating load than EnergyPlus with the model inputs aligned as closely as possible.
+Use of the co-simulation, brings the engines to within 5.4\%.
+Figure \ref{fig:qn_eplusvscitysim_heating} illustrates these differences.
 
@@
 
-\subsection{EnergyPlus Co-simulation results}
+\subsection{EnergyPlus co-simulation results}
+
+When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed.
 
@@
 
+A 2.8\% increase in heating energy is observed.
+
 \begin{figure}[H]
@@
 
-\subsection{CitySim Co-simulation results}
+\subsection{CitySim co-simulation results}
+
+When focusing on solely on CitySim, a X\% decrease in cooling energy is observed.
 
@@
 \end{figure}
+
+A 30.8\% decrease in heating energy is observed.
 
@@
 \section{Conclusion}
+The ability to couple and leverage the best aspects of multiple simulation engines can enhance the modeling of large scale urban agglomerations.
+This paper has outlined one such scenario in which the building-focused EnergyPlus simulation engine is coupled and co-simulated with the urban-scale CitySim engine.
+This process is implemented through a fully automated work flow process that extract geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each time step of targeted variables, and accumulates the results for analysis.
+The process has been implemented on simpflied theoretical scenarios in the past and the key innovation with this work is in implementation on actual case study campuses and targeted buildings.
+More reliable results of the magnitude of differences between the simulation techniques can be extracted from this scenario.
 

### 2016-04-18 latex/UMEM_CoSim.tex
Added text content for lit review, massaging references, results discussion, etc

@@
 In order to address the deficiencies of the individual engines, the current effort described seeks to couple building and urban scale simulation.
-The research in this paper is part of an larger coupling effort in which various engines are connected and co-simulated to create a more comprehensive analysis of the urban scale \citep{Dorer:2013vt}.
+The research in this paper is part of an larger coupling effort in which various engines are connected and co-simulated to create a more comprehensive analysis of the urban scale \citep{Dorer:2013vt,Allegrini:2012kx}.
 The target is the computational interface between the building energy model, using EnergyPlus, and the urban energy model using CitySim.
@@
 Previous attempts of information exchange have been implemented between simulation engines at various scales.
-Much of the initial co-simulation work is at the subsystem and building-scales.
+Much of the initial co-simulation work in the literature is at the subsystem and building-scales.
 Previous studies have analyzed strong and loose coupling of engines at this scale \citep{Trcka:2010cr,Wetter:2011kh}.
-Coupling of building-scale simulation with urban-scale computational fluid dynamics (CFD) is attempted for modelling natural ventilation \citep{Zhang:2013vx} and to improve energy prediction \citep{Bouyer:2011eha}.
+Coupling of building-scale simulation with urban-scale computational fluid dynamics (CFD) is attempted for modeling natural ventilation \citep{Zhang:2013vx} and to improve energy prediction \citep{Bouyer:2011eha}.
+A comprehensive review of energy and airflow modeling of neighborhoods and university campuses was published that includes strategies aspects of coupling different types of models \citep{Srebric:2015gq}.
 EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program \citep{Yang:2012cr}.
 It was also coupled with simplified lumped parameter models in order to facilitate comparison with measured sensor data \citep{Martin:2015fj}.
-EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi}.
+EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi} and urban weather generation \citep{Bueno:2013hh}.
+Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}.
 % \subsection{Urban scale performance simulation}
@@
 \section{Methodology}\label{Methodology}
-% A significant amount of the following methodology is developed in previous literature and is reiterated in this section in order to set the context for Section \ref{Implementation}.
+% Portions of the following methodology is developed in previous literature and is reiterated in this section in order to set the context for Section \ref{Implementation}.
 The previous published research is clearly outlined at the beginning of each subsection.
@@
 The DPV utilizes the Revit API to extract geometrical information about the building and the physical properties of walls, windows, doors, roofs and floors.
-This information is encoded in the BIM model as wall types, roof types,
-floor types as well as window and door families.
+This information is encoded in the BIM model as wall types, roof types, floor types as well as window and door families.
 Wherever possible, the tool uses the layering and materials of the construction types, enhancing them with physical attributes relevant to EnergyPlus.
@@
 \includegraphics[scale=0.7]{figures/UMEM_Workflow}
-\caption{Overview diagram of the coupling process including tools and outputs (adapted from \cite{thomas2014multiscale})}
+\caption{Overview diagram of the coupling process including tools and outputs \citep{thomas2014multiscale}}
 \label{fig:OverallWorkflowProcess}
@@
 \includegraphics[scale=0.7]{figures/UMEM_FMU_Overview}
-\caption{Simulation information exchange between CitySim and EnergyPlus using FMI (adapted from \cite{thomas2014multiscale})}
+\caption{Simulation information exchange between CitySim and EnergyPlus using FMI \citep{thomas2014multiscale}}
 \label{fig:FMUOverview}
@@
   \includegraphics[width=1.0\textwidth]{figures/LWRCalc_Combined_V3}
-  \caption{Comparison of the LWR components between a) Solo EnergyPlus and b) Coupled CitySim/EnergyPlus configuration (adapted from \citep{Miller:2015vk})
+  \caption{Comparison of the LWR components between a) Solo EnergyPlus and b) Coupled CitySim/EnergyPlus configuration \citep{Miller:2015vk}
   \label{combinedLWR}}
 \end{figure}
+
+\subsection{Work flow automation}
+The coupling, simulation and co-simulation process is completely managed within a program called VisTrails.
+This tool empowers the coupling of various executable files and their connecting scripts in a graphical diagrams that enhances reproducibility and process automation \citep{Freire:2014tt}.
+
+INSERT VISTRAILS GRAPHIC HERE
 
@@
 The HPI building on campus was chosen in this case study due to amount and quality of measured data available from the EMS for this building.
-The HPI building is indicated on a campus map shown in Figure \ref{fig:campusmap} and is shaded red.
+HPI is a 2,610 sq.
+meter building that made up mostly of office space and classrooms.
+It also includes 400 sq.
+meter convenience store and coffee shop.
+The building is indicated on a campus map shown in Figure \ref{fig:campusmap} and is shaded red.
 
@@
 Through the workflow automation process, this geometry was converted into an EnergyPlus input file as seen in Figure \ref{fig:HPIcampus}.
+The EnergyPlus input file is then used as an input to execute EnergyPlus solo and co-simulation processes for the purpose of simplified calibration, and then to understand the magnitude of difference between these simulation scenarios.
 % An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.
@@
 \includegraphics[scale=0.2]{figures/HPI_Campus.png}
-\caption{The HPI building modeled with OpenStudio for Sketchup.}
+\caption{The HPI building modeled with OpenStudio for Sketchup}
 \label{fig:HPIcampus}
@@
 Figure \ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the simulations after the tuning process.
-Daily data was used to calculated goodness of fit to determine calibration success.
+The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating.
+These metrics fall within the +/- 10\% and 30\% used in this case study for the purposes of partial calibration.
+The goal of calibration in this case is to simply bring the models to within a reasonable range of reality in order to bring more confidence to analysis of the discrepancies between the solo and co-simulation scenarios.
+%Daily data was used to calculated goodness of fit to determine calibration success. 
+%The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating.
 
@@
 
-After calibration, a comparison of co-simulation and solo EnergyPlus simulations are made.
+After calibration, a comparison of co-simulation and solo EnergyPlus simulations is made.
+For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus.
+A 20.2\% decrease in predicted cooling energy is observed as seen in Figure \ref{hpi_energypluscooling}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.55]{figures/HPI_EnergyPlus_Cooling}
+\caption{HPI Co-Simulation vs. EnergyPlus Solo for Cooling}
+\label{fig:hpi_energypluscooling}
+\end{figure}
+
 Figure \ref{fig:hpi_energyplusheating} illustates the difference in predicted heating energy consumption across the test year.
@@
 \label{fig:hpi_energyplusheating}
-\end{figure}
-
-For cooling, a more dramatic discrepancy can be seen between co-simulation and solo EnergyPlus. A 20.2\% decrease in predicted cooling energy is observed.
-
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.55]{figures/HPI_EnergyPlus_Cooling}
-\caption{HPI Co-Simulation vs. EnergyPlus Solo for Cooling}
-\label{fig:hpi_energypluscooling}
 \end{figure}
@@
 This complex includes a Convention Centre with an auditorium with a maximum capacity of 3000 (seated) people, housing for 516 students, retail and service areas and a hotel.
-As a public space, this ensemble is organized around a main plaza (see Figure \ref{fig:quartier_nord_1}).
+As a public space, this ensemble is organized around a main plaza as seen in  Figure \ref{fig:quartier_nord_1}).
 
@@
 
-Considering the lack of detailed information about the building, a so-called detailed reference case was modeled with EnergyPlus \citep{Mauree:2015} in which regulation standards applied in the design phase from the SIA norms were used to complete the missing information (see Figure \ref{fig:model_yang}).
+Considering the lack of detailed information about the building, a so-called detailed reference case was modeled with EnergyPlus \citep{Mauree:2015} in which regulation standards applied in the design phase from the SIA norms were used to complete the missing information.
+A rendering of this model is seen in Figure \ref{fig:model_yang}.
 
@@
 
-When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed.
+When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_cooling}.
 
@@
 
-A 2.8\% increase in heating energy is observed.
+A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}.
 
@@
 
-When focusing on solely on CitySim, a X\% decrease in cooling energy is observed.
+When focusing on solely on CitySim, a X\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}.
 
@@
 
-A 30.8\% decrease in heating energy is observed.
+A 30.8\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}.
 
@@
 
+Future work in using co-simulation models for buildings and campuses would more intensively utilize the model results in a practical implementation of retrofit scenarios or urban-scale energy systems research.
+
 \subsection{Acknowledgements}
@@
 The authors would like to acknowledge the ETH Z\"urich Campus Facilities Department and the EPFL Real Estate and Infrastructure Department.
-This research was funded by the Competence Center in Energy and Mobility (CCEM) under the UMEM project.
+This research was funded by the Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale Energy Modeling (UMEM) project.
 

### 2016-04-18 latex/UMEM_CoSim.tex
updated clustering graphic

@@
 \subsection{Coupling process}
-The coupling process of a simplified single zone model and contextual surrounding buildings is outlined in a previous study \citep{thomas2014multiscale}.
+The coupling process of a simplified single zone model and contextual surrounding buildings is outlined in previous studies \citep{thomas2014multiscale,Thomas:2012wj}.
 This study forms the basis for the methodology in the current effort.
@@
 
-As of version 8.1.0, EnergyPlus supports exporting a simulation model as a Functional Mock-up Unit (FMU) \citep{Nouidui:2014hq}.
+As of version 8.1.0, EnergyPlus supports exporting a simulation model as a Functional Mock-up Unit (FMU) \citep{Nouidui:2014hq,Anonymous:ZZTfF80-}.
 This feature introduces new IDF objects to specify the interface such an FMU exposes.
@@
 Co-simulation exchange variables either mimic an EnergyPlus schedule, an EMS variable or drive an EMS actuator.
-It was determined that in order to export an output variable using the FMU export functionality, the variable itself must also be output with an IDF object of type \emph{Output:Variable} or \emph{EnergyManagementSystem:OutputVariable} in the IDF file as well.
 Since the model used by CitySim to simulate a building is more abstract than the model used by EnergyPlus, the EMS is used to aggregate certain values.
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.7]{figures/UMEM_FMU_Overview}
-\caption{Simulation information exchange between CitySim and EnergyPlus using FMI \citep{thomas2014multiscale}}
-\label{fig:FMUOverview}
-\end{figure}
+% It was determined that in order to export an output variable using the FMU export functionality, the variable itself must also be output with an IDF object of type \emph{Output:Variable} or \emph{EnergyManagementSystem:OutputVariable} in the IDF file as well.
 
@@
 Once configured, this script produces an FMU file based on the augmented IDF file and the weather file to be used as well as a DLL file implementing the Functional Mock-up Interface that can load the IDF file, locate EnergyPlus and run the simulation.
-Table \ref{FMUimports} and \ref{FMUexports} outline the variables exchanged between EnergyPlus and CitySim through the FMI.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.7]{figures/UMEM_FMU_Overview}
+\caption{Simulation information exchange between CitySim and EnergyPlus using FMI \citep{thomas2014multiscale}}
+\label{fig:FMUOverview}
+\end{figure}
+
+% Table \ref{FMUimports} and \ref{FMUexports} outline the variables exchanged between EnergyPlus and CitySim through the FMI.
 
@@
 
-On an hourly basis, CitySim performs a heating and cooling needs prediction step.
+% On an hourly basis, CitySim performs a heating and cooling needs prediction step.
 The temperature determination step for the main building is replaced with the results of the EnergyPlus timestep as obtained through FMI library.
-The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus (see Table \ref{FMUimports}), and to receive data from EnergyPlus that are further used within CitySim for the next time steps (see Table \ref{FMUimports}).
+The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus, and to receive data from EnergyPlus that are further used within CitySim for the next time steps.
+Several key urban-scale weather variables are sent to EnergyPlus from CitySim in order to better account for the localized effects of surrounding buildings, geography and climactic conditions.
+These variables include various outdoor air conditions such as drybulb and wetbulb temperatures, dewpoint, humidity, wind speed and direction, and direct and diffuse solar radiation.
+These variables overwrite the input weather variables that EnergyPlus obtains from its weather file input.
+One of the key objectives of CitySim as a a simulation engine has been its to account for physical phenomenon inherent to urban environments that is often neglected in building-scale simulation environments \citep{Robinson:2004cr,Robinson:2009tm}.
+Long wave radiation exchange between the simulated building and its surroundings is sent to EnergyPlus; this process is describe in detail in a subsequent methodology section.
+Finally, CitySim shares its calculated occupancy schedules as it uses a more robust model of occupants behavior \citep{Haldi:2011dr}.
 
 \begin{table}[H]
-\tbl{Values imported by EnergyPlus from CitySim by the FMU}
+\tbl{Values sent to EnergyPlus from CitySim by the FMU}
 {\begin{tabular}[l]{@{}lcc}\toprule
-  \bf{Object (ep\_id)} &  \bf{Variable Name} & \bf{Description} \\
+  \bf{Object} &  \bf{Variable Name} & \bf{Description} \\
 \colrule
@@
 
+Variables sent to CitySim by EnergyPlus at each timestep include several variables related to the calculation of heating and cooling loads of a targeted building.
+These variables are transferred due to the ability of EnergyPlus to model more detailed building systems, schedules, ventilation and internal load types than CitySim.
+For example, EnergyPlus is flexible enough to model a detailed, radiant heating and cooling system that would be impossible in CiytSim \cite{barbara:2015tz}.
+EnergyPlus is an engine optimized on the accuracy of building-scale systems, thus CitySim can take advantage of these models through coupling and co-simulation.
+EnergyPlus sends the heating and cooling loads, the surface temperatures of the exterior surfaces and the ventilation flow rates to CitySim.
+
 \begin{table}[H]
-\tbl{Values exported by EnergyPlus to CitySim by the FMU}
+\tbl{Values to CitySim from EnergyPlus by the FMU}
 {\begin{tabular}[l]{@{}lcc}\toprule
-  \bf{Object (ep\_id)} &  \bf{Variable Name} & \bf{Description} \\
+  \bf{Object} &  \bf{Variable Name} & \bf{Description} \\
 \colrule
@@
 
-Long wave radiation exchange in the urban scale environment is also coupled in the co-simulation process.
-However, it requires the development of a set of approximations to reduce the number of coupled variables between the engines and to account for differences in the methods by which each engine calculates this metric.
+Long wave radiation exchange in the urban scale environment is coupled in the co-simulation process and it requires the development of a set of approximations to reduce the number of coupled variables between the engines and to account for differences in the methods by which each engine calculates this metric.
 A detailed description of Long Wave Radiation (LWR) variable exchange and approximation is found in a previously published study \citep{Miller:2015vk} on a simplified theoretical case.
@@
 \subsection{Work flow automation}
-The coupling, simulation and co-simulation process is completely managed within a program called VisTrails.
+The coupling, simulation and co-simulation process is completely managed within a program called VisTrails \citep{Anonymous:Cayf2tu7}.
 This tool empowers the coupling of various executable files and their connecting scripts in a graphical diagrams that enhances reproducibility and process automation \citep{Freire:2014tt}.
@@
 \centering
-\includegraphics[scale=0.6]{figures/HPI_combinedclusterandcal_4}
+\includegraphics[scale=0.55]{figures/HPI_combinedclusterandcal_5}
 \caption{HPI Electrical Energy Typical Profiles}
@@
 The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating.
-These metrics fall within the +/- 10\% and 30\% used in this case study for the purposes of partial calibration.
+These metrics fall within the +/-10\% NMBE and +/-30\% CVRSME used in this case study for the purposes of partial calibration.
 The goal of calibration in this case is to simply bring the models to within a reasonable range of reality in order to bring more confidence to analysis of the discrepancies between the solo and co-simulation scenarios.
@@
 For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus.
-A 20.2\% decrease in predicted cooling energy is observed as seen in Figure \ref{hpi_energypluscooling}.
+A 20.2\% decrease in predicted cooling energy is observed as seen in Figure \ref{fig:hpi_energypluscooling}.
 
@@
 This paper has outlined one such scenario in which the building-focused EnergyPlus simulation engine is coupled and co-simulated with the urban-scale CitySim engine.
-This process is implemented through a fully automated work flow process that extract geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each time step of targeted variables, and accumulates the results for analysis.
+This process is implemented through a fully automated work flow process that extract geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each timestep of targeted variables, and accumulates the results for analysis.
 The process has been implemented on simpflied theoretical scenarios in the past and the key innovation with this work is in implementation on actual case study campuses and targeted buildings.

### 2016-04-20 latex/UMEM_CoSim.tex
Added a commenting format for reviewing the paper
Clayton writes in red.
Jerome in blue
Daren in green

@@
 \newtheorem{remark}{Remark}
+\newcommand{\noteCM}[1]{\footnote{\textcolor{red}{#1}}}
+\newcommand{\noteJK}[1]{\footnote{\textcolor{blue}{#1}}}
+\newcommand{\noteDT}[1]{\footnote{\textcolor{green}{#1}}}
 
@@
 
-\section{Introduction}
+\section{Introduction}\noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}
 
@@
 \includegraphics[scale=0.7]{figures/UMEM_overview_new}
-\caption{EnergyPlus and CitySim coupling are part of the wider context. Each block in the diagram represents an environment, with the tool/engine name in italics (adapted from \citep{Dorer:2013vt})}
+\caption{EnergyPlus and CitySim coupling are part of the wider context.
+Each block in the diagram represents an environment, with the tool/engine name in italics (\citep{thomas2014multiscale}, adapted from \citep{Dorer:2013vt})}
 \label{fig:UMEM}
@@
 
-Variables sent to CitySim by EnergyPlus at each timestep include several variables related to the calculation of heating and cooling loads of a targeted building.
+Variables sent to CitySim by EnergyPlus at each time step include several variables related to the calculation of heating and cooling loads of a targeted building.
 These variables are transferred due to the ability of EnergyPlus to model more detailed building systems, schedules, ventilation and internal load types than CitySim.
@@
 
-INSERT VISTRAILS GRAPHIC HERE
+INSERT VISTRAILS GRAPHIC HERE\noteCM{Daren -- can you give me a good screenshot of the Vistrails for the HPI building? Pretty please.}
 
@@
 
-\section{Implementation}\label{Implementation}
+\section{Implementation}\label{Implementation and results}
 The co-simulation process is implemented on two case studies in Switzerland.
@@
 A 20.2\% decrease in predicted cooling energy is observed as seen in Figure \ref{fig:hpi_energypluscooling}.
+Figure \ref{fig:hpi_energyplusheating} illustrates the difference in predicted heating energy consumption across the test year.
+A consistent offset exists across the time frame of days in January, the peak of the heating season.
+A more varied discrepancy across the heating months is noticed resulting and overall increase of heating prediction of 4.8\% due to co-simulation.
+The exchange of long wave radiation for this particular site is likely greater due to the proximity of surrounding buildings.
+These performance differences due to co-simulation are compared to a theoretical single-zone case study in which there was a 15-30\% increase in heating energy and a 4-11\% decrease in cooling energy.
+The results form this scenario are less extreme from the heating side and more extreme from the cooling side.
 
@@
 \end{figure}
-
-Figure \ref{fig:hpi_energyplusheating} illustates the difference in predicted heating energy consumption across the test year.
-A consistent offset exists across the time frame of days in January, the peak of the heating season.
-A more varied discrepancy across the heating months is noticed resulting and overall increase of heating prediction of 4.8\% due to co-simulation.
 
@@
 The information required in the simulation mainly comprises three parts: physical, geometrical and operational data.
-The geometry information including the building’s shape, dimension, structure and materials was obtained from the Real Estate and Infrastructure Department of École Polytechnique Fédérale de Lausanne (EPFL), which was responsible for carrying out the project from call to tender to construction.
+The geometry information including the shape, dimension, structure and materials was obtained from the Real Estate and Infrastructure Department of École Polytechnique Fédérale de Lausanne (EPFL), which was responsible for carrying out the project from call to tender to construction.
 However, since the documents provided were full of details but also conflicting with what has been installed as compared to the documents before construction, the task to realise a precise model of the buildings itself is rather tedious.
@@
 
-Considering the lack of detailed information about the building, a so-called detailed reference case was modeled with EnergyPlus \citep{Mauree:2015} in which regulation standards applied in the design phase from the SIA norms were used to complete the missing information.
+Considering the lack of detailed information about the building, a so-called detailed reference case was modeled with EnergyPlus \citep{Mauree:2015to} in which regulation standards applied in the design phase from the SIA norms were used to complete the missing information.
 A rendering of this model is seen in Figure \ref{fig:model_yang}.
@@
 
-Both the CitySim and EnergyPlus engines are utilized in this case study. The first comparison to observe are the differences between the two engines when focused on the Quartier Nord building.
+Both the CitySim and EnergyPlus engines are utilized in this case study.
+The first comparison to observe are the differences between the two engines when focused on the Quartier Nord building.
+When simulated in isolation, the CitySim engine predicts a 28.6\% increase in heating load and a 44.4\% increase in cooling load than EnergyPlus with the model inputs aligned as closely as possible.
+This phenomenon is due to the differences in the way each of these engines calculates heating and cooling loads.
+Use of the co-simulation process, brings the engines to within 5.4\%.
+Figure \ref{fig:qn_eplusvscitysim_heating} illustrates these differences.
 
@@
 \end{figure}
-
-When simulated in isolation, the CitySim engine predicts a 28.8\% higher heating load than EnergyPlus with the model inputs aligned as closely as possible.
-Use of the co-simulation, brings the engines to within 5.4\%.
-Figure \ref{fig:qn_eplusvscitysim_heating} illustrates these differences.
 
@@
 When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_cooling}.
+A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}.
+These differences are less
 
@@
 
-A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}.
-
 \begin{figure}[H]
@@
 
-\subsection{CitySim co-simulation results}
+\subsection{CitySim co-simulation results}\noteCM{Jerome -- I really need some help interpreting this...}
 
-When focusing on solely on CitySim, a X\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}.
+When focusing on solely on CitySim, a 26.9\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}.
+A 49.1\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}.
 
@@
 \end{figure}
-
-A 30.8\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}.
 
@@
 The ability to couple and leverage the best aspects of multiple simulation engines can enhance the modeling of large scale urban agglomerations.
-This paper has outlined one such scenario in which the building-focused EnergyPlus simulation engine is coupled and co-simulated with the urban-scale CitySim engine.
+This paper has outlined two such scenarios in which the building-focused EnergyPlus simulation engine is coupled and co-simulated with the urban-scale CitySim engine.
 This process is implemented through a fully automated work flow process that extract geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each timestep of targeted variables, and accumulates the results for analysis.
-The process has been implemented on simpflied theoretical scenarios in the past and the key innovation with this work is in implementation on actual case study campuses and targeted buildings.
-More reliable results of the magnitude of differences between the simulation techniques can be extracted from this scenario.
+The process has been implemented on simplified theoretical scenarios in the past and the key innovation with this work is in implementation on actual case study campuses and targeted buildings.
+The results illustrate that the differences between the co-simulation and solo environments are within range of previous theoretical models.
+More reliable results of the magnitude of differences between the simulation techniques can be extracted from these real-world scenarios.
 

### 2016-04-20 latex/UMEM_CoSim.tex
A few more comments added

@@
 A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}.
-These differences are less
+These differences are less prounced that the HPI case study.
+\noteCM{I'm planning to elaborate on these sections but am struggling to interpret the results other than just "co-sim and solo are difference" -- what do you guys think?}
 
@@
 
-\subsection{CitySim co-simulation results}\noteCM{Jerome -- I really need some help interpreting this...}
+\subsection{CitySim co-simulation results}
 
@@
 A 49.1\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}.
+\noteCM{Jerome -- I need some help interpreting these results -- you mentioned that there is an expected delta between citysim and energyplus in previous studies.
+Can you help elaborate on that?}
 

### 2016-04-22 latex/UMEM_CoSim.tex
added comments to tex and pdf of workflow

@@
 In the first case study, on-site weather and measured performance data is then compared to the output from two modeling scenarios: building-scale simulation using EnergyPlus and co-simulation of the engines.
-A partial calibration process is implemented to reconcile the simulations with the measured data a targeted office building on campus.
+A partial calibration process is implemented to reconcile the simulations with the measured data \noteDT{insert: "of"} a targeted office building on campus.
 In the second case study, the co-simulation results are compared to the both the CitySim simulation and EnergyPlus engines.
 The results show that {\color{red}insert results here}.
-A discussion is included of the challenges encountered with the urban scale calibration and the strengths and weaknesses of the developed process.
+A discussion is included of the challenges encountered with the urban scale calibration and the strengths and weaknesses of the developed process.\noteDT{Clayton, can you get your editor to do hard linewrapping?
+all your paragraphs are a single line which breaks the diff model of GitHub and makes editing in VIM super hard...}
 \end{abstract}
@@
 For example, urban scale simulation highly simplifies the building systems and internal load models, thus making retrofit analysis at the systems level difficult.
-And whole building simulation neglects many of the various contextual consideration of the urban environment such as long wave radiation exchange with adjacent surfaces and localized urban weather effects.
+And whole building simulation neglects many of the various contextual consideration of the urban environment such as long wave radiation exchange with adjacent surfaces and localized urban weather effects.\noteDT{ref?}
 
-In order to address the deficiencies of the individual engines, the current effort described seeks to couple building and urban scale simulation.
-The research in this paper is part of an larger coupling effort in which various engines are connected and co-simulated to create a more comprehensive analysis of the urban scale \citep{Dorer:2013vt,Allegrini:2012kx}.
+In order to address the deficiencies of the individual engines, the current effort described\noteDT{can we do phrasing?
+prettyplease?} seeks to couple building and urban scale simulation.
+The research in this paper is part of an\noteDT{s/an/a/} larger coupling effort in which various engines are connected and co-simulated to create a more comprehensive analysis of the urban scale \citep{Dorer:2013vt,Allegrini:2012kx}.
 The target is the computational interface between the building energy model, using EnergyPlus, and the urban energy model using CitySim.
@@
 The campus was modeled in the CitySim simulation engine and co-simulated using work-flow automation.
-The target of this case study is to evaluate the differences between the coupled and uncoupled EnergyPlus simulation results with a target on the use of these models for building retrofit analysis.
-This scenario includes the use of measured data for heating and cooling within their respective seasons to compare to the simulation results.
+The target of this case study is to evaluate the differences between the coupled and uncoupled EnergyPlus simulation results with a target on the use of these models for building retrofit analysis.\noteDT{I do not understand the preceding sentence.
+Neither will the reviewer} This scenario includes the use of measured data for heating and cooling within their respective seasons to compare to the simulation results.
 The second case study is the EPFL campus in Lausanne, Switzerland.
@@
   \item Co-simulate the urban and building scale models through concurrent information exchange
-  \item Implement a simplified calibration procedure based on reconciling the co-simulation output results for a target building that have adequate measured energy performance data from the campus energy information system (EIS)
+  \item Implement a simplified calibration procedure based on reconciling the co-simulation output results for a target building that have\noteDT{s/have/has/} adequate measured energy performance data from the campus energy information system (EIS)
 \end{enumerate}
@@
 The innovation in the current publication is an extension to this research through the modelling and co-simulation of real-world case studies.
-With respect to the third contribution, to the best of the author's knowledge, no previous study has compared the results of a building and urban-scale co-simulation procedure to measured data from a real-world campus.
+With respect to the third contribution, to the best of the author's knowledge, no previous study has compared the results of a building and urban-scale co-simulation procedure to measured data from a real-world campus.\noteDT{:)}
 
@@
 Coupling of building-scale simulation with urban-scale computational fluid dynamics (CFD) is attempted for modeling natural ventilation \citep{Zhang:2013vx} and to improve energy prediction \citep{Bouyer:2011eha}.
-A comprehensive review of energy and airflow modeling of neighborhoods and university campuses was published that includes strategies aspects of coupling different types of models \citep{Srebric:2015gq}.
+A comprehensive review of energy and airflow modeling of neighborhoods and university campuses was published that includes strategies\noteDT{did you mean: "strategic"?} aspects of coupling different types of models \citep{Srebric:2015gq}.
 EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program \citep{Yang:2012cr}.
@@
 EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi} and urban weather generation \citep{Bueno:2013hh}.
-Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}.
+Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}\noteDT{this is not technically a simulation coupling}.
 % \subsection{Urban scale performance simulation}
@@
 \subsection{Coupling process}
-The coupling process of a simplified single zone model and contextual surrounding buildings is outlined in previous studies \citep{thomas2014multiscale,Thomas:2012wj}.
+The coupling process of a simplified single zone model and contextual surrounding buildings is outlined in previous studies \citep{thomas2014multiscale,Thomas:2012wj}\noteDT{not sure the second reference includes coupling...}.
 This study forms the basis for the methodology in the current effort.
@@
 Since the model used by CitySim to simulate a building is more abstract than the model used by EnergyPlus, the EMS is used to aggregate certain values.
-CitySim does not model windows separately, therefore a weighted average of window and wall surface temperatures is calculated with EMS subroutines.
+CitySim does not model windows separately, therefore a weighted average of window and wall surface temperatures is calculated with EMS subroutines.\noteDT{@JK: is this last statement correct?}
 
@@
 The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus, and to receive data from EnergyPlus that are further used within CitySim for the next time steps.
-Several key urban-scale weather variables are sent to EnergyPlus from CitySim in order to better account for the localized effects of surrounding buildings, geography and climactic conditions.
+Several key urban-scale weather variables are sent to EnergyPlus from CitySim in order to better account for the localized effects of surrounding buildings, geography and climactic\noteDT{s/climactic/climatic/} conditions.
 These variables include various outdoor air conditions such as drybulb and wetbulb temperatures, dewpoint, humidity, wind speed and direction, and direct and diffuse solar radiation.
 These variables overwrite the input weather variables that EnergyPlus obtains from its weather file input.
-One of the key objectives of CitySim as a a simulation engine has been its to account for physical phenomenon inherent to urban environments that is often neglected in building-scale simulation environments \citep{Robinson:2004cr,Robinson:2009tm}.
-Long wave radiation exchange between the simulated building and its surroundings is sent to EnergyPlus; this process is describe in detail in a subsequent methodology section.
+One of the key objectives of CitySim as a a\noteDT{s/a a/a/} simulation engine has been its to account for physical phenomenon inherent to urban environments that is often neglected in building-scale simulation environments \citep{Robinson:2004cr,Robinson:2009tm}.\noteDT{this sentence, man.
+i can't even} Long wave radiation exchange between the simulated building and its surroundings is sent to EnergyPlus; this process is describe\noteDT{s/describe/described/} in detail in a subsequent methodology section\noteDT{can we not just name the section?
+this phrasing seems awkward}.
 Finally, CitySim shares its calculated occupancy schedules as it uses a more robust model of occupants behavior \citep{Haldi:2011dr}.
@@
 These variables are transferred due to the ability of EnergyPlus to model more detailed building systems, schedules, ventilation and internal load types than CitySim.
-For example, EnergyPlus is flexible enough to model a detailed, radiant heating and cooling system that would be impossible in CiytSim \cite{barbara:2015tz}.
-EnergyPlus is an engine optimized on the accuracy of building-scale systems, thus CitySim can take advantage of these models through coupling and co-simulation.
+For example, EnergyPlus is flexible enough to model a detailed, radiant heating and cooling system that would be impossible in CiytSim \noteDT{add parenthesis to citation}}\cite{barbara:2015tz}.
+EnergyPlus is an engine optimized on\noteDT{I'm not sure this is proper English.
+Or American for that matter...} the accuracy of building-scale systems, thus CitySim can take advantage of these models through coupling and co-simulation.
 EnergyPlus sends the heating and cooling loads, the surface temperatures of the exterior surfaces and the ventilation flow rates to CitySim.
 
+\noteDT{in table 2: "Values SENT to CitySim..."}
 \begin{table}[H]
@@
 The coupling, simulation and co-simulation process is completely managed within a program called VisTrails \citep{Anonymous:Cayf2tu7}.
-This tool empowers the coupling of various executable files and their connecting scripts in a graphical diagrams that enhances reproducibility and process automation \citep{Freire:2014tt}.
+This tool empowers the coupling of various executable files and their connecting scripts in \noteDT{deleted: "a"} graphical diagrams that enhances reproducibility and process automation \citep{Freire:2014tt}.
 
-INSERT VISTRAILS GRAPHIC HERE\noteCM{Daren -- can you give me a good screenshot of the Vistrails for the HPI building? Pretty please.}
+INSERT VISTRAILS GRAPHIC HERE\noteCM{Daren -- can you give me a good screenshot of the Vistrails for the HPI building? Pretty please.}\noteDT{sure - check out 36-HPI-cosim.pdf in the figures folder}
 
 \subsection{Simplified calibration}
-In the first case study, one aspect of this analysis is the comparison of actual measured performance of a buildings on campus with the simulation results of the co-simulation.
+In the first case study, one aspect of this analysis is the comparison of actual measured performance of a buildings\noteDT{s/buildings/building/} on campus with the simulation results of the co-simulation.
 A simplified calibration procedure is adapted from previous research to compare the measured heating and cooling data available on campus with various simulation scenarios \citep{Samuelson:2015jg}.
@@
 %The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland. 
-The ETH Z\"urich Hoenggerberg campus includes 32 higher education buildings with spaces allocated to laboratories, office space, lecture halls, cafeterias, data centers and other types of similar spaces.
+The ETH Z\"urich Hoenggerberg campus includes 32 higher education \noteDT{deleted: "buildings"} with spaces allocated to laboratories, office space, lecture halls, cafeterias, data centers and other types of similar spaces.
 The campus has a centralized energy management system (EMS) that contains 807 energy and water measurement points from heating, cooling, electricity, city gas, domestic hot water, grey water, and general water consumption.
@@
 The focus of the co-simulation process is that the performance of a targeted building is evaluated through solo and coupled methods.
-The HPI building on campus was chosen in this case study due to amount and quality of measured data available from the EMS for this building.
+The HPI building on campus was chosen in this case study due to \noteDT{insert: "the"} amount and quality of measured data available from the EMS for this building.
 HPI is a 2,610 sq.
-meter building that made up mostly of office space and classrooms.
+meter building that \noteDT{insert: "is"} made up mostly of office space and classrooms.
 It also includes 400 sq.
-meter convenience store and coffee shop.
+meter\noteDT{can we use $m^2$ instead?} convenience store and coffee shop.
 The building is indicated on a campus map shown in Figure \ref{fig:campusmap} and is shaded red.
@@
 This profile is used to set the availability schedules as inputs into the EnergyPlus simulation to emulate the way occupants inhabit the building and how the building management system (BMS) controls the lighting and HVAC systems.
-This approach is compared to the practice of interviews and site visits to determine such input parameters.
+This approach is compared to the practice of interviews and site visits to determine such input parameters.\noteDT{where???
+how???
+i don't get it...}
 
@@
 These metrics fall within the +/-10\% NMBE and +/-30\% CVRSME used in this case study for the purposes of partial calibration.
-The goal of calibration in this case is to simply bring the models to within a reasonable range of reality in order to bring more confidence to analysis of the discrepancies between the solo and co-simulation scenarios.
+The goal of calibration in this case is to simply bring the models to within a reasonable range of reality in order to bring more confidence to analysis of the discrepancies between the solo and co-simulation scenarios.\noteDT{Clayton, can you introduce a consistency in the symbols for the figures?
+say, squares for co-simulation, circles for e+, triangles for measured?
+and do this across all the figures?
+small detail, but i think shows quality and a certain, how shall i call it?
+swissness?
+a qualité suisse?}
 %Daily data was used to calculated goodness of fit to determine calibration success. 
@@
 For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus.
-A 20.2\% decrease in predicted cooling energy is observed as seen in Figure \ref{fig:hpi_energypluscooling}.
+A 20.2\% decrease in \noteDT{with respect to what???} predicted cooling energy is observed as seen in Figure \ref{fig:hpi_energypluscooling}.
 Figure \ref{fig:hpi_energyplusheating} illustrates the difference in predicted heating energy consumption across the test year.
 A consistent offset exists across the time frame of days in January, the peak of the heating season.
-A more varied discrepancy across the heating months is noticed resulting and overall increase of heating prediction of 4.8\% due to co-simulation.
-The exchange of long wave radiation for this particular site is likely greater due to the proximity of surrounding buildings.
+A more varied discrepancy across the heating months is noticed resulting and\noteDT{s/and/in an/} overall increase of heating prediction of 4.8\% due to co-simulation.
+The exchange of long wave radiation for this particular site is likely greater due to \noteDT{greater than what??} the proximity of surrounding buildings.
 These performance differences due to co-simulation are compared to a theoretical single-zone case study in which there was a 15-30\% increase in heating energy and a 4-11\% decrease in cooling energy.
-The results form this scenario are less extreme from the heating side and more extreme from the cooling side.
+The results form\noteDT{s/form/from/} this\noteDT{which?} scenario are less extreme from the heating side and more extreme from\noteDT{from, from, from, you know what?
+there has to be a better way to formulate this sentence} the cooling side.
 
@@
 
-With a particularly strong visual and formal identity, the SwissTech Convention Centre (STCC) is clearly the key protagonist.
-Applied with important functions for the region, the building has definitely become the new landmark.
-Designed as a Minergie building, it includes modern energy conversion technologies to reduce its energy consumption.
+With a particularly strong visual and formal identity, the SwissTech Convention Centre (STCC) is clearly the key protagonist.\noteDT{move main sentence to start of paragraph} Applied with important functions for the region, the building has definitely become the new landmark.
+Designed as a Minergie\noteDT{ref?} building, it includes modern energy conversion technologies to reduce its energy consumption.
 The focus of the co-simulation is realised on the STCC, simulated with the nearby buidings for housing, retail and service areas.
@@
 Besides, it is even more challenging to get the operational data (daily occupancy, lighting and electrical equipment usage level and ventilation rate) as the building has only recently been set in operation mode and as engineers and technicians have been working on improving the controls.
-Therefore, due to unreliable monitoring data, the calibration step of the model has been unfortunately abandoned.\\
+Therefore, due to unreliable monitoring data, the calibration step of the model has been unfortunately\noteDT{delete: "unfortunately".
+we are cold hard scientists battling the evil nemesis that is entropy and his plan to suffocate everyone with the inevitable heat death of the universe.
+we have no time for lame excuses.
+we just abandon.
+no regrets.
+thug life!} abandoned.\\
 
@@
 \includegraphics[width=\textwidth]{figures/model_yang}
-\caption{The Quartier Nord modeled with OpenStudio for Sketchup. The STCC on the left is the main focus of the study and represented by two thermal zones.}
+\caption{The Quartier Nord modeled with OpenStudio for Sketchup\noteDT{s/sketchup/SketchUp/}.
+The STCC on the left is the main focus of the study and \noteDT{insert: "is"} represented by two thermal zones.}
 \label{fig:model_yang}
@@
 The first comparison to observe are the differences between the two engines when focused on the Quartier Nord building.
-When simulated in isolation, the CitySim engine predicts a 28.6\% increase in heating load and a 44.4\% increase in cooling load than EnergyPlus with the model inputs aligned as closely as possible.
+When simulated in isolation, the CitySim engine predicts a 28.6\% increase in heating load and a 44.4\% increase in cooling load than\noteDT{s/than/compared to} EnergyPlus with the model inputs aligned as closely as possible\noteDT{??!
+aligned as closely as possible?
+this is not how we overcome the dark lord.
+can we quantify this?}.
 This phenomenon is due to the differences in the way each of these engines calculates heating and cooling loads.
-Use of the co-simulation process, brings the engines to within 5.4\%.
-Figure \ref{fig:qn_eplusvscitysim_heating} illustrates these differences.
+Use of the co-simulation process,\noteDT{comma-comma-comma, or not} brings the engines to within 5.4\%.
+Figure \ref{fig:qn_eplusvscitysim_heating} illustrates these differences.\noteDT{in the figures that follow, Cosim and CoSim are both used.
+decide.
+then stick to one spelling.
+everywhere.
+notice how i need a break?
+tgif!}
 
@@
 
-When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_cooling}.
+When focusing on\noteDT{delete: "on"} solely \noteDT{what exactly do we mean here?
+solely?} on EnergyPlus, a 7.5\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_cooling}.
 A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}.
 These differences are less prounced that the HPI case study.
-\noteCM{I'm planning to elaborate on these sections but am struggling to interpret the results other than just "co-sim and solo are difference" -- what do you guys think?}
+\noteCM{I'm planning to elaborate on these sections but am struggling to interpret the results other than just "co-sim and solo are difference" -- what do you guys think?}\noteDT{well, for a start, the two case studies differ in the amount of LWR radiation.
+we could quantify that?
+also, the number of surfaces of the e+ model with viewfactor to surrounding buildings?}
 
@@
 
-When focusing on solely on CitySim, a 26.9\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}.
+When focusing on\noteDT{delte: "on"} solely on CitySim, a 26.9\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}.
 A 49.1\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}.
@@
 This paper has outlined two such scenarios in which the building-focused EnergyPlus simulation engine is coupled and co-simulated with the urban-scale CitySim engine.
-This process is implemented through a fully automated work flow process that extract geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each timestep of targeted variables, and accumulates the results for analysis.
+This process is implemented through a fully automated work flow process that extract\noteDT{s/extract/extracts/} geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each timestep of targeted variables, and accumulates the results for analysis.
 The process has been implemented on simplified theoretical scenarios in the past and the key innovation with this work is in implementation on actual case study campuses and targeted buildings.
@@
 The authors would like to acknowledge the ETH Z\"urich Campus Facilities Department and the EPFL Real Estate and Infrastructure Department.
-This research was funded by the Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale Energy Modeling (UMEM) project.
+This research was funded by the Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale Energy Modeling (UMEM) project.\noteDT{We also want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}
 

### 2016-04-25 latex/UMEM_CoSim.tex
Fixed a bunch of stuff Daren suggested

@@
-% tBPSguide.tex
-% v2.1 released November 2014
+% tBPSguide.tex v2.1 released November 2014
 
@@
 \usepackage{lineno}
+\RequirePackage{fix-cm}
 
@@
 \begin{abstract}
-    This paper describes the co-simulation process of the building and urban scale models of two campuses of higher education buildings in Switzerland.
-The campuses are modeled at both the building scale using the EnergyPlus simulation engine and at the urban scale using the CitySim engine.
-A co-simulation framework is used to execute simulations from both engines concurrently with an exchange of information to leverage the various strengths of each.
-In the first case study, on-site weather and measured performance data is then compared to the output from two modeling scenarios: building-scale simulation using EnergyPlus and co-simulation of the engines.
-A partial calibration process is implemented to reconcile the simulations with the measured data \noteDT{insert: "of"} a targeted office building on campus.
-In the second case study, the co-simulation results are compared to the both the CitySim simulation and EnergyPlus engines.
-The results show that {\color{red}insert results here}.
-A discussion is included of the challenges encountered with the urban scale calibration and the strengths and weaknesses of the developed process.\noteDT{Clayton, can you get your editor to do hard linewrapping?
-all your paragraphs are a single line which breaks the diff model of GitHub and makes editing in VIM super hard...}
+    This paper describes the co-simulation process of the building and urban
+    scale models of two campuses of higher education buildings in Switzerland.
+    The campuses are modeled at both the building scale using the EnergyPlus
+    simulation engine and at the urban scale using the CitySim engine. A co-
+    simulation framework is used to execute simulations from both engines
+    concurrently with an exchange of information to leverage the various
+    strengths of each. In the first case study, on-site weather and measured
+    performance data is then compared to the output from two modeling
+    scenarios: building-scale simulation using EnergyPlus and co-simulation of
+    the engines. A partial calibration process is implemented to reconcile the
+    simulations with the measured data of a targeted office building on
+    campus. In the second case study, the co-simulation results are compared
+    to the both the CitySim simulation and EnergyPlus engines. The results
+    show that {\color{red}insert results here}. A discussion is included of
+    the challenges encountered with the urban scale calibration and the
+    strengths and weaknesses of the developed process.
+    % \noteDT{Clayton, can you
+    % get your editor to do hard linewrapping? all your paragraphs are a single
+    % line which breaks the diff model of GitHub and makes editing in VIM super
+    % hard...}
 \end{abstract}
@@
 
-Urban scale building performance simulation is a process that empowers the analysis and optimization of cities.
-Urban populations are growing around the world at an unprecedented rate.
-A shift from urban to rural is underway and 2.5 billion people are expected to join urban centers throughout the world \citep{UnitedNations:2014vn}.
-Expansions of entire districts and even cities is not an uncommon phenomenon, especially in East Asia and Africa.
-Urban scale modeling is in the midst of a strong focus within the research community with six key areas of practice: technology design, building design, urban climate, systems design, policy assessment, and land use and transportation \citep{Keirstead:2012ct}.
-The ability to simulate the interaction between large collections of buildings enables the development and testing of optimization and planning scenarios for this new development \citep{Dorer:2013vt}.
+Urban scale building performance simulation is a process that empowers the
+analysis and optimization of cities. Urban populations are growing around the
+world at an unprecedented rate. A shift from urban to rural is underway and
+2.5 billion people are expected to join urban centers throughout the world
+\citep{UnitedNations:2014vn}. Expansions of entire districts and even cities
+is not an uncommon phenomenon, especially in East Asia and Africa. Urban scale
+modeling is in the midst of a strong focus within the research community with
+six key areas of practice: technology design, building design, urban climate,
+systems design, policy assessment, and land use and transportation
+\citep{Keirstead:2012ct}. The ability to simulate the interaction between
+large collections of buildings enables the development and testing of
+optimization and planning scenarios for this new development
+\citep{Dorer:2013vt}.
 
-The CitySim simulation engine is an example of such a program designed and optimized for urban-scale simulation.
-CitySim is an urban performance simulation engine that comprises a Solver module as well as a graphical user interface.
-It focuses on the energy flows of multiple simplified building models and their interdependent relationship with their urban climate \citep{Robinson:2009tm}.
-CitySim includes building thermal, urban radiation, occupant behavior, and plant/equipment models integrated as a single simulation engine.
-CitySim simulates multiple buildings up to city scale using simplified models in order to achieve a good compromise between modeling accuracy, computational overheads and data availability.
-Each building's thermal behavior is based on an electrical analogy using a two node resistor-capacitor network.
-The internal lighting, people, and miscellaneous loads are modeled using a simplified occupancy-based approximation.
-The heating, ventilation, and air-conditioning (HVAC) systems are modeled using a single equation that approximates the total mass flow rate required to meet the sensible and latent loads of each building as a whole.
-Each of these simplifying approximations empowers the urban-scale simulation to have reasonable execution times with respect to the number of buildings being simulated.
+The CitySim simulation engine is an example of such a program designed and
+optimized for urban-scale simulation. CitySim is an urban performance
+simulation engine that comprises a Solver module as well as a graphical user
+interface. It focuses on the energy flows of multiple simplified building
+models and their interdependent relationship with their urban climate
+\citep{Robinson:2009tm}. CitySim includes building thermal, urban radiation,
+occupant behavior, and plant/equipment models integrated as a single
+simulation engine. CitySim simulates multiple buildings up to city scale using
+simplified models in order to achieve a good compromise between modeling
+accuracy, computational overheads and data availability. Each building's
+thermal behavior is based on an electrical analogy using a two node resistor-
+capacitor network. The internal lighting, people, and miscellaneous loads are
+modeled using a simplified occupancy-based approximation. The heating,
+ventilation, and air-conditioning (HVAC) systems are modeled using a single
+equation that approximates the total mass flow rate required to meet the
+sensible and latent loads of each building as a whole. Each of these
+simplifying approximations empowers the urban-scale simulation to have
+reasonable execution times with respect to the number of buildings being
+simulated.
 
-Building performance simulation is a mature domain of research relative to urban scale efforts.
-The use of whole building simulation engines originated in the 1960s with the US government's development of the BLAST and DOE-2 hourly energy simulation programs \citep{Lawrie:2001vf}.
-In 1996, development on a new simulation engine, EnergyPlus, began in order to combine the advantages of previous efforts in a single, modular program.
-EnergyPlus, as a result, has become a popular choice in detailed whole-building performance simulation due to the breadth of mechanical, renewable, and electrical systems that can be modeled.
-EnergyPlus specifically excels in its ability to model unique mechanical system types such as decoupled centralized cooling \citep{Miller:2010wa} and low exergy heating and cooling systems \citep{barbara:2015tz}.
-Additionally, EnergyPlus is designed to provide a high resolution in which internal loads and natural ventilation technologies can be modeled in detail at the building level.
+Building performance simulation is a mature domain of research relative to
+urban scale efforts. The use of whole building simulation engines originated
+in the 1960s with the US government's development of the BLAST and DOE-2
+hourly energy simulation programs \citep{Lawrie:2001vf}. In 1996, development
+on a new simulation engine, EnergyPlus, began in order to combine the
+advantages of previous efforts in a single, modular program. EnergyPlus, as a
+result, has become a popular choice in detailed whole-building performance
+simulation due to the breadth of mechanical, renewable, and electrical systems
+that can be modeled. EnergyPlus specifically excels in its ability to model
+unique mechanical system types such as decoupled centralized cooling
+\citep{Miller:2010wa} and low exergy heating and cooling systems
+\citep{barbara:2015tz}. Additionally, EnergyPlus is designed to provide a high
+resolution in which internal loads and natural ventilation technologies can be
+modeled in detail at the building level.
 
-Both building and urban-scale simulation domains have rightfully chosen boundary conditions that reflect their key goals while seeking to minimize the input parameters necessary and run-times of the engines themselves.
-This focus results in certain deficiencies with respect to modeling various phenomenon.
-For example, urban scale simulation highly simplifies the building systems and internal load models, thus making retrofit analysis at the systems level difficult.
-And whole building simulation neglects many of the various contextual consideration of the urban environment such as long wave radiation exchange with adjacent surfaces and localized urban weather effects.\noteDT{ref?}
+Both building and urban-scale simulation domains have rightfully chosen
+boundary conditions that reflect their key goals while seeking to minimize the
+input parameters necessary and run-times of the engines themselves. This focus
+results in certain deficiencies with respect to modeling various phenomenon.
+For example, urban scale simulation highly simplifies the building systems and
+internal load models, thus making retrofit analysis at the systems level
+difficult. And whole building simulation in EnergyPlus neglects many of the
+various contextual consideration of the urban environment such as long wave
+radiation exchange with adjacent surfaces and localized urban weather effects
+\citep{Lawrie:2001vf}.%\noteDT{ref?}
 
-In order to address the deficiencies of the individual engines, the current effort described\noteDT{can we do phrasing?
-prettyplease?} seeks to couple building and urban scale simulation.
-The research in this paper is part of an\noteDT{s/an/a/} larger coupling effort in which various engines are connected and co-simulated to create a more comprehensive analysis of the urban scale \citep{Dorer:2013vt,Allegrini:2012kx}.
-The target is the computational interface between the building energy model, using EnergyPlus, and the urban energy model using CitySim.
-An overview of the larger scope is shown in Figure \ref{fig:UMEM} and the context of the coupling task is shown as the interface between the City Energy Simulation (CES) model and the Building Energy Simulation (BES) model.
+In order to address the deficiencies of the individual engines, the current
+effort seeks to couple building and urban scale simulation. The research in
+this paper is part of an\noteDT{s/an/a/} larger coupling effort in which
+various engines are connected and co-simulated to create a more comprehensive
+analysis of the urban scale \citep{Dorer:2013vt,Allegrini:2012kx}. The target
+is the computational interface between the building energy model, using
+EnergyPlus, and the urban energy model using CitySim. An overview of the
+larger scope is shown in Figure \ref{fig:UMEM} and the context of the coupling
+task is shown as the interface between the City Energy Simulation (CES) model
+and the Building Energy Simulation (BES) model.
 
-The coupling and co-simulation process is implemented on two case studies in Switzerland.
-The first case study is the ETH Z\"urich Hoenggerberg campus in Z\"urich, Switzerland.
-The campus was modeled in the CitySim simulation engine and co-simulated using work-flow automation.
-The target of this case study is to evaluate the differences between the coupled and uncoupled EnergyPlus simulation results with a target on the use of these models for building retrofit analysis.\noteDT{I do not understand the preceding sentence.
-Neither will the reviewer} This scenario includes the use of measured data for heating and cooling within their respective seasons to compare to the simulation results.
-The second case study is the EPFL campus in Lausanne, Switzerland.
-The objective of this scenario is to evaluate the differences between coupled and uncoupled versions of the CitySim simulation engine.
+% \noteDT{can we do phrasing? prettyplease?}
+
+The coupling and co-simulation process is implemented on two case studies in
+Switzerland. The first case study is the ETH Z\"urich Hoenggerberg campus in
+Z\"urich, Switzerland. The campus was modeled in the CitySim simulation engine
+and co-simulated using work-flow automation. The target of this case study is
+to evaluate the differences between the coupled and solo EnergyPlus
+simulations based on the variables exchanged. This scenario includes the use
+of measured data for heating and cooling within their respective seasons to
+compare to the simulation results. The second case study is the EPFL campus in
+Lausanne, Switzerland. The objective of this scenario is to evaluate the
+differences between coupled and uncoupled versions of the CitySim simulation
+engine.
+
+ % with a target on the use of these models for building retrofit analysis.\noteDT{I do not understand the preceding sentence. Neither will the reviewer}
 
@@
 \includegraphics[scale=0.7]{figures/UMEM_overview_new}
-\caption{EnergyPlus and CitySim coupling are part of the wider context.
-Each block in the diagram represents an environment, with the tool/engine name in italics (\citep{thomas2014multiscale}, adapted from \citep{Dorer:2013vt})}
+\caption{EnergyPlus and CitySim coupling are part of the wider context. Each
+block in the diagram represents an environment, with the tool/engine name in
+italics (\citep{thomas2014multiscale}, adapted from \citep{Dorer:2013vt})}
 \label{fig:UMEM}
@@
 \begin{enumerate}
-  \item Automation of the process of simultaneous meta-data extraction from a building information model (BIM) for the creation of both building and urban-scale performance models for a real-world campus of buildings
+  \item Automation of the process of simultaneous meta-data extraction from a
+  building information model (BIM) for the creation of both building and
+  urban-scale performance models for a real-world campus of buildings
   \item Co-simulate the urban and building scale models through concurrent information exchange
-  \item Implement a simplified calibration procedure based on reconciling the co-simulation output results for a target building that have\noteDT{s/have/has/} adequate measured energy performance data from the campus energy information system (EIS)
+  \item Implement a simplified calibration procedure based on reconciling the
+  co-simulation output results for a target building using measured energy
+  performance data from the campus energy information system (EIS)
 \end{enumerate}
 
-The first two objectives have been demonstrated in a simplified context in previous literature \citep{thomas2014multiscale,Miller:2015vk}.
-The innovation in the current publication is an extension to this research through the modelling and co-simulation of real-world case studies.
-With respect to the third contribution, to the best of the author's knowledge, no previous study has compared the results of a building and urban-scale co-simulation procedure to measured data from a real-world campus.\noteDT{:)}
+% \noteDT{s/have/has/}
+
+The first two objectives have been demonstrated in a simplified context in
+previous literature \citep{thomas2014multiscale,Miller:2015vk}. The innovation
+in the current publication is an extension to this research through the
+modelling and co-simulation of real-world case studies. With respect to the
+third contribution, to the best of the authors' knowledge, no previous study
+has compared the results of a building and urban-scale co-simulation procedure
+to measured data from a real-world campus.% \noteDT{:)}
 
 \subsection{Previous multi-scale coupling studies}
-Previous attempts of information exchange have been implemented between simulation engines at various scales.
-Much of the initial co-simulation work in the literature is at the subsystem and building-scales.
-Previous studies have analyzed strong and loose coupling of engines at this scale \citep{Trcka:2010cr,Wetter:2011kh}.
-Coupling of building-scale simulation with urban-scale computational fluid dynamics (CFD) is attempted for modeling natural ventilation \citep{Zhang:2013vx} and to improve energy prediction \citep{Bouyer:2011eha}.
-A comprehensive review of energy and airflow modeling of neighborhoods and university campuses was published that includes strategies\noteDT{did you mean: "strategic"?} aspects of coupling different types of models \citep{Srebric:2015gq}.
-EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program \citep{Yang:2012cr}.
-It was also coupled with simplified lumped parameter models in order to facilitate comparison with measured sensor data \citep{Martin:2015fj}.
-EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi} and urban weather generation \citep{Bueno:2013hh}.
-Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}\noteDT{this is not technically a simulation coupling}.
+Previous attempts of information exchange have been implemented between
+simulation engines at various scales. Much of the initial co-simulation work
+in the literature is at the subsystem and building-scales. Previous studies
+have analyzed strong and loose coupling of engines at this scale
+\citep{Trcka:2010cr,Wetter:2011kh}. Coupling of building-scale simulation with
+urban-scale computational fluid dynamics (CFD) is attempted for modeling
+natural ventilation \citep{Zhang:2013vx} and to improve energy prediction
+\citep{Bouyer:2011eha}. A comprehensive review of energy and airflow modeling
+of neighborhoods and university campuses was published that includes
+strategic aspects of coupling different %\noteDT{did you mean: "strategic"?}b
+types of models \citep{Srebric:2015gq}. EnergyPlus has been coupled with ENVI-
+met, a micro-climate computational fluid dynamics (CFD) program
+\citep{Yang:2012cr}. It was also coupled with simplified lumped parameter
+models in order to facilitate comparison with measured sensor data
+\citep{Martin:2015fj}. EnergyPlus and the TEP Urban Canopy Model program were
+coupled in order to quantify the influences of urban localized weather effects
+on whole building simulation \citep{Bueno:2011hi} and urban weather generation
+\citep{Bueno:2013hh}.
+% Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}\noteDT{this is not technically a simulation coupling}.
 % \subsection{Urban scale performance simulation}
@@
 
-\subsection{Coupling process}
-The coupling process of a simplified single zone model and contextual surrounding buildings is outlined in previous studies \citep{thomas2014multiscale,Thomas:2012wj}\noteDT{not sure the second reference includes coupling...}.
-This study forms the basis for the methodology in the current effort.
-This process utilizes the Design Performance Viewer (DPV) and associated work flow.
-The DPV is a tool written to extract and simulate an EnergyPlus input data file (IDF) from an Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM \citep{Schlueter2009}.
-The main philosophy behind the tool is rapid simulation of the building information model from the earliest design possible and can be used throughout the life-cycle of the building including retrofit analysis \citep{Miller:2014tu}.
-This process is achieved by augmenting the information in the BIM with default values and abstracting information not relevant for energy simulation.
-The tool already has a simplified notion of surrounding buildings, which are modeled in the BIM as simple mass objects without further information and are exported as shading surfaces to EnergyPlus.
-This functionality is used for creating the CitySim mass scene and leads to a crude model of the urban context of the building.
-The existing DPV philosophy of allowing the designer to iterate rapidly on early design decisions based on feedback about the performance of the design remains.
-This approach includes streamlining the process where running a simulation requires no effort from the designer due to automatic creation of input files, execution and analysis of the results.
+\subsection{Coupling process} The coupling process of a simplified single zone
+model and contextual surrounding buildings is outlined in previous studies
+\citep{thomas2014multiscale}. This study forms the basis for the methodology
+in the current effort. This process utilizes the Design Performance Viewer
+(DPV) and associated work flow. The DPV is a tool written to extract and
+simulate an EnergyPlus input data file (IDF) from an
+Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM
+\citep{Schlueter2009}. The main philosophy behind the tool is rapid simulation
+of the building information model from the earliest design possible and can be
+used throughout the life-cycle of the building including retrofit analysis
+\citep{Miller:2014tu}. This process is achieved by augmenting the information
+in the BIM with default values and abstracting information not relevant for
+energy simulation. The tool already has a simplified notion of surrounding
+buildings, which are modeled in the BIM as simple mass objects without further
+information and are exported as shading surfaces to EnergyPlus. This
+functionality is used for creating the CitySim mass scene and leads to a crude
+model of the urban context of the building. The existing DPV philosophy of
+allowing the designer to iterate rapidly on early design decisions based on
+feedback about the performance of the design remains. This approach includes
+streamlining the process where running a simulation requires no effort from
+the designer due to automatic creation of input files, execution and analysis
+of the results.% \noteDT{not sure the second reference includes coupling...}
 
-The coupling process of EnergyPlus and CitySim is shown in Figure \ref{fig:OverallWorkflowProcess}.
-First, the DPV is used to extract an EnergyPlus simulation model from the BIM.
-The DPV utilizes the Revit API to extract geometrical information about the building and the physical properties of walls, windows, doors, roofs and floors.
-This information is encoded in the BIM model as wall types, roof types, floor types as well as window and door families.
-Wherever possible, the tool uses the layering and materials of the construction types, enhancing them with physical attributes relevant to EnergyPlus.
-Where not defined, it assumes default values.
+The coupling process of EnergyPlus and CitySim is shown in Figure
+\ref{fig:OverallWorkflowProcess}. First, the DPV is used to extract an
+EnergyPlus simulation model from the BIM. The DPV utilizes the Revit API to
+extract geometrical information about the building and the physical properties
+of walls, windows, doors, roofs and floors. This information is encoded in the
+BIM model as wall types, roof types, floor types as well as window and door
+families. Wherever possible, the tool uses the layering and materials of the
+construction types, enhancing them with physical attributes relevant to
+EnergyPlus. Where not defined, it assumes default values.
 
@@
 
-Next, geometry is created to be used in both the CitySim and EnergyPlus models as buildings and surfaces surrounding the building targeted in the IDF.
-This feature of the DPV is used for including shading surfaces in the EnergyPlus simulation model: it uses so-called \emph{mass objects} in the BIM model as surrounding buildings.
-The DPV model views these buildings as a series of shading surfaces.
-A transformation is added on the DPV model that produces an input file for the CitySim solver.
-This file uses an XML format describing the buildings in a scene for simulation, including their construction types, geometry and systems for heating and cooling.
-The main BIM is extracted to the CitySim scene as one of the buildings to be simulated, with the properties of the construction types matching those in the DPV model.
-The glazing ratio is calculated based on the window and wall areas of the DPV model.
-Shading surfaces are grouped into buildings based on the mass object they were extracted from.
-These neighboring buildings use default construction properties for walls and roofs and we assign them a default glazing ratio.
-These defaults can be overridden by custom properties applied to the mass objects in the BIM much in the same way as the model elements of the main building are enriched with DPV information.
+Next, geometry is created to be used in both the CitySim and EnergyPlus models
+as buildings and surfaces surrounding the building targeted in the IDF. This
+feature of the DPV is used for including shading surfaces in the EnergyPlus
+simulation model: it uses so-called \emph{mass objects} in the BIM model as
+surrounding buildings. The DPV model views these buildings as a series of
+shading surfaces. A transformation is added on the DPV model that produces an
+input file for the CitySim solver. This file uses an XML format describing the
+buildings in a scene for simulation, including their construction types,
+geometry and systems for heating and cooling. The main BIM is extracted to the
+CitySim scene as one of the buildings to be simulated, with the properties of
+the construction types matching those in the DPV model. The glazing ratio is
+calculated based on the window and wall areas of the DPV model. Shading
+surfaces are grouped into buildings based on the mass object they were
+extracted from. These neighboring buildings use default construction
+properties for walls and roofs and we assign them a default glazing ratio.
+These defaults can be overridden by custom properties applied to the mass
+objects in the BIM much in the same way as the model elements of the main
+building are enriched with DPV information.
 
-As of version 8.1.0, EnergyPlus supports exporting a simulation model as a Functional Mock-up Unit (FMU) \citep{Nouidui:2014hq,Anonymous:ZZTfF80-}.
-This feature introduces new IDF objects to specify the interface such an FMU exposes.
-These objects define which output variables are exported by the FMU and which variables are imported.
-The FMU export functionality is closely linked to the Energy Management System (EMS) of EnergyPlus.
-Co-simulation exchange variables either mimic an EnergyPlus schedule, an EMS variable or drive an EMS actuator.
-Since the model used by CitySim to simulate a building is more abstract than the model used by EnergyPlus, the EMS is used to aggregate certain values.
-CitySim does not model windows separately, therefore a weighted average of window and wall surface temperatures is calculated with EMS subroutines.\noteDT{@JK: is this last statement correct?}
+As of version 8.1.0, EnergyPlus supports exporting a simulation model as a
+Functional Mock-up Unit (FMU) \citep{Nouidui:2014hq,Anonymous:ZZTfF80-}. This
+feature introduces new IDF objects to specify the interface such an FMU
+exposes. These objects define which output variables are exported by the FMU
+and which variables are imported. The FMU export functionality is closely
+linked to the Energy Management System (EMS) of EnergyPlus. Co-simulation
+exchange variables either mimic an EnergyPlus schedule, an EMS variable or
+drive an EMS actuator. Since the model used by CitySim to simulate a building
+is more abstract than the model used by EnergyPlus, the EMS is used to
+aggregate certain values. CitySim does not model windows separately, therefore
+a weighted average of window and wall surface temperatures is calculated with
+EMS subroutines.\noteDT{@JK: is this last statement correct?}
 
@@
 
-The FMU creation process is the basis for coupling the two models at each timestep in the simulation.
-Figure \ref{fig:FMUOverview} illustrates this process from both the EnergyPlus and CitySim perspective.
-The augmented IDF file is fed to the \emph{EnergyPlusToFMI} script \citep{Nouidui:2014bo}.
-Once configured, this script produces an FMU file based on the augmented IDF file and the weather file to be used as well as a DLL file implementing the Functional Mock-up Interface that can load the IDF file, locate EnergyPlus and run the simulation.
+The FMU creation process is the basis for coupling the two models at each
+timestep in the simulation. Figure \ref{fig:FMUOverview} illustrates this
+process from both the EnergyPlus and CitySim perspective. The augmented IDF
+file is fed to the \emph{EnergyPlusToFMI} script \citep{Nouidui:2014bo}. Once
+configured, this script produces an FMU file based on the augmented IDF file
+and the weather file to be used as well as a DLL file implementing the
+Functional Mock-up Interface that can load the IDF file, locate EnergyPlus and
+run the simulation.
 
@@
 The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus, and to receive data from EnergyPlus that are further used within CitySim for the next time steps.
-Several key urban-scale weather variables are sent to EnergyPlus from CitySim in order to better account for the localized effects of surrounding buildings, geography and climactic\noteDT{s/climactic/climatic/} conditions.
-These variables include various outdoor air conditions such as drybulb and wetbulb temperatures, dewpoint, humidity, wind speed and direction, and direct and diffuse solar radiation.
-These variables overwrite the input weather variables that EnergyPlus obtains from its weather file input.
-One of the key objectives of CitySim as a a\noteDT{s/a a/a/} simulation engine has been its to account for physical phenomenon inherent to urban environments that is often neglected in building-scale simulation environments \citep{Robinson:2004cr,Robinson:2009tm}.\noteDT{this sentence, man.
-i can't even} Long wave radiation exchange between the simulated building and its surroundings is sent to EnergyPlus; this process is describe\noteDT{s/describe/described/} in detail in a subsequent methodology section\noteDT{can we not just name the section?
-this phrasing seems awkward}.
-Finally, CitySim shares its calculated occupancy schedules as it uses a more robust model of occupants behavior \citep{Haldi:2011dr}.
+Several key urban-scale weather variables are sent to EnergyPlus from CitySim
+in order to better account for the localized effects of surrounding buildings,
+geography and climate conditions. These variables include various outdoor air
+conditions such as drybulb and wetbulb temperatures, dewpoint, humidity, wind
+speed and direction, and direct and diffuse solar radiation. These variables
+overwrite the input weather variables that EnergyPlus obtains from its weather
+file input. CitySim is designed to account for physical phenomenon inherent to
+urban environments, that are often neglected in building-scale simulation
+environments \citep{Robinson:2004cr,Robinson:2009tm}. Long wave radiation
+exchange between the simulated building and its surroundings is sent to
+EnergyPlus; this process is describe\noteDT{s/describe/described/} in detail
+in a subsequent methodology section\noteDT{can we not just name the section?
+this phrasing seems awkward}. Finally, CitySim shares its calculated occupancy
+schedules as it uses a more robust model of occupants behavior
+\citep{Haldi:2011dr}.
+
+% \noteDT{s/climactic/climatic/}
+% \noteDT{this sentence, man. i can't even}
 
@@
 
-Variables sent to CitySim by EnergyPlus at each time step include several variables related to the calculation of heating and cooling loads of a targeted building.
-These variables are transferred due to the ability of EnergyPlus to model more detailed building systems, schedules, ventilation and internal load types than CitySim.
-For example, EnergyPlus is flexible enough to model a detailed, radiant heating and cooling system that would be impossible in CiytSim \noteDT{add parenthesis to citation}}\cite{barbara:2015tz}.
-EnergyPlus is an engine optimized on\noteDT{I'm not sure this is proper English.
-Or American for that matter...} the accuracy of building-scale systems, thus CitySim can take advantage of these models through coupling and co-simulation.
-EnergyPlus sends the heating and cooling loads, the surface temperatures of the exterior surfaces and the ventilation flow rates to CitySim.
+Variables sent to CitySim by EnergyPlus at each time step include several
+variables related to the calculation of heating and cooling loads of a
+targeted building. These variables are transferred due to the ability of
+EnergyPlus to model more detailed building systems, schedules, ventilation and
+internal load types than CitySim. For example, EnergyPlus is flexible enough
+to model a detailed, radiant heating and cooling system that would be
+impossible in CiytSim \citep{barbara:2015tz}. EnergyPlus is an engine
+optimized to accurately model building-scale systems, thus CitySim can take 
+advantage of these models through coupling and co-simulation. EnergyPlus sends
+the heating and cooling loads, the surface temperatures of the exterior
+surfaces and the ventilation flow rates to CitySim.
+
+%\noteDT{I'm not sure this is proper English. Or American for that
+%matter...}
 
@@
 
-Long wave radiation exchange in the urban scale environment is coupled in the co-simulation process and it requires the development of a set of approximations to reduce the number of coupled variables between the engines and to account for differences in the methods by which each engine calculates this metric.
-A detailed description of Long Wave Radiation (LWR) variable exchange and approximation is found in a previously published study \citep{Miller:2015vk} on a simplified theoretical case.
+Long wave radiation exchange in the urban scale environment is coupled in the
+co-simulation process and it requires the development of a set of
+approximations to reduce the number of coupled variables between the engines
+and to account for differences in the methods by which each engine calculates
+this metric. A detailed description of Long Wave Radiation (LWR) variable
+exchange and approximation is found in a previously published study
+\citep{Miller:2015vk} on a simplified theoretical case.
 
-In EnergyPlus, LWR exchange for a surface is calculated through the summation of radiation gain from the ground, sky, and air as seen in Equation \ref{EPlus_LWR_Ext} and Figure \ref{combinedLWR}a \citep{doe2010energyplus}.
-The radiant heat transfer coefficient for each of these environmental variables is calculated according to Equation \ref{EPlus_h} with $\sigma$ as the Stefan-Boltzmann constant and $\epsilon$ as the emissivity.
-A major assumption of this approach is that the modeled building's surfaces and those of adjacent buildings are at a uniform temperature and the LWR radiation exchange is negligible; a situation that is an oversimplification in an urban
+In EnergyPlus, LWR exchange for a surface is calculated through the summation
+of radiation gain from the ground, sky, and air as seen in Equation
+\ref{EPlus_LWR_Ext} and Figure \ref{combinedLWR}a \citep{doe2010energyplus}.
+The radiant heat transfer coefficient for each of these environmental
+variables is calculated according to Equation \ref{EPlus_h} with $\sigma$ as
+the Stefan-Boltzmann constant and $\epsilon$ as the emissivity. A major
+assumption of this approach is that the modeled building's surfaces and those
+of adjacent buildings are at a uniform temperature and the LWR radiation
+exchange is negligible; a situation that is an oversimplification in an urban
 scale domain \citep{Evins:2014cf}.
@@
 
-In comparison, CitySim calculates LWR exchange by calculating an aggregated equivalent temperature, $T_{env}$, and radiative heat transfer coefficient, $h_{r,env}$, from surrounding urban surfaces in addition to ground, sky, and air \citep{Robinson:2009tm}.
-The calculation for $T_{env}$ is expressed in Equation \ref{CitySim_Tenv} with the $F$ values being view factors of the surrounding environment including adjacent surfaces $i=1..n$.
-$h_{r,env}$ is based on a first order Talyor development of the numerator of Equation \ref{EPlus_h} around $(T_{surf}+T_{variable})/2$ and therefore $Q_{LWR,CitySim}$ is calculated using Equation \ref{CitySim_LWR_Ext}.
+In comparison, CitySim calculates LWR exchange by calculating an aggregated
+equivalent temperature, $T_{env}$, and radiative heat transfer coefficient,
+$h_{r,env}$, from surrounding urban surfaces in addition to ground, sky, and
+air \citep{Robinson:2009tm}. The calculation for $T_{env}$ is expressed in
+Equation \ref{CitySim_Tenv} with the $F$ values being view factors of the
+surrounding environment including adjacent surfaces $i=1..n$. $h_{r,env}$ is
+based on a first order Talyor development of the numerator of Equation
+\ref{EPlus_h} around $(T_{surf}+T_{variable})/2$ and therefore
+$Q_{LWR,CitySim}$ is calculated using Equation \ref{CitySim_LWR_Ext}.
+
 \begin{equation} \label{CitySim_Tenv} 
@@
 
-In the coupled simulation, EnergyPlus uses the CitySim supplied equivalent $h_{r,env}$ and $T_{env}$ to calculate weighted $h_{r,sky}$, $h_{r,grd}$, and $h_{r,air}$ values using the view factors and the sky-to-air split ratio.
-Figure \ref{combinedLWR} illustrates the schematic differences between the solo and coupled simulations on a theoretical example of a target building with two adjacent buildings with surfaces available for radiation exchange.
+In the coupled simulation, EnergyPlus uses the CitySim supplied equivalent
+$h_{r,env}$ and $T_{env}$ to calculate weighted $h_{r,sky}$, $h_{r,grd}$, and
+$h_{r,air}$ values using the view factors and the sky-to-air split ratio.
+Figure \ref{combinedLWR} illustrates the schematic differences between the
+solo and coupled simulations on a theoretical example of a target building
+with two adjacent buildings with surfaces available for radiation exchange.
 
@@
 \subsection{Work flow automation}
-The coupling, simulation and co-simulation process is completely managed within a program called VisTrails \citep{Anonymous:Cayf2tu7}.
-This tool empowers the coupling of various executable files and their connecting scripts in \noteDT{deleted: "a"} graphical diagrams that enhances reproducibility and process automation \citep{Freire:2014tt}.
+The coupling, simulation and co-simulation process is completely managed
+within a program called VisTrails \citep{Anonymous:Cayf2tu7}. This tool
+empowers the coupling of various executable files and their connecting scripts
+in graphical diagrams that enhances reproducibility and
+process automation \citep{Freire:2014tt}.
 
-INSERT VISTRAILS GRAPHIC HERE\noteCM{Daren -- can you give me a good screenshot of the Vistrails for the HPI building? Pretty please.}\noteDT{sure - check out 36-HPI-cosim.pdf in the figures folder}
+% INSERT VISTRAILS GRAPHIC HERE\noteCM{Daren -- can you give me a good screenshot of the Vistrails for the HPI building? Pretty please.}\noteDT{sure - check out 36-HPI-cosim.pdf in the figures folder}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/36-cosim-HPI}
+  \caption{Workflow in VizTrails
+  \label{VizTrails}}
+\end{figure}
 
 \subsection{Simplified calibration}
-In the first case study, one aspect of this analysis is the comparison of actual measured performance of a buildings\noteDT{s/buildings/building/} on campus with the simulation results of the co-simulation.
-A simplified calibration procedure is adapted from previous research to compare the measured heating and cooling data available on campus with various simulation scenarios \citep{Samuelson:2015jg}.
-This calibration procedure was utilized in the performance reconciliation of 18 buildings that were built according to the LEED Canada protocol and were under review of actualized performance.
-This protocol is unique in its analysis process to uncover design model deficiencies in a step-wise manner, utilizing the most easily accessible knowledge first and working towards equilibrium between measured and simulated.
-An appropriate balance between effort of implementation and value generated through the calibration process.
+In the first case study, one aspect of this analysis is the comparison of
+actual measured performance of the target building on campus with the
+simulation results of the co-simulation. A simplified calibration procedure is
+adapted from previous research to compare the measured heating and cooling
+data available on campus with various simulation scenarios
+\citep{Samuelson:2015jg}. This calibration procedure was utilized in the
+performance reconciliation of 18 buildings that were built according to the
+LEED Canada protocol and were under review of actualized performance. This
+protocol is unique in its analysis process to uncover design model
+deficiencies in a step-wise manner, utilizing the most easily accessible
+knowledge first and working towards equilibrium between measured and
+simulated. An appropriate balance between effort of implementation and value
+generated through the calibration process.
 
@@
 The first is the ETH Z\"urich Hoenggerberg campus in Z\"urich, Switzerland.
-The focus of this case study is to compare the impact of the information exchange through co-simulation within the EnergyPlus engine.
-The intent on this campus was to develop techniques for retrofit analysis using EnergyPlus.
-The targeted building on this campus is the HPI Building.
-Raw measured data is available for many of the buildings on campus, thus a simplified calibration procedure is used to reconcile the simulation results.\\
+The focus of this case study is to compare the impact of the information
+exchange through co-simulation within the EnergyPlus engine. The intent on
+this campus was to develop techniques for retrofit analysis using EnergyPlus.
+The targeted building on this campus is the HPI Building. Raw measured data is
+available for many of the buildings on campus, thus a simplified calibration
+procedure is used to reconcile the simulation results.\\
 
-The second case study is the EPFL campus in Lausanne, Switzerland.
-The targeted building in this case was the Quartier Nord complex.
-The focus of this study was to compare the output results of both CitySim and EnergyPlus.
-Reliable measured data for calibration is not currently available for this building.
+The second case study is the EPFL campus in Lausanne, Switzerland. The
+targeted building in this case was the Quartier Nord complex. The focus of
+this study was to compare the output results of both CitySim and EnergyPlus.
+Reliable measured data for calibration is not currently available for this
+building.
 
@@
 %The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland. 
-The ETH Z\"urich Hoenggerberg campus includes 32 higher education \noteDT{deleted: "buildings"} with spaces allocated to laboratories, office space, lecture halls, cafeterias, data centers and other types of similar spaces.
-The campus has a centralized energy management system (EMS) that contains 807 energy and water measurement points from heating, cooling, electricity, city gas, domestic hot water, grey water, and general water consumption.
+The ETH Z\"urich Hoenggerberg campus includes 32 higher education facilities
+ with spaces allocated to laboratories, office space, lecture halls,
+ cafeterias, data centers and other types of similar spaces. The campus has a
+ centralized energy management system (EMS) that contains 807 energy and water
+ measurement points from heating, cooling, electricity, city gas, domestic hot
+ water, grey water, and general water consumption. %\noteDT{deleted: "buildings"}
 
@@
 
-The focus of the co-simulation process is that the performance of a targeted building is evaluated through solo and coupled methods.
-The HPI building on campus was chosen in this case study due to \noteDT{insert: "the"} amount and quality of measured data available from the EMS for this building.
-HPI is a 2,610 sq.
-meter building that \noteDT{insert: "is"} made up mostly of office space and classrooms.
-It also includes 400 sq.
-meter\noteDT{can we use $m^2$ instead?} convenience store and coffee shop.
-The building is indicated on a campus map shown in Figure \ref{fig:campusmap} and is shaded red.
+The focus of the co-simulation process is that the performance of a targeted
+building is evaluated through solo and coupled methods. The HPI building on
+campus was chosen in this case study due to the amount and quality of measured
+data available from the EMS for this building. HPI is a 2,610 sq. meter
+building that is made up mostly of office space and classrooms. It also
+includes 400 $m^2$ convenience store and coffee shop. The building is
+indicated on a campus map shown in Figure \ref{fig:campusmap} and is shaded
+red.
 
@@
 \subsection{Model development}
-In order to perform a co-simulation of the targeted buildings, initially a CitySim model of the campus is developed.
-Through the workflow automation process, this geometry was converted into an EnergyPlus input file as seen in Figure \ref{fig:HPIcampus}.
-The EnergyPlus input file is then used as an input to execute EnergyPlus solo and co-simulation processes for the purpose of simplified calibration, and then to understand the magnitude of difference between these simulation scenarios.
-% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.
+In order to perform a co-simulation of the targeted buildings, initially a
+CitySim model of the campus is developed. Through the workflow automation
+process, this geometry was converted into an EnergyPlus input file as seen in
+Figure \ref{fig:HPIcampus}. The EnergyPlus input file is then used as an input
+to execute EnergyPlus solo and co-simulation processes for the purpose of
+simplified calibration, and then to understand the magnitude of difference
+between these simulation scenarios.% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.
 
@@
 
-Energy data from the HPI building was collected and analyzed in the context of the simplified calibration procedures.
-The measured datasets are screened and aggregated into typical usage profiles to be used for the lighting, plug-loads, and HVAC equipment availability schedules and power densities.
-Figure \ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical energy for the HPI building.
-This profile was created through a filtering and clustering process known as \emph{DayFilter} \citep{Miller:2015kr}.
-This profile is used to set the availability schedules as inputs into the EnergyPlus simulation to emulate the way occupants inhabit the building and how the building management system (BMS) controls the lighting and HVAC systems.
-This approach is compared to the practice of interviews and site visits to determine such input parameters.\noteDT{where???
-how???
-i don't get it...}
+Energy data from the HPI building was collected and analyzed in the context of
+the simplified calibration procedures. The measured datasets are screened and
+aggregated into typical usage profiles to be used for the lighting, plug-
+loads, and HVAC equipment availability schedules and power densities. Figure
+\ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical
+energy for the HPI building. This profile was created through a filtering and
+clustering process known as \emph{DayFilter} \citep{Miller:2015kr}. This
+profile is used to set the availability schedules as inputs into the
+EnergyPlus simulation to emulate the way occupants inhabit the building and
+how the building management system (BMS) controls the lighting and HVAC
+systems. 
+% This approach is compared to the practice of interviews and site
+% visits to determine such input parameters.\noteDT{where??? how??? i don't get
+% it...}
 
@@
 
-The measured and simulated data from both the co-simulation and EnergyPlus solo simulation was compared in order to create a realistic scenario for comparison.
-The calibration process was undertaken through a series of steps such as including local weather conditions for the simulation period and adding custom lighting schedules and power densities extracted from the measured data.
-The models were calibrated to the summer season (May-September) for cooling and the winter season (Jan-April and October to December) for heating.
-This approach was taken as the data quality for the measurements were deemed most accurate during the appropriate seasons.
-Figure \ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the simulations after the tuning process.
-The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating.
-These metrics fall within the +/-10\% NMBE and +/-30\% CVRSME used in this case study for the purposes of partial calibration.
-The goal of calibration in this case is to simply bring the models to within a reasonable range of reality in order to bring more confidence to analysis of the discrepancies between the solo and co-simulation scenarios.\noteDT{Clayton, can you introduce a consistency in the symbols for the figures?
-say, squares for co-simulation, circles for e+, triangles for measured?
-and do this across all the figures?
-small detail, but i think shows quality and a certain, how shall i call it?
-swissness?
-a qualité suisse?}
+The measured and simulated data from both the co-simulation and EnergyPlus
+solo simulation was compared in order to create a realistic scenario for
+comparison. The calibration process was undertaken through a series of steps
+such as including local weather conditions for the simulation period and
+adding custom lighting schedules and power densities extracted from the
+measured data. The models were calibrated to the summer season (May-September)
+for cooling and the winter season (Jan-April and October to December) for
+heating. This approach was taken as the data quality for the measurements were
+deemed most accurate during the appropriate seasons. Figure
+\ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the
+simulations after the tuning process. The final calibrated EnergyPlus solo
+model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of
+variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\%
+and 29.4\% for heating. These metrics fall within the +/-10\% NMBE and +/-30\%
+CVRSME used in this case study for the purposes of partial calibration. The
+goal of calibration in this case is to simply bring the models to within a
+reasonable range of reality in order to bring more confidence to analysis of
+the discrepancies between the solo and co-simulation
+scenarios.
+%\noteDT{Clayton, can you introduce a consistency in the symbols for
+% the figures? say, squares for co-simulation, circles for e+, triangles for
+% measured? and do this across all the figures? small detail, but i think shows
+% quality and a certain, how shall i call it? swissness? a qualité suisse?}
 %Daily data was used to calculated goodness of fit to determine calibration success. 
@@
 \subsection{EnergyPlus co-simulation results}
+After calibration, a comparison of co-simulation and solo EnergyPlus
+simulations is made. For cooling, a discrepancy can be seen between co-
+simulation and solo EnergyPlus. Co-simulation results in a 20.2\% decrease in
+predicted cooling energy is observed as seen in Figure
+\ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
+illustrates the difference in predicted heating energy consumption across the
+test year. A consistent offset exists across the time frame of days in
+January, the peak of the heating season. A more varied discrepancy across the
+heating months is noticed resulting an overall increase of heating prediction
+of 4.8\% due to co-simulation. The exchange of long wave radiation for this
+particular site is substantial due to the proximity of surrounding buildings.
+These performance differences due to co-simulation are compared to a
+theoretical single-zone case study in which there was a 15-30\% increase in
+heating energy and a 4-11\% decrease in cooling energy. The results from this
+scenario are less extreme on the heating side and more on the cooling side.
 
-After calibration, a comparison of co-simulation and solo EnergyPlus simulations is made.
-For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus.
-A 20.2\% decrease in \noteDT{with respect to what???} predicted cooling energy is observed as seen in Figure \ref{fig:hpi_energypluscooling}.
-Figure \ref{fig:hpi_energyplusheating} illustrates the difference in predicted heating energy consumption across the test year.
-A consistent offset exists across the time frame of days in January, the peak of the heating season.
-A more varied discrepancy across the heating months is noticed resulting and\noteDT{s/and/in an/} overall increase of heating prediction of 4.8\% due to co-simulation.
-The exchange of long wave radiation for this particular site is likely greater due to \noteDT{greater than what??} the proximity of surrounding buildings.
-These performance differences due to co-simulation are compared to a theoretical single-zone case study in which there was a 15-30\% increase in heating energy and a 4-11\% decrease in cooling energy.
-The results form\noteDT{s/form/from/} this\noteDT{which?} scenario are less extreme from the heating side and more extreme from\noteDT{from, from, from, you know what?
-there has to be a better way to formulate this sentence} the cooling side.
+% \noteDT{with respect to what???}
+% \noteDT{greater than what??}
 
@@
 \subsection{Campus case study 2: EPFL Quartier Nord} 
-Quartier Nord is a whole new quarter of the École Polytechnique Fédérale de Lausanne (EPFL) campus located at its northwest corner.
-This complex includes a Convention Centre with an auditorium with a maximum capacity of 3000 (seated) people, housing for 516 students, retail and service areas and a hotel.
-As a public space, this ensemble is organized around a main plaza as seen in  Figure \ref{fig:quartier_nord_1}).
+Quartier Nord is a whole new quarter of the École Polytechnique Fédérale de
+Lausanne (EPFL) campus located at its northwest corner. This complex includes
+a Convention Centre with an auditorium with a maximum capacity of 3000
+(seated) people, housing for 516 students, retail and service areas and a
+hotel. As a public space, this ensemble is organized around a main plaza as
+seen in Figure \ref{fig:quartier_nord_1}).
 
@@
 
-With a particularly strong visual and formal identity, the SwissTech Convention Centre (STCC) is clearly the key protagonist.\noteDT{move main sentence to start of paragraph} Applied with important functions for the region, the building has definitely become the new landmark.
-Designed as a Minergie\noteDT{ref?} building, it includes modern energy conversion technologies to reduce its energy consumption.
-The focus of the co-simulation is realised on the STCC, simulated with the nearby buidings for housing, retail and service areas.
+With a particularly strong visual and formal identity, the SwissTech
+Convention Centre (STCC) is clearly the key protagonist.\noteDT{move main
+sentence to start of paragraph} Applied with important functions for the
+region, the building has definitely become the new landmark. Designed as a
+Minergie\noteDT{ref?} building, it includes modern energy conversion
+technologies to reduce its energy consumption. The focus of the co-simulation
+is realized on the STCC, simulated with the nearby buildings for housing,
+retail and service areas.
 
 \subsection{Model development}
-The information required in the simulation mainly comprises three parts: physical, geometrical and operational data.
-The geometry information including the shape, dimension, structure and materials was obtained from the Real Estate and Infrastructure Department of École Polytechnique Fédérale de Lausanne (EPFL), which was responsible for carrying out the project from call to tender to construction.
-However, since the documents provided were full of details but also conflicting with what has been installed as compared to the documents before construction, the task to realise a precise model of the buildings itself is rather tedious.
-Besides, it is even more challenging to get the operational data (daily occupancy, lighting and electrical equipment usage level and ventilation rate) as the building has only recently been set in operation mode and as engineers and technicians have been working on improving the controls.
-Therefore, due to unreliable monitoring data, the calibration step of the model has been unfortunately\noteDT{delete: "unfortunately".
-we are cold hard scientists battling the evil nemesis that is entropy and his plan to suffocate everyone with the inevitable heat death of the universe.
-we have no time for lame excuses.
-we just abandon.
-no regrets.
+The information required in the simulation mainly comprises three parts:
+physical, geometrical and operational data. The geometry information including
+the shape, dimension, structure and materials was obtained from the Real
+Estate and Infrastructure Department of École Polytechnique Fédérale de
+Lausanne (EPFL), which was responsible for carrying out the project from call
+to tender to construction. However, since the documents provided were full of
+details but also conflicting with what has been installed as compared to the
+documents before construction, the task to realize a precise model of the
+buildings itself is rather tedious. Besides, it is even more challenging to
+get the operational data (daily occupancy, lighting and electrical equipment
+usage level and ventilation rate) as the building has only recently been set
+in operation mode and as engineers and technicians have been working on
+improving the controls. Therefore, due to unreliable monitoring data, the
+calibration step of the model has been unfortunately\noteDT{delete:
+"unfortunately". we are cold hard scientists battling the evil nemesis that is
+entropy and his plan to suffocate everyone with the inevitable heat death of
+the universe. we have no time for lame excuses. we just abandon. no regrets.
 thug life!} abandoned.\\
 
-Considering the lack of detailed information about the building, a so-called detailed reference case was modeled with EnergyPlus \citep{Mauree:2015to} in which regulation standards applied in the design phase from the SIA norms were used to complete the missing information.
-A rendering of this model is seen in Figure \ref{fig:model_yang}.
+Considering the lack of detailed information about the building, a so-called
+detailed reference case was modeled with EnergyPlus \citep{Mauree:2015to} in
+which regulation standards applied in the design phase from the SIA norms were
+used to complete the missing information. A rendering of this model is seen in
+Figure \ref{fig:model_yang}.
 
@@
 \includegraphics[width=\textwidth]{figures/model_yang}
-\caption{The Quartier Nord modeled with OpenStudio for Sketchup\noteDT{s/sketchup/SketchUp/}.
-The STCC on the left is the main focus of the study and \noteDT{insert: "is"} represented by two thermal zones.}
+\caption{The Quartier Nord modeled with OpenStudio for
+Sketchup\noteDT{s/sketchup/SketchUp/}. The STCC on the left is the main focus
+of the study and is represented by two thermal zones.}
 \label{fig:model_yang}
@@
 
-The corresponding CitySim model was created by exporting a DXF file from EnergyPlus, and importing it into the Graphical User Interface of CitySim.
-Physical caracteristics of the building were added to complete the CitySim model.
-Finally, the same script as described in Section \ref{Methodology} was used to export the model from CitySim to EnergyPlus, giving a simplified EnergyPlus model.\\
+The corresponding CitySim model was created by exporting a DXF file from
+EnergyPlus, and importing it into the Graphical User Interface of CitySim.
+Physical caracteristics of the building were added to complete the CitySim
+model. Finally, the same script as described in Section \ref{Methodology} was
+used to export the model from CitySim to EnergyPlus, giving a simplified
+EnergyPlus model.\\
 
@@
 
-Both the CitySim and EnergyPlus engines are utilized in this case study.
-The first comparison to observe are the differences between the two engines when focused on the Quartier Nord building.
-When simulated in isolation, the CitySim engine predicts a 28.6\% increase in heating load and a 44.4\% increase in cooling load than\noteDT{s/than/compared to} EnergyPlus with the model inputs aligned as closely as possible\noteDT{??!
-aligned as closely as possible?
-this is not how we overcome the dark lord.
-can we quantify this?}.
-This phenomenon is due to the differences in the way each of these engines calculates heating and cooling loads.
-Use of the co-simulation process,\noteDT{comma-comma-comma, or not} brings the engines to within 5.4\%.
-Figure \ref{fig:qn_eplusvscitysim_heating} illustrates these differences.\noteDT{in the figures that follow, Cosim and CoSim are both used.
-decide.
-then stick to one spelling.
-everywhere.
-notice how i need a break?
-tgif!}
+Both the CitySim and EnergyPlus engines are utilized in this case study. The
+first comparison to observe are the differences between the two engines when
+focused on the Quartier Nord building. When simulated in isolation, the
+CitySim engine predicts a 28.6\% increase in heating load and a 44.4\%
+increase in cooling load than EnergyPlus with the
+model inputs aligned as closely as possible\noteDT{??! aligned as closely as
+possible? this is not how we overcome the dark lord. can we quantify this?}.
+This phenomenon is due to the differences in the way each of these engines
+calculates heating and cooling loads. Use of the co-simulation process,\noteDT
+{comma-comma-comma, or not} brings the engines to within 5.4\%. Figure
+\ref{fig:qn_eplusvscitysim_heating} illustrates these differences.\noteDT{in
+the figures that follow, Cosim and CoSim are both used. decide. then stick to
+one spelling. everywhere. notice how i need a break? tgif!}
 
@@
 \subsection{EnergyPlus co-simulation results}
-
-When focusing on\noteDT{delete: "on"} solely \noteDT{what exactly do we mean here?
-solely?} on EnergyPlus, a 7.5\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_cooling}.
-A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}.
-These differences are less prounced that the HPI case study.
-\noteCM{I'm planning to elaborate on these sections but am struggling to interpret the results other than just "co-sim and solo are difference" -- what do you guys think?}\noteDT{well, for a start, the two case studies differ in the amount of LWR radiation.
-we could quantify that?
-also, the number of surfaces of the e+ model with viewfactor to surrounding buildings?}
+When focusing on the EnergyPlus results, a 7.5\% decrease in cooling energy is
+observed, as seen in Figure
+\ref{fig:qn_eplus_cosimvssolo_cooling}. A 2.8\% increase in heating energy is
+observed, as seen in Figure
+\ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less prounced
+that the HPI case study. \noteCM{I'm planning to elaborate on these sections
+but am struggling to interpret the results other than just "co-sim and solo
+are difference" -- what do you guys think?}\noteDT{well, for a start, the two
+case studies differ in the amount of LWR radiation. we could quantify that?
+also, the number of surfaces of the e+ model with viewfactor to surrounding
+buildings?}
 
@@
 
-When focusing on\noteDT{delte: "on"} solely on CitySim, a 26.9\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}.
-A 49.1\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}.
-\noteCM{Jerome -- I need some help interpreting these results -- you mentioned that there is an expected delta between citysim and energyplus in previous studies.
-Can you help elaborate on that?}
+When focusing solely on CitySim, a 26.9\% decrease in heating energy is
+observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}. A 49.1\%
+decrease in heating energy is observed, as seen in Figure
+\ref{fig:qn_citysim_cosimvssolo_heating}. \noteCM{Jerome -- I need some help
+interpreting these results -- you mentioned that there is an expected delta
+between citysim and energyplus in previous studies. Can you help elaborate on
+that?}
 
@@
 \section{Conclusion}
-The ability to couple and leverage the best aspects of multiple simulation engines can enhance the modeling of large scale urban agglomerations.
-This paper has outlined two such scenarios in which the building-focused EnergyPlus simulation engine is coupled and co-simulated with the urban-scale CitySim engine.
-This process is implemented through a fully automated work flow process that extract\noteDT{s/extract/extracts/} geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each timestep of targeted variables, and accumulates the results for analysis.
-The process has been implemented on simplified theoretical scenarios in the past and the key innovation with this work is in implementation on actual case study campuses and targeted buildings.
-The results illustrate that the differences between the co-simulation and solo environments are within range of previous theoretical models.
-More reliable results of the magnitude of differences between the simulation techniques can be extracted from these real-world scenarios.
+The ability to couple and leverage the best aspects of multiple simulation
+engines can enhance the modeling of large scale urban agglomerations. This
+paper has outlined two such scenarios in which the building-focused EnergyPlus
+simulation engine is coupled and co-simulated with the urban-scale CitySim
+engine. This process is implemented through a fully automated work flow
+process that extract\noteDT{s/extract/extracts/} geometry information at the
+urban-scale, creates the necessary input information, executes each engine
+with information exchange at each timestep of targeted variables, and
+accumulates the results for analysis. The process has been implemented on
+simplified theoretical scenarios in the past and the key innovation with this
+work is in implementation on actual case study campuses and targeted
+buildings. The results illustrate that the differences between the co-
+simulation and solo environments are within range of previous theoretical
+models. More reliable results of the magnitude of differences between the
+simulation techniques can be extracted from these real-world scenarios.
 
-Future work in using co-simulation models for buildings and campuses would more intensively utilize the model results in a practical implementation of retrofit scenarios or urban-scale energy systems research.
+Future work in using co-simulation models for buildings and campuses would
+more intensively utilize the model results in a practical implementation of
+retrofit scenarios or urban-scale energy systems research.
 
 \subsection{Acknowledgements}
-
-The authors would like to acknowledge the ETH Z\"urich Campus Facilities Department and the EPFL Real Estate and Infrastructure Department.
-This research was funded by the Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale Energy Modeling (UMEM) project.\noteDT{We also want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}
+The authors would like to acknowledge the ETH Z\"urich Campus Facilities
+Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
+Thoma for their assistance in this project. This research was funded by the
+Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
+Energy Modeling (UMEM) project.% \noteDT{We also
+% want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}
 

### 2016-04-27 latex/UMEM_CoSim.tex
Fixed loads of typos and added content

@@
     scale models of two campuses of higher education buildings in Switzerland.
-    The campuses are modeled at both the building scale using the EnergyPlus
-    simulation engine and at the urban scale using the CitySim engine. A co-
+    The campuses are modeled at both the building level, using the EnergyPlus
+    simulation engine, and at the urban scale using the CitySim engine. A co-
     simulation framework is used to execute simulations from both engines
@@
     strengths of each. In the first case study, on-site weather and measured
-    performance data is then compared to the output from two modeling
+    performance data are then compared to the output from two modeling
     scenarios: building-scale simulation using EnergyPlus and co-simulation of
@@
     to the both the CitySim simulation and EnergyPlus engines. The results
-    show that {\color{red}insert results here}. A discussion is included of
-    the challenges encountered with the urban scale calibration and the
-    strengths and weaknesses of the developed process.
+    show that coupling of EnergyPlus with CitySim resulted in a -20\% and
+    -7.5\% impact on cooling consumption and a +2.8\% and +4.8\% impact on
+    heating consumption. Challenges encountered with the urban scale
+    calibration and the strengths and weaknesses of the developed process are
+    discussed.
     % \noteDT{Clayton, can you
-    % get your editor to do hard linewrapping? all your paragraphs are a single
+    % get your editor to do hard line wrapping? all your paragraphs are a single
     % line which breaks the diff model of GitHub and makes editing in VIM super
@@
 analysis and optimization of cities. Urban populations are growing around the
-world at an unprecedented rate. A shift from urban to rural is underway and
-2.5 billion people are expected to join urban centers throughout the world
+world at an unprecedented rate. A transition from urban to rural is underway and
+2.5 billion people are expected to join cities throughout the world
 \citep{UnitedNations:2014vn}. Expansions of entire districts and even cities
 is not an uncommon phenomenon, especially in East Asia and Africa. Urban scale
-modeling is in the midst of a strong focus within the research community with
+modeling is in the midst of an intense focus on the research community with
 six key areas of practice: technology design, building design, urban climate,
@@
 simulation engine. CitySim simulates multiple buildings up to city scale using
-simplified models in order to achieve a good compromise between modeling
-accuracy, computational overheads and data availability. Each building's
+simplified models to achieve a good compromise between modeling
+accuracy, computational overheads, and data availability. Each building's
 thermal behavior is based on an electrical analogy using a two node resistor-
@@
 simplifying approximations empowers the urban-scale simulation to have
-reasonable execution times with respect to the number of buildings being
+reasonable execution times on the number of buildings being
 simulated.
@@
 input parameters necessary and run-times of the engines themselves. This focus
-results in certain deficiencies with respect to modeling various phenomenon.
+results in certain deficiencies concerning modeling various phenomenon.
 For example, urban scale simulation highly simplifies the building systems and
-internal load models, thus making retrofit analysis at the systems level
+internal load models, thus making a retrofit analysis at the systems level
 difficult. And whole building simulation in EnergyPlus neglects many of the
@@
 
-In order to address the deficiencies of the individual engines, the current
+To address the deficiencies of the individual engines, the current
 effort seeks to couple building and urban scale simulation. The research in
-this paper is part of an\noteDT{s/an/a/} larger coupling effort in which
-various engines are connected and co-simulated to create a more comprehensive
-analysis of the urban scale \citep{Dorer:2013vt,Allegrini:2012kx}. The target
-is the computational interface between the building energy model, using
-EnergyPlus, and the urban energy model using CitySim. An overview of the
-larger scope is shown in Figure \ref{fig:UMEM} and the context of the coupling
-task is shown as the interface between the City Energy Simulation (CES) model
-and the Building Energy Simulation (BES) model.
+this paper is part of a larger coupling effort in which various engines are
+connected and co-simulated to create a more comprehensive analysis of the
+urban scale \citep{Dorer:2013vt,Allegrini:2012kx}. The target is the
+computational interface between the building energy model, using EnergyPlus,
+and the urban energy model using CitySim. An overview of the larger scope is
+shown in Figure \ref{fig:UMEM} and the context of the coupling task appears as the interface between the City Energy Simulation (CES) model and the
+Building Energy Simulation (BES) model.
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 \centering
@@
 previous literature \citep{thomas2014multiscale,Miller:2015vk}. The innovation
-in the current publication is an extension to this research through the
-modelling and co-simulation of real-world case studies. With respect to the
+in the current publication is an extension of this research through the
+modeling and co-simulation of real-world case studies. With respect to the
 third contribution, to the best of the authors' knowledge, no previous study
@@
 simulation engines at various scales. Much of the initial co-simulation work
-in the literature is at the subsystem and building-scales. Previous studies
+in the literature is done at the subsystem and building-scale. Previous studies
 have analyzed strong and loose coupling of engines at this scale
@@
 \citep{Yang:2012cr}. It was also coupled with simplified lumped parameter
-models in order to facilitate comparison with measured sensor data
+models to facilitate comparison with measured sensor data
 \citep{Martin:2015fj}. EnergyPlus and the TEP Urban Canopy Model program were
-coupled in order to quantify the influences of urban localized weather effects
+coupled to quantify the influences of urban localized weather effects
 on whole building simulation \citep{Bueno:2011hi} and urban weather generation
@@
 \section{Methodology}\label{Methodology}
-% Portions of the following methodology is developed in previous literature and is reiterated in this section in order to set the context for Section \ref{Implementation}.
-The previous published research is clearly outlined at the beginning of each subsection.
+% Portions of the following methodology is developed in previous literature and is reiterated to set the context for Section \ref{Implementation}.
+The previously published research is clearly outlined at the beginning of each subsection.
 
-\subsection{Coupling process} The coupling process of a simplified single zone
-model and contextual surrounding buildings is outlined in previous studies
-\citep{thomas2014multiscale}. This study forms the basis for the methodology
+\subsection{Coupling process} 
+The coupling process of a simplified single zone
+model and contextual surrounding buildings is described in previous studies
+\citep{thomas2014multiscale}, which forms the basis for the methodology
 in the current effort. This process utilizes the Design Performance Viewer
-(DPV) and associated work flow. The DPV is a tool written to extract and
+(DPV) and associated workflow. The DPV is a tool written to extract and
 simulate an EnergyPlus input data file (IDF) from an
 Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM
-\citep{Schlueter2009}. The main philosophy behind the tool is rapid simulation
+\citep{Schlueter2009}. The central philosophy behind the tool is a rapid simulation
 of the building information model from the earliest design possible and can be
@@
 functionality is used for creating the CitySim mass scene and leads to a crude
-model of the urban context of the building. The existing DPV philosophy of
+model of the urban context of the building. The current DPV philosophy of
 allowing the designer to iterate rapidly on early design decisions based on
@@
 streamlining the process where running a simulation requires no effort from
-the designer due to automatic creation of input files, execution and analysis
+the designer due to automatic creation of input files, execution, and analysis
 of the results.% \noteDT{not sure the second reference includes coupling...}
@@
 extract geometrical information about the building and the physical properties
-of walls, windows, doors, roofs and floors. This information is encoded in the
+of walls, windows, doors, roofs, and floors. This information is encoded in the
 BIM model as wall types, roof types, floor types as well as window and door
@@
 surrounding buildings. The DPV model views these buildings as a series of
-shading surfaces. A transformation is added on the DPV model that produces an
+shading surfaces. A transformation is added to the DPV model that produces an
 input file for the CitySim solver. This file uses an XML format describing the
 buildings in a scene for simulation, including their construction types,
-geometry and systems for heating and cooling. The main BIM is extracted to the
+geometry, and systems for heating and cooling. The main BIM is extracted to the
 CitySim scene as one of the buildings to be simulated, with the properties of
@@
 calculated based on the window and wall areas of the DPV model. Shading
-surfaces are grouped into buildings based on the mass object they were
-extracted from. These neighboring buildings use default construction
-properties for walls and roofs and we assign them a default glazing ratio.
+surfaces are grouped into buildings based on the mass object from which they were extracted.
+These neighboring buildings use default construction properties for walls and roofs, and we assign them a default glazing ratio.
 These defaults can be overridden by custom properties applied to the mass
@@
 is more abstract than the model used by EnergyPlus, the EMS is used to
-aggregate certain values. CitySim does not model windows separately, therefore
+aggregate certain values. CitySim does not model windows separately. Therefore,
 a weighted average of window and wall surface temperatures is calculated with
@@
 
-% It was determined that in order to export an output variable using the FMU export functionality, the variable itself must also be output with an IDF object of type \emph{Output:Variable} or \emph{EnergyManagementSystem:OutputVariable} in the IDF file as well.
+% It was determined that to export an output variable using the FMU export functionality, the variable itself must also be output with an IDF object of type \emph{Output:Variable} or \emph{EnergyManagementSystem:OutputVariable} in the IDF file as well.
 
@@
 Several key urban-scale weather variables are sent to EnergyPlus from CitySim
-in order to better account for the localized effects of surrounding buildings,
+to account better for the localized effects of surrounding buildings,
 geography and climate conditions. These variables include various outdoor air
-conditions such as drybulb and wetbulb temperatures, dewpoint, humidity, wind
+conditions such as dry bulb and wet bulb temperatures, dewpoint, humidity, wind
 speed and direction, and direct and diffuse solar radiation. These variables
@@
 exchange between the simulated building and its surroundings is sent to
-EnergyPlus; this process is describe\noteDT{s/describe/described/} in detail
-in a subsequent methodology section\noteDT{can we not just name the section?
-this phrasing seems awkward}. Finally, CitySim shares its calculated occupancy
-schedules as it uses a more robust model of occupants behavior
+EnergyPlus; this process is described in detail in Section \ref{lwradiation}.
+Finally, CitySim shares its calculated occupancy schedules as it uses a more
+robust model of occupants behavior
 \citep{Haldi:2011dr}.
@@
 internal load types than CitySim. For example, EnergyPlus is flexible enough
-to model a detailed, radiant heating and cooling system that would be
+to model a detailed radiant heating and cooling system that would be
 impossible in CiytSim \citep{barbara:2015tz}. EnergyPlus is an engine
-optimized to accurately model building-scale systems, thus CitySim can take 
+optimized to accurately model building-scale systems. Thus, CitySim can take 
 advantage of these models through coupling and co-simulation. EnergyPlus sends
@@
 
-\noteDT{in table 2: "Values SENT to CitySim..."}
+%\noteDT{in table 2: "Values SENT to CitySim..."}
 \begin{table}[H]
-\tbl{Values to CitySim from EnergyPlus by the FMU}
+\tbl{Values sent to CitySim from EnergyPlus by the FMU}
 {\begin{tabular}[l]{@{}lcc}\toprule
@@
 \subsection{Long wave radiation exchange}
-
+\label{lwradiation}
 Long wave radiation exchange in the urban scale environment is coupled in the
-co-simulation process and it requires the development of a set of
+co-simulation process. It requires the development of a set of
 approximations to reduce the number of coupled variables between the engines
 and to account for differences in the methods by which each engine calculates
-this metric. A detailed description of Long Wave Radiation (LWR) variable
+this value. A detailed description of Long Wave Radiation (LWR) variable
 exchange and approximation is found in a previously published study
@@
 The coupling, simulation and co-simulation process is completely managed
-within a program called VisTrails \citep{Anonymous:Cayf2tu7}. This tool
-empowers the coupling of various executable files and their connecting scripts
-in graphical diagrams that enhances reproducibility and
-process automation \citep{Freire:2014tt}.
+within a program called VisTrails \citep{Anonymous:Cayf2tu7}. The
+implementation of this type of work flow is outlined in previous work focused
+on automating DPV using the Kepler platform \citep{Thomas:2012wj}. This
+process reduces the effort expended by a designer down to pressing a single
+button. This functionality allows an iterative design style informed by
+readily available simulation results. An automated work flow to tie the
+various steps together and maintain the effortless iterative design process.
+VisTrails enables the coupling of various work flow subprocesses script
+initializations, executions of the engines, and the compilation of the
+outputs. This tool empowers the coupling of various executable files and their
+connecting scripts in graphical diagrams that enhances reproducibility and
+process automation \citep{Freire:2014tt}. The VisTrails work flow diagram for
+the first case study in this paper is seen in Figure \ref{VizTrails}.
 
@@
 knowledge first and working towards equilibrium between measured and
-simulated. An appropriate balance between effort of implementation and value
+simulated. An appropriate balance between the effort of implementation and value
 generated through the calibration process.
@@
 The second case study is the EPFL campus in Lausanne, Switzerland. The
-targeted building in this case was the Quartier Nord complex. The focus of
+targeted building, in this case, was the Quartier Nord complex. The focus of
 this study was to compare the output results of both CitySim and EnergyPlus.
@@
  with spaces allocated to laboratories, office space, lecture halls,
- cafeterias, data centers and other types of similar spaces. The campus has a
+ cafeterias, data centers and other types of similar areas. The campus has a
  centralized energy management system (EMS) that contains 807 energy and water
@@
 and 29.4\% for heating. These metrics fall within the +/-10\% NMBE and +/-30\%
-CVRSME used in this case study for the purposes of partial calibration. The
-goal of calibration in this case is to simply bring the models to within a
+CVRSME used in this case study for calibration. The
+goal of calibration, in this case, is to just bring the models to within a
 reasonable range of reality in order to bring more confidence to analysis of
@@
 simulation and solo EnergyPlus. Co-simulation results in a 20.2\% decrease in
-predicted cooling energy is observed as seen in Figure
+predicted cooling energy, as seen in Figure
 \ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
@@
 theoretical single-zone case study in which there was a 15-30\% increase in
-heating energy and a 4-11\% decrease in cooling energy. The results from this
-scenario are less extreme on the heating side and more on the cooling side.
+heating energy and a 4-11\% decrease in cooling energy \citep{Miller:2015vk}.
+The results from this scenario are less extreme on the heating side and more
+on the cooling side than the theoretical case study.
 
@@
 (seated) people, housing for 516 students, retail and service areas and a
-hotel. As a public space, this ensemble is organized around a main plaza as
+hotel. As a public space, this ensemble is organized around the central plaza as
 seen in Figure \ref{fig:quartier_nord_1}).
@@
 Convention Centre (STCC) is clearly the key protagonist.\noteDT{move main
-sentence to start of paragraph} Applied with important functions for the
+sentence to start of paragraph} Applied with essential functions for the
 region, the building has definitely become the new landmark. Designed as a
@@
 buildings itself is rather tedious. Besides, it is even more challenging to
-get the operational data (daily occupancy, lighting and electrical equipment
+get the operational data (daily occupancy, lighting, and electrical equipment
 usage level and ventilation rate) as the building has only recently been set
@@
 EnergyPlus, and importing it into the Graphical User Interface of CitySim.
-Physical caracteristics of the building were added to complete the CitySim
+Physical characteristics of the building were added to complete the CitySim
 model. Finally, the same script as described in Section \ref{Methodology} was
@@
 % As a summary, three models are compared: a detailed EnergyPlus model, a simplified CitySim model and a simplified EnergyPlus model.
-In addition to what a coupled simplified CitySim and EnergyPlus model is realised and its results analysed with respect to the other three models.
+In addition to what a coupled simplified CitySim and EnergyPlus model is realized and its results analyzed with respect to the other three models.
 
@@
 Both the CitySim and EnergyPlus engines are utilized in this case study. The
-first comparison to observe are the differences between the two engines when
+first comparison to observe is the differences between the two engines when
 focused on the Quartier Nord building. When simulated in isolation, the
 CitySim engine predicts a 28.6\% increase in heating load and a 44.4\%
-increase in cooling load than EnergyPlus with the
-model inputs aligned as closely as possible\noteDT{??! aligned as closely as
-possible? this is not how we overcome the dark lord. can we quantify this?}.
-This phenomenon is due to the differences in the way each of these engines
-calculates heating and cooling loads. Use of the co-simulation process,\noteDT
-{comma-comma-comma, or not} brings the engines to within 5.4\%. Figure
-\ref{fig:qn_eplusvscitysim_heating} illustrates these differences.\noteDT{in
-the figures that follow, Cosim and CoSim are both used. decide. then stick to
-one spelling. everywhere. notice how i need a break? tgif!}
+increase in cooling load as compared to EnergyPlus. This phenomenon is due to
+the differences in the way each of these engines calculates heating and
+cooling loads. Use of the co-simulation process brings the engines to within
+5.4\%. Figure \ref{fig:qn_eplusvscitysim_cooling} illustrates these
+differences for cooling and Figure \ref{fig:qn_eplusvscitysim_heating} for
+heating.
+% \noteDT{in
+% the figures that follow, Cosim and CoSim are both used. decide. then stick to
+% one spelling. everywhere. notice how i need a break? tgif!}
+
+% as closely as possible\noteDT{??! aligned as closely as
+% possible? this is not how we overcome the dark lord. can we quantify this?}
+
+% ,\noteDT % {comma-comma-comma, or not}
 
@@
 \subsection{EnergyPlus co-simulation results}
-When focusing on the EnergyPlus results, a 7.5\% decrease in cooling energy is
+The Quartier Nord building is also simulated within the solo and
+cosimulation environments. When
+focusing on the EnergyPlus results, a 7.5\% decrease in cooling energy is
 observed, as seen in Figure
@@
 observed, as seen in Figure
-\ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less prounced
-that the HPI case study. \noteCM{I'm planning to elaborate on these sections
+\ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less pronounced
+that the HPI and theoretical case studies due to the number and proximity of
+surrounding buildings is not as large. \noteCM{I'm planning to elaborate on
+these sections
 but am struggling to interpret the results other than just "co-sim and solo
-are difference" -- what do you guys think?}\noteDT{well, for a start, the two
+are different" -- what do you guys think?}\noteDT{well, for a start, the two
 case studies differ in the amount of LWR radiation. we could quantify that?
@@
 decrease in heating energy is observed, as seen in Figure
-\ref{fig:qn_citysim_cosimvssolo_heating}. \noteCM{Jerome -- I need some help
+\ref{fig:qn_citysim_cosimvssolo_heating}. These results align with the
+previous comparison of EnergyPlus and CitySim engines. The substantial
+differences between solo and co-simulation in these cases is a result of
+EnergyPlus transferring the heating and cooling load values at each time step. \noteCM{Jerome -- I need some help
 interpreting these results -- you mentioned that there is an expected delta
@@
 engine. This process is implemented through a fully automated work flow
-process that extract\noteDT{s/extract/extracts/} geometry information at the
+process that extracts geometry information at the
 urban-scale, creates the necessary input information, executes each engine
-with information exchange at each timestep of targeted variables, and
-accumulates the results for analysis. The process has been implemented on
+with information exchange at each time step of targeted variables, and
+accumulates the results of analysis. The process has been implemented on
 simplified theoretical scenarios in the past and the key innovation with this
@@
 Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
-Energy Modeling (UMEM) project.% \noteDT{We also
+Energy Modeling (UMEM) project. The authors would also like to acknowledge
+ Emanuel Thoma for his work in developing the geometric models.% %
+ % \noteDT{We also
 % want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}

### 2016-11-28 latex/UMEM_CoSim.tex
Content Updates

@@
 
-\section{Introduction}\noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}
+\section{Introduction}
+% \noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}
 
@@
 a weighted average of window and wall surface temperatures is calculated with
-EMS subroutines.\noteDT{@JK: is this last statement correct?}
+EMS subroutines.
+% \noteDT{@JK: is this last statement correct?}
 
@@
 simulations is made. For cooling, a discrepancy can be seen between co-
-simulation and solo EnergyPlus. Co-simulation results in a 20.2\% decrease in
+simulation and solo EnergyPlus. Co-simulation results in a 15.5\% decrease in
 predicted cooling energy, as seen in Figure
@@
 heating months is noticed resulting an overall increase of heating prediction
-of 4.8\% due to co-simulation. The exchange of long wave radiation for this
+of 6.5\% due to co-simulation. The exchange of long wave radiation for this
 particular site is substantial due to the proximity of surrounding buildings.
@@
 on the cooling side than the theoretical case study.
+
+When comparing the solo and co-simulated models to the measured data, it is noticed that 
+cooling energy is over-predicted by the solo simulation by 4\%, while co-simulation under-predicted 
+by 11.1\%. For heating energy, co-simulation was able to bring the predicted value to within 2\% of 
+the measured value for the year, an improvement as compared to the solo simulation, which was 8.5\% less than the measured value.
 
@@
 With a particularly strong visual and formal identity, the SwissTech
-Convention Centre (STCC) is clearly the key protagonist.\noteDT{move main
-sentence to start of paragraph} Applied with essential functions for the
+Convention Centre (STCC) is clearly the key protagonist. Applied with essential functions for the
 region, the building has definitely become the new landmark. Designed as a
-Minergie\noteDT{ref?} building, it includes modern energy conversion
+Minergie building, it includes modern energy conversion
 technologies to reduce its energy consumption. The focus of the co-simulation
@@
 retail and service areas.
+% \noteDT{move main
+% sentence to start of paragraph}
 
@@
 improving the controls. Therefore, due to unreliable monitoring data, the
-calibration step of the model has been unfortunately\noteDT{delete:
-"unfortunately". we are cold hard scientists battling the evil nemesis that is
-entropy and his plan to suffocate everyone with the inevitable heat death of
-the universe. we have no time for lame excuses. we just abandon. no regrets.
-thug life!} abandoned.\\
+calibration step of the model was not undertaken.\\
+% \noteDT{delete:
+% "unfortunately". we are cold hard scientists battling the evil nemesis that is
+% entropy and his plan to suffocate everyone with the inevitable heat death of
+% the universe. we have no time for lame excuses. we just abandon. no regrets.
+% thug life!}
 
@@
 that the HPI and theoretical case studies due to the number and proximity of
-surrounding buildings is not as large. \noteCM{I'm planning to elaborate on
-these sections
-but am struggling to interpret the results other than just "co-sim and solo
-are different" -- what do you guys think?}\noteDT{well, for a start, the two
-case studies differ in the amount of LWR radiation. we could quantify that?
-also, the number of surfaces of the e+ model with viewfactor to surrounding
-buildings?}
+surrounding buildings is not as large. Long wave radiation exchange in this situation 
+doesn't have as large of an impact on the heating and cooling calculations.
+% \noteCM{I'm planning to elaborate on
+% these sections
+% but am struggling to interpret the results other than just "co-sim and solo
+% are different" -- what do you guys think?}\noteDT{well, for a start, the two
+% case studies differ in the amount of LWR radiation. we could quantify that?
+% also, the number of surfaces of the e+ model with viewfactor to surrounding
+% buildings?}
 
@@
 
-\subsection{CitySim co-simulation results}
+% \subsection{CitySim co-simulation results}
 
-When focusing solely on CitySim, a 26.9\% decrease in heating energy is
-observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}. A 49.1\%
-decrease in heating energy is observed, as seen in Figure
-\ref{fig:qn_citysim_cosimvssolo_heating}. These results align with the
-previous comparison of EnergyPlus and CitySim engines. The substantial
-differences between solo and co-simulation in these cases is a result of
-EnergyPlus transferring the heating and cooling load values at each time step. \noteCM{Jerome -- I need some help
-interpreting these results -- you mentioned that there is an expected delta
-between citysim and energyplus in previous studies. Can you help elaborate on
-that?}
+% When focusing solely on CitySim, a 26.9\% decrease in heating energy is
+% observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}. A 49.1\%
+% decrease in heating energy is observed, as seen in Figure
+% \ref{fig:qn_citysim_cosimvssolo_heating}. These results align with the
+% previous comparison of EnergyPlus and CitySim engines. The substantial
+% differences between solo and co-simulation in these cases is a result of
+% EnergyPlus transferring the heating and cooling load values at each time step. \noteCM{Jerome -- I need some help
+% interpreting these results -- you mentioned that there is an expected delta
+% between citysim and energyplus in previous studies. Can you help elaborate on
+% that?}
 
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.55]{figures/QN_CitySim_Cooling}
-\caption{Quartier Nord CitySim Co-Simulation vs. Solo for Cooling}
-\label{fig:qn_citysim_cosimvssolo_cooling}
-\end{figure}
+% \begin{figure}[H]
+% \centering
+% \includegraphics[scale=0.55]{figures/QN_CitySim_Cooling}
+% \caption{Quartier Nord CitySim Co-Simulation vs. Solo for Cooling}
+% \label{fig:qn_citysim_cosimvssolo_cooling}
+% \end{figure}
 
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.55]{figures/QN_CitySim_Heating}
-\caption{Quartier Nord CitySim Co-Simulation vs. Solo for Heating}
-\label{fig:qn_citysim_cosimvssolo_heating}
-\end{figure}
+% \begin{figure}[H]
+% \centering
+% \includegraphics[scale=0.55]{figures/QN_CitySim_Heating}
+% \caption{Quartier Nord CitySim Co-Simulation vs. Solo for Heating}
+% \label{fig:qn_citysim_cosimvssolo_heating}
+% \end{figure}
 
@@
 Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
-Energy Modeling (UMEM) project. The authors would also like to acknowledge
- Emanuel Thoma for his work in developing the geometric models.% %
+Energy Modeling (UMEM) project. 
+% The authors would also like to acknowledge
+ % Emanuel Thoma for his work in developing the geometric models.% %
  % \noteDT{We also

### 2016-12-19 coverletter/CoverLetter.tex
DT review comments

%\documentclass[ngerman]{ethbrief3}
\documentclass[english]{ethbrief3}
%\documentclass[ngerman,DepLogo]{ethbrief3}
%\documentclass[english,DepLogo]{ethbrief3}
%\documentclass[ngerman,ETHUZH]{ethbrief3}
%\documentclass[english,ETHUZH]{ethbrief3}
% \usepackage{silence}
% \WarningFilter{latex}{Option pagecontinue is false}
\usepackage[utf8]{inputenc}
\usepackage[pdfborder={0 0 0},pdftex]{hyperref}
\usepackage{graphicx}

% automatic language support (Niklas Beisert)
\EthLang{
  \RequirePackage[document]{ragged2e}% Corrects hyphenation in german
  \RequirePackage{ngerman}
  \PassOptionsToPackage{ngerman}{babel}
}{
  \PassOptionsToPackage{english}{babel}
}

% Declaration of the personal data
    \EthFirstUnitName{\EthLang{1. Zeile Organisationseinheit}{Institute of Technology in Architecture}}
    % \EthSecondUnitName{\EthLang{2. Zeile Organisationseinheit}{Future Cities Laboratory}}
    \EthName{ETH \Zurich} % if to change the town see below
    \EthPersName{\EthLang{Herr Max Mustermann}{Mr. Clayton Miller}}
    \EthPersPosition{\EthLang{Funktion}{Researcher}}
    \EthOffice{\EthLang{Geb\"aude Raum}{Future Cities Laboratory}}
    \EthStreet{\EthLang{Strasse Hausnummer}{1 CREATE Way \#06-01}}
    \EthTown{Singapore} % if to change the town see below
%    \EthAddress{\EthLang{Freie\\Adresseingabe}{freestyle\\address}}
% --- country optional, typical if sendig outside CH
%     \EthLang{}{\EthCountry{\Switzerland}} % only the country in english version
     %\EthCountry{Singapore} % in german and english version
     \EthPhone {(Worldwide Contact Number):\\+1 402 403 0090}
%     \EthPhone {+41 44 632 bb bb} % secondary phone, fax, \ldots
%     \EthFax   {+41 44 632 aa ab}
%     \EthMobile{+41 7 59 aa bbb}
\EthLang{
     \EthEmail{miller.clayton@arch.ethz.ch}
     \EthWeb{www.systems.arch.ch}
}{
     \EthEmail{miller.clayton@arch.ethz.ch}
     \EthWeb{www.systems.arch.ch}
}
%     \EthPersInfo{\EthLang{Zus\"atzliche\\Daten}{additional\\data}}

% --- end of declaration of the personal data ---

% --- load the signature-graphic
%\signaturefile[0.5cm]{\includegraphics[height=1cm]{mysig}} % include a signature file
\signature{Clayton Miller}

%\makelabels         % to get the address for an envelope
%\date{July, 3 2013} % be free to define the date manually
% --- multilinguale Ortsnamen, \Zurich definiert als Standard
\location{Singapore}  % be free to define the location manually

\subject[]{Journal Paper Submission}

\recipient{
Ian Beausoleil-Morrison \\
Jan Hensen\\
Co-Editors\\
Journal of Building Performance Simulation\\}

\begin{document}
\opening{Dear Dr. Beausoleil-Morrison and Dr. Hensen:}

The attached manuscript entitled “Urban and building multiscale co-simulation: case study implementations on two university campuses” is an original research article that I would like to submit for consideration in Journal of Building Performance Simulation. This paper outlines the process of co-simulation between EnergyPlus and CitySim for two campuses. This paper builds upon the work from two previous conference papers and includes properly-referenced content from both papers. References of those papers are found below: \\[12pt]
Thomas, D., Miller, C., Kämpf, J., Schlueter, A., 2014. Multiscale co-simulation of EnergyPlus and CitySim models derived from a building information model, in: Proceedings of Bausim 2014: Fifth German-Austrian IBPSA Conference. Presented at the Bausim 2014: Fifth German-Austrian IBPSA Conference, IBPSA, Aachen, Germany, pp. 469–476. doi:10.13140/2.1.4639.1040\\[12pt]

Miller, C., Thomas, D., Kämpf, J., Schlueter, A., 2015. Long wave radiation exchange for urban scale modelling within a co-simulation environment, in: Proceedings of CISBAT 2015. Presented at the CISBAT 2015, CISBAT, Lausanne, Switzerland, pp. 871–876. doi:10.13140/RG.2.1.2876.4640\\[12pt]
This paper builds upon the previous research by applying the workflow to two campus case study projects. This contextual application gives a realistic analysis of how much differences between solo and co-simulations.

This paper was funded through the UMEM: Urban Multiscale Energy Modelling project from the Swiss Competence Center Energy and Mobility (CCEM).

Any questions or comments can be directed to myself as the corresponding author. I am avail-
able via email at miller.clayton@arch.ethz.ch and by phone at 1-402-403-0090.

\closing{Kind Regards,}

% Enclosures:\\
% Curriculum Vitae\\
% Reference List\\
% Research Statement\\
% Teaching Statement\\
% Unofficial Transcripts\\

%These insights will influence future design, construction, commissioning, and performance evaluation practices. 
%I believe Nebraska can become known for its building performance informatics research in addition to its already strong reputation for design and construction.

% It is through my active contacts and familiarity with Omaha and the State of Nebraska that I would be able to collect even larger data sets.
% more often applied to social media, advertising or medicine.

%I plan to undertake an academic career focused on analytics of performance data from the built and urban environments. My background includes experiences in engineering and architecture, as well as in research and entrepreneurship. In this application, I propose a teaching and research plan built upon this foundation.

%I thrive in interdisciplinary research environments. My primary advisor is an architect, my co-advisor is a computer science professor, my mentors are a robotics researcher and a mechanical engineer, and my colleagues are even more diverse. Crossing these boundaries is not trivial, and my career has a sound basis in this exact skill set.

%Sensor data are everywhere these days. As seen in the hype cycle, the Internet-of-Things concept is on many researchers' minds. Despite this fact, these ideas are not novel in the building industry; we have been connecting machines and sensors to the Internet for years. However, due to this movement's emphasis on sensor data, we rapidly realize how much more value can be extracted using new techniques. I am working at the forefront of utilizing temporal sensor data sets containing billions of measurements to improve performance, comfort and safety in buildings.

%HERE DISCUSS THE PROJECTS THAT I'M CURRENTLY COMPLETING AND THE FUNDING OPPORTUNITIES THAT I AM EXPLORING!

% It can be noticed from my CV that I am in the process of completing my Ph.D. degree. I have a deadline of June 2016 to submit my dissertation, and I plan to defend in the early Fall semester. This schedule puts me on track to be available for a faculty position in 2017. I see that the current on-line posting indicates a \emph{Planned Hire Date} of August 2016, but I'd like the opportunity to discuss further my application in the context of the Durham School's plans for expansion.

% \ps{Postscriptum}
% \encl{Research Statement\\
%  Teaching Statement}

% \cc{carbon copy}

% \newpage
% \setcounter{page}{1}
% \recipient{Address 2}
% \opening{Hallo all,}
% This is a sample for a serial letter. For the other changes please look into the file \emph{brief-sample-serial.tex}, there are only a few changes to the standard letter.

% In the moment there is only one known issue. In principal you can produce a serial letter with different pages each, at the moment I do not know, how the get in this circumstance the particular \emph{number of the last page}. This number could appear to be not the right one. The work-around is not to print the page-numbering (starting on the second page). Please uncomment in \emph{ethbrief3.cls} the following line then:

% \begin{verbatim}
% \hfill\raggedleft\mbox{\eth@xiiiv\ethpagename~\thepage~/~\lastpageref*{pagesLTS.arabic}}
% \end{verbatim}

% If anybody could help for this problem, I would like to include this in the following subversion.

% \closing{Have a nice day}
\end{document}

### 2016-12-19 latex/UMEM_CoSim.tex
DT review comments

@@
     to the both the CitySim simulation and EnergyPlus engines. The results
-    show that coupling of EnergyPlus with CitySim resulted in a -20\% and
-    -7.5\% impact on cooling consumption and a +2.8\% and +4.8\% impact on
+    show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and
+    -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on
     heating consumption. Challenges encountered with the urban scale
@@
  Long Wave Radiation & Environmental Radiant Temp. & Calculated $T_{env}$ from the sky,\\&& ground, and surrounding surfaces \\
- & Environmental Radiant Heat & Calculated $h_{env}$ from the sky,\\&& ground, and surrounding surfaces \\
- & Gain Coefficient \\
+ & Environmental Radiant Heat  & Calculated $h_{env}$ from the sky,\\
+ & Gain Coefficient & ground, and surrounding surfaces \\
+
  \hline
@@
 knowledge first and working towards equilibrium between measured and
-simulated. An appropriate balance between the effort of implementation and value
+simulated. There is an appropriate balance between the effort of implementation and value
 generated through the calibration process.
@@
 campus was chosen in this case study due to the amount and quality of measured
-data available from the EMS for this building. HPI is a 2,610 sq. meter
+data available from the EMS for this building. HPI is a 2,610 square meter
 building that is made up mostly of office space and classrooms. It also
@@
 In order to perform a co-simulation of the targeted buildings, initially a
-CitySim model of the campus is developed. Through the workflow automation
+CitySim model of the campus was developed. Through the workflow automation
 process, this geometry was converted into an EnergyPlus input file as seen in
-Figure \ref{fig:HPIcampus}. The EnergyPlus input file is then used as an input
+Figure \ref{fig:HPIcampus}. The EnergyPlus input file was then used as an input
 to execute EnergyPlus solo and co-simulation processes for the purpose of
@@
 simulations is made. For cooling, a discrepancy can be seen between co-
-simulation and solo EnergyPlus. Co-simulation results in a 15.5\% decrease in
-predicted cooling energy, as seen in Figure
+simulation and solo EnergyPlus. Co-simulation decreases the predicted cooling energy by 15.5\%, as seen in Figure
 \ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
@@
 heating energy and a 4-11\% decrease in cooling energy \citep{Miller:2015vk}.
-The results from this scenario are less extreme on the heating side and more
+The results from this case study are less extreme on the heating side and more
 on the cooling side than the theoretical case study.
@@
 hotel. As a public space, this ensemble is organized around the central plaza as
-seen in Figure \ref{fig:quartier_nord_1}).
+seen in Figure \ref{fig:quartier_nord_1}). With a particularly strong visual and formal identity, the SwissTech
+Convention Centre (STCC) is clearly the key protagonist.  Designed as a
+Minergie building, it includes modern energy conversion
+technologies to reduce its energy consumption. The focus of the co-simulation
+is realized on the STCC, simulated with the nearby buildings for housing,
+retail and service areas.
 
@@
 
-With a particularly strong visual and formal identity, the SwissTech
-Convention Centre (STCC) is clearly the key protagonist. Applied with essential functions for the
-region, the building has definitely become the new landmark. Designed as a
-Minergie building, it includes modern energy conversion
-technologies to reduce its energy consumption. The focus of the co-simulation
-is realized on the STCC, simulated with the nearby buildings for housing,
-retail and service areas.
+% Applied with essential functions for the
+% region, the building has definitely become the new landmark.
+
 % \noteDT{move main
@@
 \ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less pronounced
-that the HPI and theoretical case studies due to the number and proximity of
+than the HPI and theoretical case studies due to the number and proximity of
 surrounding buildings is not as large. Long wave radiation exchange in this situation 
@@
 simulation and solo environments are within range of previous theoretical
-models. More reliable results of the magnitude of differences between the
+models. The results show that there is a noticeable impact 
+More reliable results of the magnitude of differences between the
 simulation techniques can be extracted from these real-world scenarios.

### 2016-12-19 latex/UMEM_CoSim_Anonymous.tex
DT review comments

--- 2016-12-19 latex/UMEM_CoSim.tex
@@
 
-\subsection{Acknowledgements}
-The authors would like to acknowledge the ETH Z\"urich Campus Facilities
-Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
-Thoma for their assistance in this project. This research was funded by the
-Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
-Energy Modeling (UMEM) project. 
+% \subsection{Acknowledgements}
+% The authors would like to acknowledge the ETH Z\"urich Campus Facilities
+% Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
+% Thoma for their assistance in this project. This research was funded by the
+% Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
+% Energy Modeling (UMEM) project. 
 % The authors would also like to acknowledge

### 2016-12-20 coverletter/CoverLetter.tex
Paper submission

@@
 
-The attached manuscript entitled “Urban and building multiscale co-simulation: case study implementations on two university campuses” is an original research article that I would like to submit for consideration in Journal of Building Performance Simulation.
+The attached manuscript entitled “Urban and building multiscale co-simulation: case study implementations on two university campuses” is an original research article that I would like to submit for consideration in the Journal of Building Performance Simulation.
 This paper outlines the process of co-simulation between EnergyPlus and CitySim for two campuses.
@@
 
-Any questions or comments can be directed to myself as the corresponding author. I am avail-
-able via email at miller.clayton@arch.ethz.ch and by phone at 1-402-403-0090.
+Any questions or comments can be directed to myself as the corresponding author. I am available via email at miller.clayton@arch.ethz.ch and by phone at 1-402-403-0090.
 

### 2016-12-20 initialsubmission/UMEM_CoSim_Anonymous.tex
Paper submission

--- 2016-12-19 latex/UMEM_CoSim_Anonymous.tex
@@
 
-\author{Clayton Miller\textsuperscript{a}%
-$^{\ast}$\thanks{$^\ast$Corresponding author. Email: miller.clayton@arch.ethz.ch}, 
-Daren Thomas\textsuperscript{a},
-J\'er\^ome K\"ampf\textsuperscript{b},
-and Arno Schlueter\textsuperscript{a}\\
-\vspace{6pt}
-\textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
-\textsuperscript{b}{\em Solar Energy and Building Physics Laboratory (LESO-PB), Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland}
-\received{Submission for review on April 30, 2016} %TARGETED!
-}
+% \author{Clayton Miller\textsuperscript{a}%
+% $^{\ast}$\thanks{$^\ast$Corresponding author. Email: miller.clayton@arch.ethz.ch}, 
+% Daren Thomas\textsuperscript{a},
+% J\'er\^ome K\"ampf\textsuperscript{b},
+% and Arno Schlueter\textsuperscript{a}\\
+% \vspace{6pt}
+% \textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
+% \textsuperscript{b}{\em Solar Energy and Building Physics Laboratory (LESO-PB), Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland}
+% \received{Submission for review on April 30, 2016} %TARGETED!
+% }
 

### 2017-04-28 latex_reviewcomments/ReviewCommentsResponse.tex
Added review comments material

\documentclass[answers,12pt]{exam}
\usepackage{xcolor}
\definecolor{SolutionColor}{rgb}{0.1,0.3,1}
\usepackage{lipsum}

\renewcommand{\thequestion}{\alph{question} }
\renewcommand\questionlabel{\llap{\thequestion)}}

%\pointsinrightmargin
%\boxedpoints
\unframedsolutions
\shadedsolutions
\definecolor{SolutionColor}{rgb}{0.9,0.9,1}
\renewcommand{\solutiontitle}{}

\usepackage{titling}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

% \setlength{\droptitle}{-10em}   % This is your set screw

\title{Review Comment Responses to Journal of Building Performance Simulation Submission}
\subtitle{Paper Title: Urban and building multiscale co-simulation: case study implementations on two university campuses 
}
% \email{miller.clayton@arch.ethz.ch}
\author{Clayton Miller, Daren Thomas, J\'er\^ome K\"ampf, Arno Schlueter}

% \subtitle{ETH Z\"urich, Institute of Technology in Architecture (ITA), Architecture and Sustainable Building Technologies (SuAT)}
% \subtitle{*Corresponding author: Phone: +1-402-403-0090, miller.clayton@arch.ethz.ch}

\begin{document}

\maketitle

% \textcolor{red}{Red text is internal notes of things to be done}

% Black text shaded in blue is the formal responses to the reviewers

\section{Review 1}

\subsection{General comments from reviewer}
This is a valuable paper that pinpoints the differences in estimated energy consumption between simulations of solo building and buildings modeled in an urban context.  The paper relies on am emerging simulation workflow and extends its application to two real-building scenarios.  Work by the authors and others is amply referenced; together the text and the references provide excellent explanation of the linkages between building and city simulations.

The paper can be improved in a large number of small ways, as indicated in specific comments.  In particular, the central figures. 10, 11, 14 and 15 and accompanying text need attention to improve clarity and correct inconsistencies between text and images.  The suggested improvements should be straightforward.

\subsection{Response to general comments}
\begin{solution}
Thank you for the comments on the importance and value of the paper and we welcome the comments and feedback to be covered in this review.
\end{solution}

\subsection{Revision items}
\begin{questions}

\question 1. p. 1.  Abstract.  The abstract quantifies percentage “impacts” of co-simulation of heating and cooling consumption but does not establish a reference: percentage change relative to what base case?  The abstract promises a discussion of “strengths and weaknesses of the developed process” but the paper does not include a discussion section and the conclusion does not summarize strengths and weaknesses. 
\begin{solution}
\textcolor{red}{Finish discussion section}

The abstract has been updated to reflect that the baseline of these comparison metrics are the EnergyPlus solo simulations of each of the engines.

A discussion section has been added to address the strengths and weaknesses mentioned in the abstract -- advantages are related to the enhancement of each of the 
engines and disadvantages related to the increase in computing power needed to undertake the process.

% \emph{The majority of these changes can be found in lines X-X.}
\end{solution}

\question  2. p. 1. Introduction. Lines 3-5 state that “2.5 billion people are expected to join cities throughout the world.” What is the associated time frame – i.e., by what year? 
\begin{solution}
\textcolor{red}{Confirm the following is true:} The United Nations World Urbanization prospectus projected that figure by 2030 -- this fact has been updated in the introduction
\end{solution}

\question 3. p. 1, line 13. Please consider a lower-case “S” for solver.   
\begin{solution}
Lower-case "S" has been used.
\end{solution}

\question 4. p. 1, lines 21-23.  The text states that a single equation approximates the total mass flow rate required to meet the sensible and later loads of each building.”  In this reviewer’s experience, there are separate mass-conservation equations for air and water vapor as well as an energy-balance equation.  Perhaps the authors could succinctly amplify their statement. 
\begin{solution}
\textcolor{red}{Jerome -- is this statement regarding CitySim correct? If so, how can we justify it with respect to this comment?} 
\end{solution}

\question 5. p. 2, line 40.  Please replace “phenomenon” with the plural “phenomena.” 
\begin{solution}
Correction made.
\end{solution}

\question 6. p. 2, line 60.  The text appears to limit the second case study to CitySim simulation output but the abstract and, later, line 224, include analysis of EnergyPlus output. 
\begin{solution}
The reference to the EnergyPlus simulation for this case study was removed.
\end{solution}

\question 7. p. 3.  Figure 1 includes acronyms not defined in the text or caption. 
\begin{solution}
{red}{Does anyone know what COSMO-CMM, UMC Model, and BIS stand for?} 
Explanation of the acronyms is now included in the text.
\end{solution}

\question 8. p. 3, lines 62-68.  For grammatical consistency, the achievements should all start with verbs (automate, co-simulate, implement) or nouns (automation, co-simulation, implementation).  The third achievement should specify what simulation model is being calibrated. 
\begin{solution}
Points were revised to all be verbs and the second scenario was indicated as the model being calibrated.
\end{solution}

\question 9. p. 3, lines 88-89.  Please note that Bueno et al. 2013 generated urban weather with a nodal model and did not directly couple EnergyPlus to a nodal representation of the urban canopy layer.  The accuracy of this approach depends on how faithfully users and the model represent the buildings that will later be simulated in detail in EnergyPlus with the modified weather file. 
\begin{solution}
It was noted that this study doesn't directly couple the simulation engines, but only connects them through a modified weather file.
\end{solution}

\question 10. p. 4, line 97.  Please consider “earliest design possible and it can be used…” or “earliest design possible that can be used….” 
\begin{solution}
Change made to the latter suggestion
\end{solution}

\question 11. p. 4, Figure 2. The test explains the paths associated with the dotted vertical lines and solid lines.  Presumably the use of the latter is intended to show the co-simulation path but the use of the dashed line in the related Figure 3 is not clear.  Further, Figure 3 is quite small; at minimum, the CItySIm block with its italicized vertical text, fmilib, could be modestly larger.  
\begin{solution}
\textcolor{red}{Daren -- what was our logic behind the dotted lines?}
\end{solution}

\question 12. p. 5, lines 145-154.  The text states that “several key urban-scale weather variables are send to EnergyPlus from CitySim” but does not succinctly state how CItySIm calculates these variables.  The text might indicate why the authors consider the CitySim occupancy model to be more robust.  Finally, as a minor point of English grammar, please consider removing the comma after “urban environments” in line 150 or replacing “that” with “which.” 
\begin{solution}
\textcolor{red}{Jerome -- can you explain quickly in the text how CitySim calculated these variables and why its better than using EnergyPlus's weather file inputs?}
\end{solution}

\question 13. p. 6.  The text on this page (or, apparently, any other) does not refer to Tables 1 and 2. 
\begin{solution}
References for Table 1 and 2 are no included in the text pertaining to those variables.
\end{solution}

\question 14. p. 7, line 178.  Equation 2 lacks a view factor, as is included in Evins et al., Equation 9 and in the EnergyPlus Engineering Reference. 
\begin{solution}
\textcolor{red}{Jerome and Daren - can you confirm the accuracy of the equations?}
\end{solution}

\question 15. p. 7, lines 195-196.  The sentence beginning with “An automated workflow” lacks a verb.  Please consider replacing “to tie” with “ties.” 
\begin{solution}
Correction made.
\end{solution}

\question 16. p. 9, line 215.  Please consider replacing “compare” with “quantify,” given that the sentence does not establish the basis of comparison (compare what with what)). 
\begin{solution}
Correction made.
\end{solution}

\question 17. p. 10. Section 3.2.  The text states that the campus “geometry was converted into an EnergyPlus input file as seen in Figure 7.  However, this figure does not clearly indicate what geometry was included in the IDF and the caption states that the HPI building was modeled in Open Studio.   
\begin{solution}
The caption for Figure 7 has been updated to clarify the situation in which the HPI building was extracted from the CiytSim model, however it is illustrated using
OpenStudio due to that software's rendering capabilities. The caption also clearly states which building is being simulationed.
\end{solution}

\question 18. p. 10, lines 246-248.  Please consider replacing “are screened” with “were screened” and removing the hyphen after plug. 
\begin{solution}
Correction made.
\end{solution}

\question 19. p. 10, section 3.3.  Either the text (lines 245-252) or the caption for Figure 8 should say a bit more (a sentence would be adequate) about the clustering process.  For example, the caption could note that the rows for each month refer to days of the week (if this is true) and could name (describe) each of the clusters (i.e., clusters that nominally align with weekdays, Saturdays and Sundays/school holidays). 
\begin{solution}
The caption for Figure 8 was revised significantly to describe what the reader is seeing in the typical average profiles on the left and the days corresponding with
each cluster on the right. Text was added in the preceding paragraphs that briefly describe the significance of each of the clusters.
\end{solution}

\question 20. p. 10., lines 253-259.  Please rewrite the sentence to avoid “compared … to create… scenario for comparison.” What is meant by “measurements were deemed most accurate during the appropriate seasons?”
\begin{solution}
The first sentence of that paragraph was rewritten to avoid the use of "comared" and "create a scenario for comparison". The sentence pertaining to the seasonal nature of the data analysis was removed as it didn't add any information to the fact that only heating and cooling seasonal data was used for each calibration.
\end{solution}

\question 21. p. 11, lines 261-262.  The NMBE for heating and cooling are exactly the same and the NMBE for cooling is not in accord with the bar charts in Figure 9. 
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\question 22. p. 11, section 3.4.  Please see the following comments for the two associated figures.  In addition, the presentation of results from the study of Miller et al. is not clear.  Does the Miller study compare solo and co-simulation results?  If so, which results are the reference for the percentage changes? Should the reader conclude that the differences between Miller and this study are comparable (which is comforting) or that deviations are significant, in which case they should be explained. 
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\question 24. p. 12, Figure 11.  The text states Figure 11 shows differences in predicted heating consumption and notes there is a consistent offset across days in January.  Figure 11 shows hourly variations for presumably averaged days and single points for each month; in short, variations across days cannot be discerned.  Are these variations important to the comparison?  The order of the bars matches Figure 10 but disagrees with Figure 9.  The text compares co-simulation with measurement (using the latter as the reference, which seems appropriate) and shows 2\% annual difference but the numbers over the bars appear to compare co-simulation and measurement with solo simulation and show 6.5\% difference.  As in Figure 11, the numbers (not percentages) over the bars are not explained. 
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\question 25. p. 12, section 3.5.  The text should include a reference to the Minergie standard and the caption or image in Figure 12 should identify the STCC building. 
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\question 
26. p. 13, line 308.  Please explain SIA and/or provide an appropriate reference.   
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\question 
27. p. 13, lines 310-313.  The text states that the CItySIm model was created from a DXF file from EnergyPlus.  Was this export used solely for the STCC building or was the remainder of the Quartier Nord as shown in Figure 13 designed in Open Studio? 
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\question 
28. P. 13, lines 316-322.  The reference in the text for percentage changes is the EnergyPlus simulation but Figures 14 and 15 place the percentages (with opposite sign) about the solo simulations.  The text states that discrepancies between solo and co-simulations are due to differences in calculation of heating and cooling loads.  Please elaborate. 
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\question 
29. P. 14, section 3.8.  The text states that the Quartier Nord building was also simulated. This is a bit confusing because Quartier Nord previously referred to the complex.  Does the building refer to the building on the right in Figures 12 and 13 – i.e., everything except the STCC?  The text also states that differences between solo and co-simulations are small because the surroundings are sparse.  If this is the case, would one expect better agreement between solo and co-simulations for the neighboring STCC?  Also, please consider replacing “due to” with “because” in line 327. 
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\question 
30. p. 15.  Conclusion.  There is no summary of strengths and weakness of the process presented in the paper and the future work is limited only to more practical implementation.  Is there nothing to improve? 
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\question 
23. p. 11, Figure 10. The bar chart in Figure 10 is unnecessarily confusing.  Please consider aligning the three bars in the same order as in Figure 9.  While the scale is acceptable, it requires careful attention to the exponent to compare Figure 9 (1e5) with Figure 10 (1e4).   Why is the reference the solar simulation and not measurement?  And what are the numbers, to four significant digits, above the bars?  The text states that the solo simulation over-predicted cooling energy by 4.1\%.  Is this the same as showing that the measured data were 4.1\% less than the solo simulation?  In other words, is measurement or solo simulation in the denominator of the percentage change?  For example, if one quantity is 150 and the other 100, the first is 50\% higher than the second and the second is 33.3\% lower than the first.  Also, the text states that the co-simulation under-predicted cooling by 11.1\%, which is not what is shown in the bar graph.
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\question 
31. p. 16. The first and last references, by Miller et al. and Zhang et al., lack volume and page numbers.  Throughout the reference section, the authors should consider consistency in use of initials versus given names.   
\begin{solution}
% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
\end{solution}

\pagebreak
\section{Review 2}

\subsection{General comments from reviewer}
This is a nice study in a series of studies that use institutional buildings for demonstration of different co-simulation strategies for modeling of urban environments and building energy consumption. Here are several review comments that are mostly focused on the fact that actual execution of co-simulation was not discussed in details; the study mostly presented the co-simulation workflow and results.

\subsection{Response to general comments}
\begin{solution}
Thank you for taking time to perform this review and for the in-depth comments related to discussing the execution of the actual co-simulation.
\end{solution}

\subsection{Revision items}

\question 
(1) At the top of page 2, the paper describes advantages of EnergyPlus. However, it is not clear why this simulation engine is used when several others could perform the presented analyses. It is important to know what technical aspects of the co-simulation procedure specifically drove the authors to use EnergyPlus. 
\begin{solution}

\end{solution}

\question 
(2) The actual co-simulation, which is the main contribution of this study is not well discussed. Specifically, the paper needs to describe: (a) frequency of data exchanges, (b) whether any data averaging took place, (c) whether the numerical scheme is stable and grid independent, (d) what is the time step for each engine?, (e) what is the simulation time?, (f) are these annual, monthly, or daily simulations?, (g) what convergence criterion was used? 
\begin{solution}
a) \\
b) \\
c) \\
d) \\
e) \\
f) \\
g) \\
\end{solution}

\question 
(3) Figure 3, Section 2.3, and Figure 4 are the same or similar to author’s previous publication. A citation would be sufficient. 
\begin{solution}

\end{solution}

\question 
(4) In Section 3.3, the paper needs many more details on the calibration process, including the specification of all calibration steps undertaken, rather than just cursory listing some of the steps. 
\begin{solution}

\end{solution}

\question 
(5) Please, discuss results in Figure 10. What are the numerical or physical reasons for the “solo” case to underperform? 
\begin{solution}

\end{solution}

\question 
(6) The conclusions need content on co-simulation execution challenges and how they were overcome during the course of that this study.
\begin{solution}

\end{solution}
\end{questions}
\end{document}

### 2017-04-28 latex_compared/UMEM_CoSim_corrected.tex
Added review comments material

--- 2016-12-19 latex/UMEM_CoSim.tex
@@
     -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on
-    heating consumption. Challenges encountered with the urban scale
+    heating consumption as compared to solo simulations. Challenges encountered with the urban scale
     calibration and the strengths and weaknesses of the developed process are
     discussed.
-    % \noteDT{Clayton, can you
-    % get your editor to do hard line wrapping? all your paragraphs are a single
-    % line which breaks the diff model of GitHub and makes editing in VIM super
-    % hard...}
 \end{abstract}
-
-%Taken out of the abstract: A significant amount of model input information was extracted for the creation of both models from a building information model (BIM) of the campus.
 

### 2017-04-28 latex_reviewcomments/LetterToEditor.tex
Added review comments material

% \documentclass[sigleft]{letter}
% \usepackage{hyperref}
% \signature{Clayton Miller}
% \address{John-von-Neumann-weg 9 \\ Building HPZ \\ Z\"urich CH-8093}
% \begin{document}

% \begin{letter}{Editor-in-Chief \\ Journal of Automation in Construction \\ Glenn L. Martin Hall 1188
% \\ University of Maryland \\ College Park, MD 20742, U.S.A}
% \opening{Dear Dr. Skibniewski:}

% Please find our responses to the 26 questions and comments made by the 3 referees. Overall we believe that we have fully addressed each issue individually in a means that hopefully satisfies the requirements of the journal.

% Each reviewers general comments were responded to and their individual questions and comments were addressed in detail in this document as well as a two revised manuscript documents: one in which the original manuscript is marked up with the changes and one that is a final draft version with all changes and additions.

% \closing{Best Regards,}

% % \ps

% % P.S. You can find the full text of GFDL license at
% % \url{http://www.gnu.org/copyleft/fdl.html}.

% % \encl{Copyright permission form}

% \end{letter}
% \end{document}

% Template from: http://tex.stackexchange.com/questions/13167/positioning-signature-on-left-in-letter?rq=1

\documentclass[11pt,stdletter,sigleft]{newlfm}
\usepackage{charter}

\widowpenalty=1000
\clubpenalty=1000

\newlfmP{headermarginskip=15pt}
\newlfmP{sigsize=25pt}
\newlfmP{dateskipafter=25pt}
\newlfmP{addrfromphone}
\newlfmP{addrfromemail}
\PhrPhone{Phone}
\PhrEmail{Email}

\namefrom{Clayton Miller \\ ITA Doctorate Fellow}

\addrfrom{John-von-Neumann-weg 9 \\ Building HPZ \\ Z\"urich CH-8093}
\phonefrom{+41 78 971 72 50}
\emailfrom{miller.clayton@arch.ethz.ch}

\addrto{Ian Beausoleil-Morrison \\
Jan Hensen\\
Co-Editors\\
Journal of Building Performance Simulation\\}
% \\ University of Maryland \\ College Park, MD 20742, U.S.A}
\begin{document}

\opening{Dear Dr. Beausoleil-Morrison and Dr. Hensen:}
\closeline{Kind Regards,}

\begin{document}
\begin{newlfm}
Please find our responses to the X questions and comments made by the referees. Overall, we believe that we have fully addressed each issue individually in a way that satisfies the requirements of the journal review process.

Each reviewer's general comments were responded to and their individual questions and comments were addressed in detail in this document. The responses are shaded blue following each reviewer's comments and questions. Included also in this submission is the revised manuscript document that is a final draft version with all changes and additions incorporated.

Please contact me with any further comments or concerns regarding this resubmission.

\end{newlfm}
\end{document}

### 2017-04-28 latex_reviewcomments/ReviewCommentsResponse.tex
updated review reponses

@@
 \begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
 \end{solution}
@@
 \begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
+\textcolor{red}{Confirm in the Juypter notebook}
 \end{solution}
@@
 \begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
+\textcolor{red}{Update graphics}
 \end{solution}
@@
 \begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
+\textcolor{red}{Add Minergie as a reference}
 \end{solution}
@@
 \begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
+\textcolor{red}{Add SIA and explain}
 \end{solution}
@@
 \begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
+\textcolor{red}{Jerome -- any feedback on this?}
 \end{solution}
@@
 \begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
+\textcolor{red}{Confirm numbers in graphics}
 \end{solution}
@@
 \begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
+\textcolor{red}{Jerome -- can you clarify this?}
 \end{solution}
@@
 \begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
-\end{solution}
-
-\question 
-23.
-p.
-11, Figure 10.
-The bar chart in Figure 10 is unnecessarily confusing.
-Please consider aligning the three bars in the same order as in Figure 9.
-While the scale is acceptable, it requires careful attention to the exponent to compare Figure 9 (1e5) with Figure 10 (1e4).
-Why is the reference the solar simulation and not measurement?
-And what are the numbers, to four significant digits, above the bars?
-The text states that the solo simulation over-predicted cooling energy by 4.1\%.
-Is this the same as showing that the measured data were 4.1\% less than the solo simulation?
-In other words, is measurement or solo simulation in the denominator of the percentage change?
-For example, if one quantity is 150 and the other 100, the first is 50\% higher than the second and the second is 33.3\% lower than the first.
-Also, the text states that the co-simulation under-predicted cooling by 11.1\%, which is not what is shown in the bar graph.
-\begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
+\textcolor{red}{Update with strengths and weaknesses in the discussion}
 \end{solution}
@@
 \begin{solution}
-% \textcolor{red}{Show a detailed example of discord inspection in the UWC case study -- in the discussion section}
+\textcolor{red}{Update references}
 \end{solution}
@@
 \begin{solution}
+\textcolor{red}{Update references}
 
@@
 \begin{solution}
+\textcolor{red}{Daren -- can you take a stab at these?}
 a) \\
@@
 \begin{solution}
-
+We chose to replicate these figures in this publication to clarify the bigger picture of the scope of the study. We believe these figures help to put the current study in context in a better way.
 \end{solution}
@@
 \begin{solution}
-
+\textcolor{red}{Explain the calibration process in much more detail}
 \end{solution}
@@
 \begin{solution}
+\textcolor{red}{Why are there differences?}
 
@@
 \begin{solution}
+\textcolor{red}{Strenghts and weaknesses and advantages/disadvantages in the}
 

### 2017-05-19 latex_corrected/UMEM_CoSim.tex
addresses review one, item k) part one (Figure 2)

--- 2017-04-28 latex_compared/UMEM_CoSim_corrected.tex
@@
     campus. In the second case study, the co-simulation results are compared
-    to the both the CitySim simulation and EnergyPlus engines. The results
+    to the both the CitySim simulation engine. The results
     show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and
     -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on
-    heating consumption as compared to solo simulations. Challenges encountered with the urban scale
+    heating consumption as compared to solo simulations of each of the engines. Challenges encountered with the urban scale
     calibration and the strengths and weaknesses of the developed process are
@@
 \section{Introduction}
-% \noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}
+\noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}
 
@@
 world at an unprecedented rate. A transition from urban to rural is underway and
-2.5 billion people are expected to join cities throughout the world
+2.5 billion people are expected to join cities throughout the world by the year 2030
 \citep{UnitedNations:2014vn}. Expansions of entire districts and even cities
@@
 optimized for urban-scale simulation. CitySim is an urban performance
-simulation engine that comprises a Solver module as well as a graphical user
+simulation engine that comprises a solver module as well as a graphical user
 interface. It focuses on the energy flows of multiple simplified building
@@
 input parameters necessary and run-times of the engines themselves. This focus
-results in certain deficiencies concerning modeling various phenomenon.
+results in certain deficiencies concerning modeling various phenomena.
 For example, urban scale simulation highly simplifies the building systems and
@@
 and the urban energy model using CitySim. An overview of the larger scope is
-shown in Figure \ref{fig:UMEM} and the context of the coupling task appears as the interface between the City Energy Simulation (CES) model and the
-Building Energy Simulation (BES) model.
+shown in Figure \ref{fig:UMEM} and the context of the coupling task appears as 
+the interface between the City Energy Simulation (CES) model and the
+Building Energy Simulation (BES) model. The scales and models contained in the 
+urban environment context include the Urban-Scale Model (UC Model), the UMC model using OpenFoam, 
+and the Meteorological Meso-scalce (MM model). On the database side, Revit, global 
+information systems (GIS), and building information systems (BIS) are utilized.
 
@@
 \begin{enumerate}
-  \item Automation of the process of simultaneous meta-data extraction from a
+  \item Automate of the process of simultaneous meta-data extraction from a
   building information model (BIM) for the creation of both building and
@@
   \item Co-simulate the urban and building scale models through concurrent information exchange
-  \item Implement a simplified calibration procedure based on reconciling the
-  co-simulation output results for a target building using measured energy
+  \item Implement a simplified calibration procedure for the first scenario by 
+  reconciling the co-simulation output results for a target building using measured energy
   performance data from the campus energy information system (EIS)
@@
 models to facilitate comparison with measured sensor data
-\citep{Martin:2015fj}. EnergyPlus and the TEP Urban Canopy Model program were
-coupled to quantify the influences of urban localized weather effects
+\citep{Martin:2015fj}. While not directly coupled, EnergyPlus and the TEP Urban Canopy Model program were connected
+through a modified weather file to quantify the influences of urban localized weather effects
 on whole building simulation \citep{Bueno:2011hi} and urban weather generation
@@
 \citep{Schlueter2009}. The central philosophy behind the tool is a rapid simulation
-of the building information model from the earliest design possible and can be
+of the building information model from the earliest design possible that can be
 used throughout the life-cycle of the building including retrofit analysis
@@
 The coupling process of EnergyPlus and CitySim is shown in Figure
-\ref{fig:OverallWorkflowProcess}. First, the DPV is used to extract an
+\ref{fig:OverallWorkflowProcess}. The solid lines depict the co-simulation of EnergyPlus
+and CitySim and the dotted lines depict solo simulations of either EnergyPlus or CitySim. 
+First, the DPV is used to extract an
 EnergyPlus simulation model from the BIM. The DPV utilizes the Revit API to
@@
 to account better for the localized effects of surrounding buildings,
-geography and climate conditions. These variables include various outdoor air
-conditions such as dry bulb and wet bulb temperatures, dewpoint, humidity, wind
+geography and climate conditions. These variables are outlined in Table \ref{FMUimports}. 
+They include various outdoor air
+conditions such as dry bulb and wet bulb temperatures, dew-point, humidity, wind
 speed and direction, and direct and diffuse solar radiation. These variables
@@
 file input. CitySim is designed to account for physical phenomenon inherent to
-urban environments, that are often neglected in building-scale simulation
+urban environments that are often neglected in building-scale simulation
 environments \citep{Robinson:2004cr,Robinson:2009tm}. Long wave radiation
@@
 variables related to the calculation of heating and cooling loads of a
-targeted building. These variables are transferred due to the ability of
+targeted building. Table \ref{FMUexports} outlines this list of exchanged variables.
+These variables are transferred due to the ability of
 EnergyPlus to model more detailed building systems, schedules, ventilation and
@@
 button. This functionality allows an iterative design style informed by
-readily available simulation results. An automated work flow to tie the
+readily available simulation results. An automated work flow ties the
 various steps together and maintain the effortless iterative design process.
@@
 The first is the ETH Z\"urich Hoenggerberg campus in Z\"urich, Switzerland.
-The focus of this case study is to compare the impact of the information
+The focus of this case study is to quantify the impact of the information
 exchange through co-simulation within the EnergyPlus engine. The intent on
@@
 targeted building, in this case, was the Quartier Nord complex. The focus of
-this study was to compare the output results of both CitySim and EnergyPlus.
+this study was to compare the solo and co-simulation output results of CitySim.
 Reliable measured data for calibration is not currently available for this
@@
 \subsection{Campus case study 1: ETHZ Hoenggerberg Campus}
-% {\color{red}This section will describe the ETH Hoenggerberg case study}
-%The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland. 
 The ETH Z\"urich Hoenggerberg campus includes 32 higher education facilities
@@
 
-% The coupling process outlined is applicable with regards to a targeted building that is surrounded by an adjacent array of buildings. 
-% {\color{red}Insert the campus map illustrating the targeted buildings.}
-
 \begin{figure}[H]
@@
 simplified calibration, and then to understand the magnitude of difference
-between these simulation scenarios.% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.
+between these simulation scenarios.
 
@@
 \includegraphics[scale=0.2]{figures/HPI_Campus.png}
-\caption{The HPI building modeled with OpenStudio for Sketchup}
+\caption{The HPI building EnergyPlus model extracted from the CitySim model. The HPI building is seen
+as the light and dark brown building in the center surrounded by gray masses that represent other buildings on 
+campus. The graphic is illustrated with OpenStudio for Sketch-up.}
 \label{fig:HPIcampus}
@@
 
-% \begin{figure}[H]
-% \centering
-% \includegraphics[scale=0.2]{figures/campuscitysim}
-% \caption{Campus modeled in CitySim}
-% \label{fig:campuscitysim}
-% \end{figure}
-
 \subsection{Measured data collection and calibration}
-
 Energy data from the HPI building was collected and analyzed in the context of
-the simplified calibration procedures. The measured datasets are screened and
+the simplified calibration procedures. The measured datasets were screened and
 aggregated into typical usage profiles to be used for the lighting, plug-
@@
 energy for the HPI building. This profile was created through a filtering and
-clustering process known as \emph{DayFilter} \citep{Miller:2015kr}. This
-profile is used to set the availability schedules as inputs into the
+clustering process known as \emph{DayFilter} \citep{Miller:2015kr}. Cluster 0 represents
+the typical energy profile for Sunday, while Cluster 1 dominates the Saturdays of the data set.
+Clusters 2 and 3 make up most of the weekdays of the data set with Cluster 3 being more common in 
+non-summer months. These profiles are used to set the availability schedules as inputs into the
 EnergyPlus simulation to emulate the way occupants inhabit the building and
@@
 systems.
-% This approach is compared to the practice of interviews and site
-% visits to determine such input parameters.\noteDT{where??? how??? i don't get
-% it...}
 
@@
 \includegraphics[scale=0.55]{figures/HPI_combinedclusterandcal_5}
-\caption{HPI Electrical Energy Typical Profiles}
+\caption{Typical measured data electricity profiles of (left) average daily electrical consumption for each cluster and (right)
+color-coded calendar of which days fall within each cluster. The diagram on the right is each month of the year with each row corresponding with
+a day of the week (starting with Monday) and each column corresponding to a week of the month.}
 \label{fig:hpi_elec_profiles}
@@
 The measured and simulated data from both the co-simulation and EnergyPlus
-solo simulation was compared in order to create a realistic scenario for
-comparison. The calibration process was undertaken through a series of steps
+solo simulation were analyzed in order to understand how both the solo and co-simulations 
+compare to real, measured data. The calibration process was undertaken through a series of steps
 such as including local weather conditions for the simulation period and
@@
 for cooling and the winter season (Jan-April and October to December) for
-heating. This approach was taken as the data quality for the measurements were
-deemed most accurate during the appropriate seasons. Figure
-\ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the
+heating. Figure \ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the
 simulations after the tuning process. The final calibrated EnergyPlus solo
@@
 scenarios.
-%\noteDT{Clayton, can you introduce a consistency in the symbols for
-% the figures? say, squares for co-simulation, circles for e+, triangles for
-% measured? and do this across all the figures? small detail, but i think shows
-% quality and a certain, how shall i call it? swissness? a qualité suisse?}
-%Daily data was used to calculated goodness of fit to determine calibration success. 
-%The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating.
 
@@
 
-% \noteDT{with respect to what???}
-% \noteDT{greater than what??}
-
 \begin{figure}[H]
@@
 \end{figure}
-
-% \ref{fig:hpz_profiles}-\ref{fig:hit_profiles}
-
-% \begin{figure}
-% \centering
-% \includegraphics[scale=0.45]{figures/HPZ_combinedclusterandcal_4}
-% \caption{HPZ Heating Energy Typical Profiles}
-% \label{fig:hpz_profiles}
-% \end{figure}
-
-% \begin{figure}
-% \centering
-% \includegraphics[scale=0.45]{figures/HPK_combinedclusterandcal_4}
-% \caption{HPK Electrical Energy Typical Profiles}
-% \label{fig:hpk_profiles}
-% \end{figure}
-
-% \begin{figure}
-% \centering
-% \includegraphics[scale=0.45]{figures/HIT_combinedclusterandcal_4}
-% \caption{HIT Electrical Energy Typical Profiles}
-% \label{fig:hit_profiles}
-% \end{figure}
 
@@
 
-% Applied with essential functions for the
-% region, the building has definitely become the new landmark.
-
-% \noteDT{move main
-% sentence to start of paragraph}
-
 \subsection{Model development}
@@
 calibration step of the model was not undertaken.\\
-% \noteDT{delete:
-% "unfortunately". we are cold hard scientists battling the evil nemesis that is
-% entropy and his plan to suffocate everyone with the inevitable heat death of
-% the universe. we have no time for lame excuses. we just abandon. no regrets.
-% thug life!}
 
@@
 
-% As a summary, three models are compared: a detailed EnergyPlus model, a simplified CitySim model and a simplified EnergyPlus model.
-In addition to what a coupled simplified CitySim and EnergyPlus model is realized and its results analyzed with respect to the other three models.
-
-% \section{Results}
-% {\color{red}Here we show all of the data of the comparison between the simulation outputs and the measured data from the campus}
-
-% \section{Results}
 \subsection{Comparison of EnergyPlus and CitySim}
@@
 heating.
-% \noteDT{in
-% the figures that follow, Cosim and CoSim are both used. decide. then stick to
-% one spelling. everywhere. notice how i need a break? tgif!}
-
-% as closely as possible\noteDT{??! aligned as closely as
-% possible? this is not how we overcome the dark lord. can we quantify this?}
-
-% ,\noteDT % {comma-comma-comma, or not}
 
@@
 doesn't have as large of an impact on the heating and cooling calculations.
-% \noteCM{I'm planning to elaborate on
-% these sections
-% but am struggling to interpret the results other than just "co-sim and solo
-% are different" -- what do you guys think?}\noteDT{well, for a start, the two
-% case studies differ in the amount of LWR radiation. we could quantify that?
-% also, the number of surfaces of the e+ model with viewfactor to surrounding
-% buildings?}
 
@@
 
+\section{Discussion}
+Two campus case studies were presented in this paper to showcase a novel process of extracting 
+model meta-data, conversion of those data into models for two separate simulation engines, and the solo
+and co-simulation process of those engines on two real-world case studies. This section will outline 
+the advantages and disadvantages of undertaking this process with respect to factors such as 
+usability for various applications, simulation speed and resources, and an overview of the tools 
+involved in the process.
+
+Advantages of a co-simulation process between EnergyPlus and CitySim were uncovered through
+this study. The key advantage is that each of the engines is enabled to account for various 
+physical phenomenon in their simulation process that were previously impossible. For example, 
+through co-simulation, EnergyPlus was able to utilize the long wave radiation exchange capabilities 
+of CitySim. \noteCM{Here we continue the discussion of advantages}
+
+Disadvantages of the co-simulation process are mainly centered upon the increase
+in computing time and power needed for the FMI to coordinate data exchange between 
+the two simulation engines. \noteCM{Here we continue the discussion of disadvantages}
+
 \section{Conclusion}
@@
 
-\subsection{Acknowledgements}
+\subsection{Acknowledgments}
 The authors would like to acknowledge the ETH Z\"urich Campus Facilities

### 2017-05-19 latex_corrected/UMEM_CoSim.tex
updated figure 3 (removed dotted lines - they really don't make much sense)
corrected item d

@@
 \usepackage{lineno}
+\usepackage{tikz}
 \RequirePackage{fix-cm}
@@
 modeled using a simplified occupancy-based approximation. The heating,
-ventilation, and air-conditioning (HVAC) systems are modeled using a single
-equation that approximates the total mass flow rate required to meet the
+ventilation, and air-conditioning (HVAC) systems are modeled using a
+set of equations that approximates the total mass flow rate required to meet the
 sensible and latent loads of each building as a whole. Each of these

### 2017-05-19 latex_corrected/UMEM_CoSim.tex
addressed a few comments

@@
 urban environments that are often neglected in building-scale simulation
-environments \citep{Robinson:2004cr,Robinson:2009tm}. Long wave radiation
+environments \citep{Robinson:2004cr,Robinson:2009tm}. CitySim can be connected to a simplified micro-climate airflow model that can 
+predict local climatic conditions around each building INSERT REFERENCES FROM JEROME - IBPSA CISBAT. Long wave radiation
 exchange between the simulated building and its surroundings is sent to
 EnergyPlus; this process is described in detail in Section \ref{lwradiation}.
-Finally, CitySim shares its calculated occupancy schedules as it uses a more
-robust model of occupants behavior
-\citep{Haldi:2011dr}.
+Finally, CitySim shares its calculated occupancy schedules as it can use a deterministic 
+or stochastic occupant behavior model, whereas EnergyPlus models are solely a deterministic models \citep{Haldi:2011dr}.
 
@@
 variables is calculated according to Equation \ref{EPlus_h} with $\sigma$ as
-the Stefan-Boltzmann constant and $\epsilon$ as the emissivity. A major
+the Stefan-Boltzmann constant, $\epsilon$ as the emissivity and $F_{variable}$ being the
+view factor to the variable that can be sky, grd (ground) or air. A major
 assumption of this approach is that the modeled building's surfaces and those
@@
 \begin{equation} \label{EPlus_h} 
-h_{r,variable} = \frac{\epsilon\sigma(T^{4}_{surf}-T^{4}_{variable})}{T_{surf}-T_{variable}}
+h_{r,variable} = \frac{\epsilon\sigma F_{variable}(T^{4}_{surf}-T^{4}_{variable})}{T_{surf}-T_{variable}}
 \end{equation}

### 2017-05-19 latex_reviewcomments/ReviewCommentsResponse.tex
addressed a few comments
addressed review item

@@
 \begin{solution}
-\textcolor{red}{Jerome and Daren - can you confirm the accuracy of the equations?}
+% \textcolor{red}{Jerome and Daren - can you confirm the accuracy of the equations?}
+That is correct -- a view factor has been added to Equation 2. 
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Jerome -- any feedback on this?}
+No, the export from EnergyPlus included both buildings -- this fact has been clarified in the text.
+
+% \textcolor{red}{Jerome -- any feedback on this?}
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Jerome -- can you clarify this?}
+% \textcolor{red}{Jerome -- can you clarify this?}
+It is not the 'Quartier Nord Building' that is being simulated -- it is the STCC. The text has been fixed to clarify this confusion.
 \end{solution}

### 2017-05-19 latex_corrected/UMEM_CoSim.tex
addressed review item

@@
 The corresponding CitySim model was created by exporting a DXF file from
-EnergyPlus, and importing it into the Graphical User Interface of CitySim.
+EnergyPlus for the whole of Quartier Nord, and importing it into the Graphical User Interface of CitySim.
 Physical characteristics of the building were added to complete the CitySim
@@
 first comparison to observe is the differences between the two engines when
-focused on the Quartier Nord building. When simulated in isolation, the
+focused on the STCC building. When simulated in isolation, the
 CitySim engine predicts a 28.6\% increase in heating load and a 44.4\%
@@
 \includegraphics[scale=0.55]{figures/QN_Cooling}
-\caption{Quartier Nord CitySim vs. EnergyPlus Solo for Cooling}
+\caption{STCC CitySim vs. EnergyPlus Solo for Cooling}
 \label{fig:qn_eplusvscitysim_cooling}
@@
 \includegraphics[scale=0.55]{figures/QN_Heating.pdf}
-\caption{Quartier Nord CitySim vs. EnergyPlus Solo for Heating}
+\caption{STCC CitySim vs. EnergyPlus Solo for Heating}
 \label{fig:qn_eplusvscitysim_heating}
@@
 \subsection{EnergyPlus co-simulation results}
-The Quartier Nord building is also simulated within the solo and
+The STCC building is also simulated within the solo and
 cosimulation environments. When

### 2017-05-24 latex_corrected/UMEM_CoSim.tex
changes addressing Review 2, question (2) a) through g) (g was omitted)

@@
 \usepackage{lineno}
-\usepackage{tikz}
 \RequirePackage{fix-cm}
@@
 
+The number of timesteps per hour for both CitySim and EnergyPlus is set to one per hour. 
+The frequency of data exchanges is set to once per timestep. No data averaging over time 
+is performed. Data exported from one simulation engine overwrites the corresponding data
+in the other simulation engine at each timestep. Each simulation is performed for a whole 
+year.
+
 \begin{figure}[H]
@@
 After calibration, a comparison of co-simulation and solo EnergyPlus
-simulations is made. For cooling, a discrepancy can be seen between co-
+simulations is made. Simulation time for the solo EnergyPlus simulation was 1 minute and 49 seconds 
+compared to 28 minutes and 10 seconds for the co-simulation.
+
+For cooling, a discrepancy can be seen between co-
 simulation and solo EnergyPlus. Co-simulation decreases the predicted cooling energy by 15.5\%, as seen in Figure

### 2017-06-13 latex_reviewcomments/ReviewCommentsResponse.tex
finished paper and resubmitted!

@@
 % \email{miller.clayton@arch.ethz.ch}
-\author{Clayton Miller, Daren Thomas, J\'er\^ome K\"ampf, Arno Schlueter}
+% \author{Clayton Miller, Daren Thomas, J\'er\^ome K\"ampf, Arno Schlueter}
 
@@
 \maketitle
-
-% \textcolor{red}{Red text is internal notes of things to be done}
-
-% Black text shaded in blue is the formal responses to the reviewers
 
@@
 \begin{solution}
-\textcolor{red}{Finish discussion section}
-
 The abstract has been updated to reflect that the baseline of these comparison metrics are the EnergyPlus solo simulations of each of the engines.
@@
 engines and disadvantages related to the increase in computing power needed to undertake the process.
-
-% \emph{The majority of these changes can be found in lines X-X.}
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Confirm the following is true:} The United Nations World Urbanization prospectus projected that figure by 2030 -- this fact has been updated in the introduction
+The United Nations World Urbanization prospectus projected that figure by 2050 -- this fact has been updated in the introduction
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Jerome -- is this statement regarding CitySim correct? If so, how can we justify it with respect to this comment?} 
+This observation is correct -- "The heating, ventilation, and air-conditioning (HVAC) systems are modeled using a single equation set of equations that approximates the total mass flow rate required to meet the sensible and latent loads of each building as a whole.'' is a mis-statement.
+This sentence has been changed to a ''set of equations''
 \end{solution}
@@
 \begin{solution}
-{red}{Does anyone know what COSMO-CMM, UMC Model, and BIS stand for?} 
 Explanation of the acronyms is now included in the text.
@@
 \begin{solution}
-\textcolor{red}{Daren -- what was our logic behind the dotted lines?}
+It is correct that the dotted line is meant to show the co-simulation path in Figure 2.
+Therefore the dotted lines have been removed from Figure 3 for consistency sake and the text has been modified to be more readable.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Jerome -- can you explain quickly in the text how CitySim calculated these variables and why its better than using EnergyPlus's weather file inputs?}
+The next now explains how CitySim has simplified micro-climate airflow model that can predict local climatic conditions around each building.
+It also further describes how CitySim shares its calculated occupancy schedules as it can use a deterministic or stochastic occupant behavior model, whereas EnergyPlus models are solely a deterministic models.
+Grammar changes have been noted.
 \end{solution}
@@
 \begin{solution}
-References for Table 1 and 2 are no included in the text pertaining to those variables.
+References for Table 1 and 2 are now included in the text pertaining to those variables.
 \end{solution}
@@
 \begin{solution}
-% \textcolor{red}{Jerome and Daren - can you confirm the accuracy of the equations?}
 That is correct -- a view factor has been added to Equation 2. 
@@
 \begin{solution}
+The NMBE for heating is actually 5.02, thus the repetition of the -9.36 value is a type. This has been corrected in the text.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Confirm in the Juypter notebook}
+The Miller study does compare solo and co-simulation results, but in an entirely different context.
+It is difficult to compare the difference between the two sets of simulations as the buildings tested are different, thus, the discrepancies between co-simulation and solo could be wildly different or very similar either one.
+Due to this, reference to this study and its comparison to the results of the campus co-simulation have been removed.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Update graphics}
+For Figure 11, we believe the variations are important to show at the daily, monthly and annual levels because even if they have small offsets and little variation at those scales, that information itself is insightful.
+For example in the monthly chart, March and April have a larger offset than Jan and Feb for heating.
+The order of the bars in all of the charts has been made consistent.
+The measured data has been made the baseline for the percentages, thus making it more clear how the solo and co-simulation perform as compared to the measured data.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Add Minergie as a reference}
+Minergie Standard added.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Add SIA and explain}
+The term SIA was replaced with local energy code standard.
 \end{solution}
@@
 No, the export from EnergyPlus included both buildings -- this fact has been clarified in the text.
-
-% \textcolor{red}{Jerome -- any feedback on this?}
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Confirm numbers in graphics}
+An explation of how the different engines calculate heating and cooling loads was added.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Update with strengths and weaknesses in the discussion}
+A discussion section was added with advantages and disadvantages as well as future research directions.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Update references}
+References are updated based on the feedback.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Update references}
-
+It wasn't necessarily the technical aspects of EnergyPlus that were the basis for choosing it in this study.
+The more relevant factor for us was familiarity and knowledge of using the engine and its ability to use FMI to interface with another program.
+Content has been added to emphasize these points.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Daren -- can you take a stab at these?}
-a) \\
-b) \\
-c) \\
-d) \\
-e) \\
-f) \\
-g) \\
+Content was added in this section which touches upon each of these points.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Explain the calibration process in much more detail}
+A total of 37 calibration steps were undertaken to tune the model -- it would be extremely tedious and lengthy to specify each of these steps and their modivations in the calibration process, especially since the goal is simplified calibration.
+Content has been added about the number of iteration steps and their impact on the calibration process.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Why are there differences?}
-
+Figure 10-17 have content added to help further explain discrepancies and significant content has been added in the new Discussion section into why these discrepancies are relevant.
 \end{solution}
@@
 \begin{solution}
-\textcolor{red}{Strenghts and weaknesses and advantages/disadvantages in the}
-
+The new Discussion section now also details the challenges, advantages and disadvantages of the study.
 \end{solution}

### 2017-06-13 latex_compared/UMEM_CoSim_original.tex
finished paper and resubmitted!

--- 2016-12-20 initialsubmission/UMEM_CoSim_Anonymous.tex
@@
 
-% \subsection{Acknowledgements}
-% The authors would like to acknowledge the ETH Z\"urich Campus Facilities
-% Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
-% Thoma for their assistance in this project. This research was funded by the
-% Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
-% Energy Modeling (UMEM) project. 
+\subsection{Acknowledgements}
+The authors would like to acknowledge the ETH Z\"urich Campus Facilities
+Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
+Thoma for their assistance in this project. This research was funded by the
+Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
+Energy Modeling (UMEM) project. 
 % The authors would also like to acknowledge

### 2017-06-13 latex_corrected/UMEM_CoSim.tex
finished paper and resubmitted!

@@
 
-\author{Clayton Miller\textsuperscript{a}%
-$^{\ast}$\thanks{$^\ast$Corresponding author. Email: miller.clayton@arch.ethz.ch}, 
-Daren Thomas\textsuperscript{a},
-J\'er\^ome K\"ampf\textsuperscript{b},
-and Arno Schlueter\textsuperscript{a}\\
+\author{Clayton Miller\textsuperscript{a,b}%
+$^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
+Daren Thomas\textsuperscript{b},
+J\'er\^ome K\"ampf\textsuperscript{c},
+and Arno Schlueter\textsuperscript{b}\\
 \vspace{6pt}
-\textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
-\textsuperscript{b}{\em Solar Energy and Building Physics Laboratory (LESO-PB), Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland}
-\received{Submission for review on April 30, 2016} %TARGETED!
+\textsuperscript{a}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
+\textsuperscript{b}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
+\textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
 }
@@
 \begin{abstract}
-    This paper describes the co-simulation process of the building and urban
-    scale models of two campuses of higher education buildings in Switzerland.
-    The campuses are modeled at both the building level, using the EnergyPlus
-    simulation engine, and at the urban scale using the CitySim engine. A co-
-    simulation framework is used to execute simulations from both engines
-    concurrently with an exchange of information to leverage the various
-    strengths of each. In the first case study, on-site weather and measured
-    performance data are then compared to the output from two modeling
-    scenarios: building-scale simulation using EnergyPlus and co-simulation of
-    the engines. A partial calibration process is implemented to reconcile the
-    simulations with the measured data of a targeted office building on
-    campus. In the second case study, the co-simulation results are compared
-    to the both the CitySim simulation engine. The results
-    show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and
-    -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on
-    heating consumption as compared to solo simulations of each of the engines. Challenges encountered with the urban scale
-    calibration and the strengths and weaknesses of the developed process are
-    discussed.
+The co-simulation of both urban and building-level models leverages the advantages of both platforms.
+It better accounts for the localized effects of surrounding buildings, geography and climate conditions while maintaining high-fidelity building systems representation.
+This paper describes the co-simulation process of the building and urban scale models of two university campuses in Switzerland using EnergyPlus and CitySim.
+In the first case study, on-site measured performance data is compared to the co-simulation results.
+The second case study examines the results of the two engines.
+The results show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on heating use as compared to solo simulations.The co-simulation process was able to better model realistic conditions for heating, but not cooling in one case study.
+It was able to substantially reduce the discrepancies in prediction between the engines in the other study.
+
+    % The co-simulation of both urban and building-level models provides the means to model 
+    % collections of buildings in ways that leverage the advantages of both platforms. It accounts better 
+    % for the localized effects of surrounding buildings, geography and climate conditions 
+    % while maintaining a high-fidelity building systems representation.
+    % This paper describes the co-simulation process of the building and urban
+    % scale models of two campuses of higher education buildings in Switzerland.
+    % The campuses are modeled at both the building level, using the EnergyPlus
+    % simulation engine, and at the urban scale using the CitySim engine. A co-
+    % simulation framework is used to execute simulations from both engines
+    % concurrently with an exchange of information to leverage the various
+    % strengths of each. In the first case study, on-site weather and measured
+    % performance data are then compared to the output from two modeling
+    % scenarios: building-scale simulation using EnergyPlus and co-simulation of
+    % the engines.  The co-simulation process was able to better model realistic conditions for heating, but not cooling in one case study and was able to 
+    % highly reduce the discrepancies in prediction between the engines in the other study.
+     % Challenges encountered with the urban scale
+    % calibration and the strengths and weaknesses of the developed process are
+    % discussed.
+    % A partial calibration process is implemented to reconcile the
+    % simulations with the measured data of a targeted office building on
+    % campus. In the second case study, the co-simulation results are compared
+    % to the CitySim simulation engine.
+
+    % A co-simulation framework is used to execute simulations from both engines concurrently with an exchange of information to leverage the various strengths of each.
+
+    % The results show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and
+    % -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on
+    % heating consumption as compared to solo simulations of each of the engines.
 \end{abstract}
@@
 
-% {\abstractfont\centerline{\bfseries Index to information contained in this guide}\vspace{12pt}
-% \hbox to \textwidth{\hsize\textwidth\vbox{\hsize19pc
-% \hspace*{-12pt} {1.}    Introduction\\
-% \hspace*{7pt} {1.1.}  The \textit{tBPS} document class\\
-% \hspace*{7pt} {1.2.}  Submission of \LaTeX\ articles\\
-% \hspace*{24pt}        to the journal\\
-% {2.}    Using the \textit{tBPS} class file\\
-% {3.}    Additional features\\
-% \hspace*{10pt}{3.1.}  Title, authors' names, abstract \\
-% \hspace*{24pt}        and keywords\\
-% \hspace*{10pt}{3.2.}  Additional footnotes to the title \\
-% \hspace*{24pt}        or authors' names\\
-% \hspace*{10pt}{3.3.}  Lists\\
-% {4.}    Some guidelines for using standard\\
-% \hspace*{6pt}         features\\
-% \hspace*{10pt}{4.1.}   Sections\\
-% \hspace*{10pt}{4.2.}   Illustrations (figures)\\
-% \hspace*{10pt}{4.3.}   Tables\\
-% \hspace*{10pt}{4.4.}   Landscape pages\\
-% \hspace*{10pt}{4.5.}   Theorem-like environments\\
-% \noindent \hspace*{7pt} {4.6.}   Typesetting mathematics\\
-% \hspace*{24pt} {4.6.1.}   Displayed mathematics\\
-% \hspace*{24pt} {4.6.2.}   Bold math italic symbols\\
-% \hspace*{24pt} {4.6.3.}   Bold Greek\\
-% \hspace*{24pt} {4.6.4.}   Upright Greek characters  \\
-% \hspace*{50pt}            and the upright partial \\
-% \hspace*{50pt}            derivative sign  \\}
-% \hspace{-24pt}\vbox{\noindent\hsize19pc
-% \hspace*{7pt} {4.7.}   Acknowledgements \\
-% \hspace*{7pt} {4.8.}   Funding \\
-% \hspace*{7pt} {4.9.}   Notes \\
-% \hspace*{7pt} {4.10.}   Supplemental material \\
-% \hspace*{7pt} {4.11.}   References \\
-% \hspace*{24pt} {4.11.1.}  References cited in the \\
-% \hspace*{54pt}            text \\
-% \hspace*{24pt} {4.11.2.}   The list of references\\
-% \hspace*{7pt} {4.12.}   Appendices \\
-% {5.}    Example of a section heading \\*
-% \hspace*{7pt}   including \textsc{small caps}, \textit{italic}, \\*
-% \hspace*{7pt}   and bold Greek such as ${\bm\kappa}$ \\
-% {6.}   {\em tBPS} journal style \\
-% \hspace*{10pt}{6.1.}   Hyphens, en rules, em rules \\ \hspace*{27pt}and minus signs\\
-% \hspace*{10pt}{6.2.}   References \\
-% \hspace*{10pt}{6.3.}   Maths fonts\\
-% \noindent   {7.}   Troubleshooting\\
-% {8.}   Fixes for coding problems\\
-% {9.}   Obtaining the tBPS2e class file\\
-% \hspace*{10pt}{9.1}  Via the Taylor \& Francis \\
-% \hspace*{24pt}       website \\
-% \hspace*{10pt}{9.2}  Via e-mail\\ }}}
-
 \linenumbers
@@
 \section{Introduction}
-\noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}
 
@@
 world at an unprecedented rate. A transition from urban to rural is underway and
-2.5 billion people are expected to join cities throughout the world by the year 2030
-\citep{UnitedNations:2014vn}. Expansions of entire districts and even cities
+2.5 billion people are expected to join cities throughout the world by the year 2050
+\citep{united_nations_world_2014}. Expansions of entire districts and even cities
 is not an uncommon phenomenon, especially in East Asia and Africa. Urban scale
@@
 systems design, policy assessment, and land use and transportation
-\citep{Keirstead:2012ct}. The ability to simulate the interaction between
+\citep{keirstead_review_2012}. The ability to simulate the interaction between
 large collections of buildings enables the development and testing of
 optimization and planning scenarios for this new development
-\citep{Dorer:2013vt}.
+\citep{dorer_modelling_2013}.
 
@@
 models and their interdependent relationship with their urban climate
-\citep{Robinson:2009tm}. CitySim includes building thermal, urban radiation,
+\citep{robinson_citysim:_2009}. CitySim includes building thermal, urban radiation,
 occupant behavior, and plant/equipment models integrated as a single
@@
 urban scale efforts. The use of whole building simulation engines originated
-in the 1960s with the US government's development of the BLAST and DOE-2
-hourly energy simulation programs \citep{Lawrie:2001vf}. In 1996, development
+in the 1960's with the US government's development of the BLAST and DOE-2
+hourly energy simulation programs \citep{lawrie_energyplus:_2001}. In 1996, development
 on a new simulation engine, EnergyPlus, began in order to combine the
@@
 unique mechanical system types such as decoupled centralized cooling
-\citep{Miller:2010wa} and low exergy heating and cooling systems
-\citep{barbara:2015tz}. Additionally, EnergyPlus is designed to provide a high
+\citep{miller_modeling_2010}. Additionally, EnergyPlus is designed to provide a high
 resolution in which internal loads and natural ventilation technologies can be
-modeled in detail at the building level.
+modeled in detail at the building level. EnergyPlus is also extensively used within the
+research community and has new features that enable it to couple with other simulation programs.
 
@@
 difficult. And whole building simulation in EnergyPlus neglects many of the
-various contextual consideration of the urban environment such as long wave
+various contextual consideration of the urban environment such as long-wave
 radiation exchange with adjacent surfaces and localized urban weather effects
-\citep{Lawrie:2001vf}.%\noteDT{ref?}
+\citep{lawrie_energyplus:_2001}.
 
-To address the deficiencies of the individual engines, the current
-effort seeks to couple building and urban scale simulation. The research in
+The current
+effort seeks to couple building and urban scale simulation to address the deficiencies of the individual engines. The research in
 this paper is part of a larger coupling effort in which various engines are
 connected and co-simulated to create a more comprehensive analysis of the
-urban scale \citep{Dorer:2013vt,Allegrini:2012kx}. The target is the
+urban scale \citep{dorer_modelling_2013,allegrini_influence_2012}. The target is the
 computational interface between the building energy model, using EnergyPlus,
@@
 Building Energy Simulation (BES) model. The scales and models contained in the 
-urban environment context include the Urban-Scale Model (UC Model), the UMC model using OpenFoam, 
-and the Meteorological Meso-scalce (MM model). On the database side, Revit, global 
-information systems (GIS), and building information systems (BIS) are utilized.
-
-% \noteDT{can we do phrasing? prettyplease?}
+urban environment context include the Urban-Scale Model (UC Model), the Urban 
+Microclimate (UMC) model using OpenFoam, and the Meteorological Meso-scale (MM model) 
+using Climate Limited-Area Modeling (COSMO-CLM). On the database side, Revit, Global 
+Information Systems (GIS), and building information systems (BIS) are utilized.
 
@@
 Switzerland. The first case study is the ETH Z\"urich Hoenggerberg campus in
-Z\"urich, Switzerland. The campus was modeled in the CitySim simulation engine
+Z\"urich, Switzerland. It was modeled in the CitySim simulation engine
 and co-simulated using work-flow automation. The target of this case study is
@@
 
- % with a target on the use of these models for building retrofit analysis.\noteDT{I do not understand the preceding sentence. Neither will the reviewer}
-
 \begin{figure}[H]
@@
 block in the diagram represents an environment, with the tool/engine name in
-italics (\citep{thomas2014multiscale}, adapted from \citep{Dorer:2013vt})}
+italics (\citep{thomas_multiscale_2014}, adapted from \citep{dorer_modelling_2013})}
 \label{fig:UMEM}
@@
 
-This paper describes the achievement of several objectives:
-\begin{enumerate}
-  \item Automate of the process of simultaneous meta-data extraction from a
-  building information model (BIM) for the creation of both building and
-  urban-scale performance models for a real-world campus of buildings
-  \item Co-simulate the urban and building scale models through concurrent information exchange
-  \item Implement a simplified calibration procedure for the first scenario by 
+This paper describes the achievement of several objectives. The first is to
+automate the process of simultaneous meta-data extraction from a
+Building Information Model (BIM) for the creation of both building and
+urban-scale performance models for a real-world campus of buildings. Next, we week to 
+co-simulate the urban and building scale models through concurrent information exchange.
+Finally, we implement a simplified calibration procedure for the first scenario by 
 reconciling the co-simulation output results for a target building using measured energy 
 performance data from the campus energy information system (EIS)
-\end{enumerate}
-
-% \noteDT{s/have/has/}
 
 The first two objectives have been demonstrated in a simplified context in
-previous literature \citep{thomas2014multiscale,Miller:2015vk}. The innovation
+previous literature \citep{thomas_customizable_2012,miller_long_2015}. The innovation
 in the current publication is an extension of this research through the
@@
 have analyzed strong and loose coupling of engines at this scale
-\citep{Trcka:2010cr,Wetter:2011kh}. Coupling of building-scale simulation with
+\citep{wetter_co-simulation_2011,trcka_co-simulation_2010}. Coupling of building-scale simulation with
 urban-scale computational fluid dynamics (CFD) is attempted for modeling
-natural ventilation \citep{Zhang:2013vx} and to improve energy prediction
-\citep{Bouyer:2011eha}. A comprehensive review of energy and airflow modeling
+natural ventilation \citep{zhang_coupled_2013} and to improve energy prediction
+\citep{bouyer_microclimatic_2011}. A comprehensive review of energy and airflow modeling
 of neighborhoods and university campuses was published that includes
 strategic aspects of coupling different %\noteDT{did you mean: "strategic"?}b
-types of models \citep{Srebric:2015gq}. EnergyPlus has been coupled with ENVI-
+types of models \citep{srebric_building_2015}. EnergyPlus has been coupled with ENVI-
 met, a micro-climate computational fluid dynamics (CFD) program
-\citep{Yang:2012cr}. It was also coupled with simplified lumped parameter
+\citep{yang_integrated_2012}. It was also coupled with simplified lumped parameter
 models to facilitate comparison with measured sensor data
-\citep{Martin:2015fj}. While not directly coupled, EnergyPlus and the TEP Urban Canopy Model program were connected
+\citep{martin_estimation_2015}. While not directly coupled, EnergyPlus and the TEP Urban Canopy Model program were connected
 through a modified weather file to quantify the influences of urban localized weather effects
-on whole building simulation \citep{Bueno:2011hi} and urban weather generation
-\citep{Bueno:2013hh}.
-% Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}\noteDT{this is not technically a simulation coupling}.
-% \subsection{Urban scale performance simulation}
+on whole building simulation \citep{bueno_combining_2011} and urban weather generation
+\citep{bueno_urban_2013}.
 
-\section{Methodology}\label{Methodology}
-% Portions of the following methodology is developed in previous literature and is reiterated to set the context for Section \ref{Implementation}.
-The previously published research is clearly outlined at the beginning of each subsection.
+\section{Methodology}
+\label{Methodology}
 
@@
 model and contextual surrounding buildings is described in previous studies
-\citep{thomas2014multiscale}, which forms the basis for the methodology
+\citep{thomas_multiscale_2014}, which forms the basis for the methodology
 in the current effort. This process utilizes the Design Performance Viewer
@@
 Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM
-\citep{Schlueter2009}. The central philosophy behind the tool is a rapid simulation
+\citep{schlueter_building_2009}. The central philosophy behind the tool is the rapid simulation
 of the building information model from the earliest design possible that can be
 used throughout the life-cycle of the building including retrofit analysis
-\citep{Miller:2014tu}. This process is achieved by augmenting the information
+\citep{miller_bim-extracted_2014}. This process is achieved by augmenting the information
 in the BIM with default values and abstracting information not relevant for
@@
 the designer due to automatic creation of input files, execution, and analysis
-of the results.% \noteDT{not sure the second reference includes coupling...}
+of the results.
 
@@
 \ref{fig:OverallWorkflowProcess}. The solid lines depict the co-simulation of EnergyPlus
-and CitySim and the dotted lines depict solo simulations of either EnergyPlus or CitySim. 
+and CitySim, and the dotted lines illustrate solo simulations of either EnergyPlus or CitySim. 
 First, the DPV is used to extract an
@@
 \includegraphics[scale=0.7]{figures/UMEM_Workflow}
-\caption{Overview diagram of the coupling process including tools and outputs \citep{thomas2014multiscale}}
+\caption{Overview diagram of the coupling process including tools and outputs \citep{thomas_multiscale_2014}}
 \label{fig:OverallWorkflowProcess}
@@
 surfaces are grouped into buildings based on the mass object from which they were extracted. 
-These neighboring buildings use default construction properties for walls and roofs, and we assign them a default glazing ratio.
-These defaults can be overridden by custom properties applied to the mass
-objects in the BIM much in the same way as the model elements of the main
+These adjacent buildings use default construction properties for walls and roofs, 
+and we assign them a default glazing ratio. These defaults can be overridden by custom 
+properties applied to the mass objects in the BIM much in the same way as the model elements of the main
 building are enriched with DPV information.
@@
 As of version 8.1.0, EnergyPlus supports exporting a simulation model as a
-Functional Mock-up Unit (FMU) \citep{Nouidui:2014hq,Anonymous:ZZTfF80-}. This
+Functional Mock-up Unit (FMU) \citep{nouidui_functional_2014}. This
 feature introduces new IDF objects to specify the interface such an FMU
@@
 EMS subroutines.
-% \noteDT{@JK: is this last statement correct?}
-
-% It was determined that to export an output variable using the FMU export functionality, the variable itself must also be output with an IDF object of type \emph{Output:Variable} or \emph{EnergyManagementSystem:OutputVariable} in the IDF file as well.
-
-% The process of augmenting the IDF file is automated with the EMS subroutines and FMU export objects.
-The script \emph{addfmutoidf.py}, written in the Python programming language, uses the \emph{parseidf} module to read in the IDF file and add the new IDF objects based on those found in the model.
-This script reads in the list of surfaces defined in the IDF file and produces EMS scripts to aggregate and output the surface temperatures of the wall and the windows as well as any other output objects necessary.
 
@@
 process from both the EnergyPlus and CitySim perspective. The augmented IDF
-file is fed to the \emph{EnergyPlusToFMI} script \citep{Nouidui:2014bo}. Once
+file is fed to the \emph{EnergyPlusToFMI} script \citep{nouidui_tool_2014}. Once
 configured, this script produces an FMU file based on the augmented IDF file
@@
 \includegraphics[scale=0.7]{figures/UMEM_FMU_Overview}
-\caption{Simulation information exchange between CitySim and EnergyPlus using FMI \citep{thomas2014multiscale}}
+\caption{Simulation information exchange between CitySim and EnergyPlus using FMI \citep{thomas_multiscale_2014}}
 \label{fig:FMUOverview}
@@
 
-% Table \ref{FMUimports} and \ref{FMUexports} outline the variables exchanged between EnergyPlus and CitySim through the FMI.
-
-% We used the \emph{fmilib} library from the JModelica project to test the FMU produced \citep{Anonymous:ZZTfF80-}.
-We altered one of the sample programs (\emph{fmi\_import\_cs\_test.c}) to load the FMU, run it and print out the values exported from EnergyPlus.
-This code was then used as a guide to extending the CitySim solver to load FMUs for co-simulation.
-
 \subsection{Coupled variables}
-
-% On an hourly basis, CitySim performs a heating and cooling needs prediction step.
-The temperature determination step for the main building is replaced with the results of the EnergyPlus timestep as obtained through FMI library.
-The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus, and to receive data from EnergyPlus that are further used within CitySim for the next time steps.
 Several key urban-scale weather variables are sent to EnergyPlus from CitySim
@@
 file input. CitySim is designed to account for physical phenomenon inherent to
-urban environments that are often neglected in building-scale simulation
-environments \citep{Robinson:2004cr,Robinson:2009tm}. CitySim can be connected to a simplified micro-climate airflow model that can 
-predict local climatic conditions around each building INSERT REFERENCES FROM JEROME - IBPSA CISBAT. Long wave radiation
-exchange between the simulated building and its surroundings is sent to
+urban environments, which are often neglected in building-scale simulation
+environments \citep{robinson_solar_2004,robinson_citysim:_2009}. CitySim can be connected 
+to a simplified micro-climate airflow model that can predict local climatic conditions 
+around each building. Long-wave radiation exchange between the simulated building and its surroundings is sent to
 EnergyPlus; this process is described in detail in Section \ref{lwradiation}.
 Finally, CitySim shares its calculated occupancy schedules as it can use a deterministic 
-or stochastic occupant behavior model, whereas EnergyPlus models are solely a deterministic models \citep{Haldi:2011dr}.
-
-% \noteDT{s/climactic/climatic/}
-% \noteDT{this sentence, man. i can't even}
+or stochastic occupant behavior model, whereas EnergyPlus models are solely a deterministic models \citep{haldi_impact_2011}.
 
@@
  \hline
- Long Wave Radiation & Environmental Radiant Temp. & Calculated $T_{env}$ from the sky,\\&& ground, and surrounding surfaces \\
+ Long-Wave Radiation & Environmental Radiant Temp. & Calculated $T_{env}$ from the sky,\\&& ground, and surrounding surfaces \\
  & Environmental Radiant Heat  & Calculated $h_{env}$ from the sky,\\
@@
 to model a detailed radiant heating and cooling system that would be
-impossible in CiytSim \citep{barbara:2015tz}. EnergyPlus is an engine
+impossible in CiytSim. EnergyPlus is an engine
 optimized to accurately model building-scale systems. Thus, CitySim can take 
@@
 
-%\noteDT{I'm not sure this is proper English. Or American for that
-%matter...}
-
-%\noteDT{in table 2: "Values SENT to CitySim..."}
 \begin{table}[H]
@@
 
-\subsection{Long wave radiation exchange}
+\subsection{long-wave radiation exchange}
 \label{lwradiation}
-Long wave radiation exchange in the urban scale environment is coupled in the
+long-wave radiation exchange in the urban scale environment is coupled in the
 co-simulation process. It requires the development of a set of
@@
 and to account for differences in the methods by which each engine calculates
-this value. A detailed description of Long Wave Radiation (LWR) variable
+this value. A detailed description of long-wave Radiation (LWR) variable
 exchange and approximation is found in a previously published study
-\citep{Miller:2015vk} on a simplified theoretical case.
+\citep{miller_long_2015} on a simplified theoretical case.
 
@@
 of radiation gain from the ground, sky, and air as seen in Equation
-\ref{EPlus_LWR_Ext} and Figure \ref{combinedLWR}a \citep{doe2010energyplus}.
+\ref{EPlus_LWR_Ext} and Figure \ref{combinedLWR}a \citep{united_states_department_of_energy_doe_energyplus_2015}.
 The radiant heat transfer coefficient for each of these environmental
@@
 exchange is negligible; a situation that is an oversimplification in an urban
-scale domain \citep{Evins:2014cf}.
+scale domain \citep{evins_simulating_2014}.
 \begin{equation} \label{EPlus_LWR_Ext} 
@@
 $h_{r,env}$, from surrounding urban surfaces in addition to ground, sky, and
-air \citep{Robinson:2009tm}. The calculation for $T_{env}$ is expressed in
+air \citep{robinson_citysim:_2009}. The calculation for $T_{env}$ is expressed in
 Equation \ref{CitySim_Tenv} with the $F$ values being view factors of the
@@
   \includegraphics[width=1.0\textwidth]{figures/LWRCalc_Combined_V3}
-  \caption{Comparison of the LWR components between a) Solo EnergyPlus and b) Coupled CitySim/EnergyPlus configuration \citep{Miller:2015vk}
+  \caption{Comparison of the LWR components between a) Solo EnergyPlus and b) Coupled CitySim/EnergyPlus configuration \citep{miller_long_2015}
   \label{combinedLWR}}
@@
 The coupling, simulation and co-simulation process is completely managed
-within a program called VisTrails \citep{Anonymous:Cayf2tu7}. The
-implementation of this type of work flow is outlined in previous work focused
-on automating DPV using the Kepler platform \citep{Thomas:2012wj}. This
+within a program called VisTrails \citep{freire_reproducibility_2014}. The
+implementation of this type of workflow is outlined in previous work focused
+on automating DPV using the Kepler platform \citep{thomas_customizable_2012}. This
 process reduces the effort expended by a designer down to pressing a single
-button. This functionality allows an iterative design style informed by
-readily available simulation results. An automated work flow ties the
-various steps together and maintain the effortless iterative design process.
-VisTrails enables the coupling of various work flow subprocesses script
+button. This functionality allows an iterative design informed by
+readily available simulation results. An automated workflow ties the
+various steps together and maintains the effortless iterative design process.
+VisTrails enables the coupling of various workflow subprocesses script
 initializations, executions of the engines, and the compilation of the
-outputs. This tool empowers the coupling of various executable files and their
-connecting scripts in graphical diagrams that enhances reproducibility and
-process automation \citep{Freire:2014tt}. The VisTrails work flow diagram for
+outputs. This tool empowers the coupling of multiple executable files and their
+connecting scripts in graphical diagrams that enhance reproducibility and
+process automation \citep{freire_reproducibility_2014}. The VisTrails workflow diagram for
 the first case study in this paper is seen in Figure \ref{VizTrails}.
-
-% INSERT VISTRAILS GRAPHIC HERE\noteCM{Daren -- can you give me a good screenshot of the Vistrails for the HPI building? Pretty please.}\noteDT{sure - check out 36-HPI-cosim.pdf in the figures folder}
 
@@
 \subsection{Simplified calibration}
-In the first case study, one aspect of this analysis is the comparison of
-actual measured performance of the target building on campus with the
+In the first case study, one aspect of this analysis is the comparison of the actual measured performance of the target building on campus with the
 simulation results of the co-simulation. A simplified calibration procedure is
@@
 data available on campus with various simulation scenarios
-\citep{Samuelson:2015jg}. This calibration procedure was utilized in the
+\citep{samuelson_analysis_2015}. This calibration procedure was utilized in the
 performance reconciliation of 18 buildings that were built according to the
@@
 protocol is unique in its analysis process to uncover design model
-deficiencies in a step-wise manner, utilizing the most easily accessible
+deficiencies in a step-wise manner, utilizing the most readily available
 knowledge first and working towards equilibrium between measured and
@@
 The second case study is the EPFL campus in Lausanne, Switzerland. The
-targeted building, in this case, was the Quartier Nord complex. The focus of
+targeted building, in this instance, was the Quartier Nord complex. The focus of
 this study was to compare the solo and co-simulation output results of CitySim.
@@
  cafeterias, data centers and other types of similar areas. The campus has a
- centralized energy management system (EMS) that contains 807 energy and water
- measurement points from heating, cooling, electricity, city gas, domestic hot
- water, grey water, and general water consumption. %\noteDT{deleted: "buildings"}
-
-%Figure \ref{fig:pointgraph} illustrates the breakdown of these measurement system data points amongst the campus buildings.
-
-% \begin{figure}
-% \centering
-% \includegraphics[scale=0.7]{figures/pointbreakdown_anon}
-% \caption{Available performance measurement points}
-% \label{fig:pointgraph}
-% \end{figure}
+ centralized energy management system (EMS) that contains 807 energy and water measurement points from heating, cooling, electricity, city gas, domestic hot water, gray water, and general water consumption.
 
@@
 to execute EnergyPlus solo and co-simulation processes for the purpose of
-simplified calibration, and then to understand the magnitude of difference
+simplified calibration, and then to understand the magnitude of the difference
 between these simulation scenarios.
@@
 energy for the HPI building. This profile was created through a filtering and
-clustering process known as \emph{DayFilter} \citep{Miller:2015kr}. Cluster 0 represents
+clustering process known as \emph{DayFilter} \citep{miller_automated_2015}. Cluster 0 represents
 the typical energy profile for Sunday, while Cluster 1 dominates the Saturdays of the data set.
@@
 model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of
-variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\%
+variation of root mean square error (CVRMSE) of 21.7\% for cooling and 5.02\%
 and 29.4\% for heating. These metrics fall within the +/-10\% NMBE and +/-30\%
-CVRSME used in this case study for calibration. The
+CVRSME used in this case study for calibration. A total of 37 calibration iterations were undertaken to modulate the simulation results to within these criteria. The
 goal of calibration, in this case, is to just bring the models to within a
@@
 \subsection{EnergyPlus co-simulation results}
-After calibration, a comparison of co-simulation and solo EnergyPlus
-simulations is made. Simulation time for the solo EnergyPlus simulation was 1 minute and 49 seconds 
-compared to 28 minutes and 10 seconds for the co-simulation.
-
 For cooling, a discrepancy can be seen between co-
@@
 heating months is noticed resulting an overall increase of heating prediction
-of 6.5\% due to co-simulation. The exchange of long wave radiation for this
+of 6.5\% due to co-simulation. The exchange of long-wave radiation for this
 particular site is substantial due to the proximity of surrounding buildings.
-These performance differences due to co-simulation are compared to a
-theoretical single-zone case study in which there was a 15-30\% increase in
-heating energy and a 4-11\% decrease in cooling energy \citep{Miller:2015vk}.
-The results from this case study are less extreme on the heating side and more
-on the cooling side than the theoretical case study.
+
+% These performance differences due to co-simulation are compared to a
+% theoretical single-zone case study in which there was a 15-30\% increase in
+% heating energy and a 4-11\% decrease in cooling energy \citep{Miller:2015vk}.
+% The results from this case study are less extreme on the heating side and more
+% on the cooling side than the theoretical case study.
 
@@
 cooling energy is over-predicted by the solo simulation by 4\%, while co-simulation under-predicted 
-by 11.1\%. For heating energy, co-simulation was able to bring the predicted value to within 2\% of 
-the measured value for the year, an improvement as compared to the solo simulation, which was 8.5\% less than the measured value.
+by 11.1\%. This discrepancy is likely due to a loss in long-wave radiation in the co-simulation to the surrounding buildings, thus reducing the overall 
+cooling load.
+
+For heating energy, co-simulation was able to bring the predicted value to within 2\% of 
+the measured value for the year, an improvement as compared to the solo simulation, which was 8.5\% less than the measured value. This situation is also 
+likely due to the long-wave radiation loss to surrounding buildings, thus increasing the overall heating load.
 
@@
 is realized on the STCC, simulated with the nearby buildings for housing,
-retail and service areas.
+retail and service areas \citep{beyeler_minergie:_2009}.
 
@@
 Lausanne (EPFL), which was responsible for carrying out the project from call
-to tender to construction. However, since the documents provided were full of
-details but also conflicting with what has been installed as compared to the
-documents before construction, the task to realize a precise model of the
+to tender to construction. However, since the documents provided were conflicting 
+with what has been installed, the task to realize a precise model of the
 buildings itself is rather tedious. Besides, it is even more challenging to
@@
 Considering the lack of detailed information about the building, a so-called
-detailed reference case was modeled with EnergyPlus \citep{Mauree:2015to} in
-which regulation standards applied in the design phase from the SIA norms were
+detailed reference case was modeled with EnergyPlus \citep{mauree_evaluation_2015} in
+which regulation standards applied in the design phase from the local building code norms were
 used to complete the missing information. A rendering of this model is seen in
@@
 the differences in the way each of these engines calculates heating and
-cooling loads. Use of the co-simulation process brings the engines to within
+cooling loads. CitySim has a much more simplified model of building occupants,
+lighting, and plug loads. CitySim also includes long-wave radiation exchange calculations
+that can greatly influence the heating and cooling load calculations as well.
+ Use of the co-simulation process brings the engines to within
 5.4\%. Figure \ref{fig:qn_eplusvscitysim_cooling} illustrates these
@@
 The STCC building is also simulated within the solo and
-cosimulation environments. When
+co-simulation environments. When
 focusing on the EnergyPlus results, a 7.5\% decrease in cooling energy is
@@
 than the HPI and theoretical case studies due to the number and proximity of
-surrounding buildings is not as large. Long wave radiation exchange in this situation 
-doesn't have as large of an impact on the heating and cooling calculations.
+surrounding buildings is not as large. long-wave radiation exchange in this situation doesn't have as large of an impact on the heating and cooling calculations.
 
@@
 \section{Discussion}
-Two campus case studies were presented in this paper to showcase a novel process of extracting 
-model meta-data, conversion of those data into models for two separate simulation engines, and the solo
-and co-simulation process of those engines on two real-world case studies. This section will outline 
-the advantages and disadvantages of undertaking this process with respect to factors such as 
-usability for various applications, simulation speed and resources, and an overview of the tools 
-involved in the process.
+Two campus case studies were presented in this paper to showcase a unique process of extracting model meta-data, conversion of those data into input files for two separate simulation engines, and the solo
+and co-simulation process of those engines on two real-world case studies.
+The analysis of the results shows that for the first case study, co-simulation can achieve values closer to measured reality for heating, but not cooling.
+These results are unique to this case study and simply show that the co-simulation process may be helpful for heating only
+in this particular instance. A limitation of this study is that we only analyze a single building against measured data in this
+context. In the second case study, significant discrepancies are found between the CitySim and EnergyPlus engines which were corrected using the co-simulation process.
+% This section will outline 
+% the advantages and disadvantages of undertaking this process with respect to factors such as 
+% usability for various applications, simulation speed and resources, and an overview of the tools 
+% involved in the process.
 
-Advantages of a co-simulation process between EnergyPlus and CitySim were uncovered through
-this study. The key advantage is that each of the engines is enabled to account for various 
+% Advantages of a co-simulation process between EnergyPlus and CitySim were uncovered through
+% this study.
+
+One of the key insights in this work is that each of the engines is enabled to account for the various 
 physical phenomenon in their simulation process that were previously impossible. For example, 
-through co-simulation, EnergyPlus was able to utilize the long wave radiation exchange capabilities 
-of CitySim. \noteCM{Here we continue the discussion of advantages}
+through co-simulation, EnergyPlus was able to utilize the long-wave radiation exchange capabilities 
+of CitySim. The ability to couple and leverage the best aspects of multiple simulation
+engines can enhance the modeling of large-scale urban agglomerations. 
+% This paper has outlined two such scenarios in which the building-focused EnergyPlus
+% simulation engine is coupled and co-simulated with the urban-scale CitySim
+% engine.
 
@@
 in computing time and power needed for the FMI to coordinate data exchange between 
-the two simulation engines. \noteCM{Here we continue the discussion of disadvantages}
+the two simulation engines. After calibration, a comparison of the run-times of the co-simulation and solo EnergyPlus
+simulations show that the execution time for the solo EnergyPlus simulation was 1 minute and 49 seconds compared to 28 minutes and 10 seconds for the co-simulation.
 
 \section{Conclusion}
-The ability to couple and leverage the best aspects of multiple simulation
-engines can enhance the modeling of large scale urban agglomerations. This
-paper has outlined two such scenarios in which the building-focused EnergyPlus
-simulation engine is coupled and co-simulated with the urban-scale CitySim
-engine. This process is implemented through a fully automated work flow
+This paper outlines the implementation of a fully automated workflow
 process that extracts geometry information at the
@@
 with information exchange at each time step of targeted variables, and
-accumulates the results of analysis. The process has been implemented on
-simplified theoretical scenarios in the past and the key innovation with this
+accumulates the results of the analysis. The process has been implemented on
+simplified theoretical scenarios in the past, and the key innovation with this
 work is in implementation on actual case study campuses and targeted
@@
 simulation and solo environments are within range of previous theoretical
-models. The results show that there is a noticeable impact 
-More reliable results of the magnitude of differences between the
+models. More reliable results of the magnitude of differences between the
 simulation techniques can be extracted from these real-world scenarios.
@@
 more intensively utilize the model results in a practical implementation of
-retrofit scenarios or urban-scale energy systems research.
+retrofit scenarios or urban-scale energy systems research. More implementations would 
+also test the feasibility of using co-simulation for retrofit analysis, urban planning studies, and
+cooling and heating system optimization.
 

### 2017-06-13 latex_corrected_anonymous/UMEM_CoSim.tex
finished paper and resubmitted!

--- 2017-06-13 latex_corrected/UMEM_CoSim.tex
@@
 
-\author{Clayton Miller\textsuperscript{a,b}%
-$^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
-Daren Thomas\textsuperscript{b},
-J\'er\^ome K\"ampf\textsuperscript{c},
-and Arno Schlueter\textsuperscript{b}\\
-\vspace{6pt}
-\textsuperscript{a}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
-\textsuperscript{b}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
-\textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
-}
+% \author{Clayton Miller\textsuperscript{a,b}%
+% $^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
+% Daren Thomas\textsuperscript{b},
+% J\'er\^ome K\"ampf\textsuperscript{c},
+% and Arno Schlueter\textsuperscript{b}\\
+% \vspace{6pt}
+% \textsuperscript{a}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
+% \textsuperscript{b}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
+% \textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
+% }
 

### 2017-07-07 latex_secondsubmission_reviewcomments/ReviewCommentsResponse.tex
Made second revision changes

\documentclass[answers,12pt]{exam}
\usepackage{xcolor}
\definecolor{SolutionColor}{rgb}{0.1,0.3,1}
\usepackage{lipsum}

\renewcommand{\thequestion}{\alph{question} }
\renewcommand\questionlabel{\llap{\thequestion)}}

%\pointsinrightmargin
%\boxedpoints
\unframedsolutions
\shadedsolutions
\definecolor{SolutionColor}{rgb}{0.9,0.9,1}
\renewcommand{\solutiontitle}{}

\usepackage{titling}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

% \setlength{\droptitle}{-10em}   % This is your set screw

\title{Review Comment Responses to Journal of Building Performance Simulation Second Submission}
\subtitle{Paper Title: Urban and building multiscale co-simulation: case study implementations on two university campuses 
}
% \email{clayton@nus.edu.sg}
% \author{Clayton Miller, Daren Thomas, J\'er\^ome K\"ampf, Arno Schlueter}

% \subtitle{ETH Z\"urich, Institute of Technology in Architecture (ITA), Architecture and Sustainable Building Technologies (SuAT)}
% \subtitle{*Corresponding author: Phone: +1-402-403-0090, miller.clayton@arch.ethz.ch}

\begin{document}

\maketitle

\section{Review Comments}
\begin{questions}

\question p. 13, line 69. “we week to co-simulate” is incorrect. Please consider “we co-simulate.”
\begin{solution}
Fixed -- thanks for catching that!
\end{solution}

\question  p. 12, lines 90-93. The correction the authors made in response to a reviewer comment
needs further modification. My comment was “Please note that Bueno et al. 2013 generated urban weather with a nodal model and did not directly couple EnergyPlus to a nodal representation of the urban canopy layer. The accuracy of this approach depends on how faithfully users and the model represent the buildings that will later be simulated in detail in EnergyPlus with the modified weather file.” This applies to Bueno et al. 2013 and NOT Bueno et al. 2011, in which TEB and EnergyPlus are coupled. In short, one of Bueno’s papers employed coupling and the other did not; the authors should distinguish them or refer to the single method of their choice.
\begin{solution}
Very good point - apologies for misunderstanding that point. The Bueno 2013 paper has been removed as it does not utilize coupling.
\end{solution}

\question p. 14, line 149. Please delete the redundant “per hour” after “timesteps.”
\begin{solution}
Fixed.
\end{solution}

\question P. 15, lines 176-177. In two places, the “l” in “long-wave” should be capitalized. 
\begin{solution}
Good catch - good example of why "find and replace" needs to be performed before final proofreading.
\end{solution}

\question P. 16, line 189. Please hyphenate “urban scale.”
\begin{solution}
This instance has been hyphenated as well as several others in the manuscript
\end{solution}

\question p. 17, line 217. Please replace “simulation results of the co-simulation” with “results of
the co-simulation.”
\begin{solution}
Fixed.
\end{solution}

\question p. 18, line 221. Please replace “actualized” with “actual.” In line 224, please replace
“measured and simulated” with “measurement and simulation.”
\begin{solution}
Fixed.
\end{solution}

\question p. 20, line 283. Please replace “co- simulation” with “co-simulation” by removing the
extraneous space after the hyphen.
\begin{solution}
Fixed.
\end{solution}

\question p. 21, Figures 10 and 11. The authors have usefully improved these figures. Is it
necessary to retain the absolute change in energy consumption, to four significant figures, as well as the percentage change? This reviewer suggests that the absolute change be removed because it suggests more precision that the process merits and because the percentages are more meaningful.
\begin{solution}
We agree with this and have changed to figures to only represent the percentage change.
\end{solution}

\question p. 21, section 3.5. The new reference to the Minergie standard should be placed after “Minergie building” or at the end of that sentence, and not at the end of the paragraph.
\begin{solution}
Fixed.
\end{solution}

\question p. 19, line 260. Online sources use “plug load” rather than plug-load.” Either is better than “plug- load” (with both a hyphen and a space), as used in the text.
\begin{solution}
Fixed.
\end{solution}

\question  p. 24, lines 348-353. The new discussion section includes two redundancies. In the first sentence, please consider deleting “on two real-world case studies,” given the reference to case studies at the beginning of the sentence. The third sentence could be ended with “...unique to this case study....”
\begin{solution}
The first redundancy was fixed. For the second one, we removed "in this particular instance", but kept the "unique to this case study" were it is
\end{solution}

\question  p. 25, lines 368-375. In line 372, please hyphenate “case-study” (when used as a modifier for campuses). In line 373, please remove the space after the hyphen in “co- simulation.”
\begin{solution}
Fixed
\end{solution}

\question   p. 25, lines 376-379. The text identifies “practical implementation of retrofit scenarios” and “retrofit analysis” as future applications. How do these applications differ?
\begin{solution}
We removed the second reference to retrofits and, instead, changed it to refer to general "systems analysis"
\end{solution}

\question   p. 26, line 416. Only the K in KAEMPF should be capitalized.
\begin{solution}
Fixed.
\end{solution}

\end{questions}
\end{document}

### 2017-07-07 latex_thirdsubmission_compared/UMEM_CoSim_original.tex
Made second revision changes

--- 2017-06-13 latex_corrected_anonymous/UMEM_CoSim.tex
@@
 
-\subsection{Acknowledgments}
-The authors would like to acknowledge the ETH Z\"urich Campus Facilities
-Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
-Thoma for their assistance in this project. This research was funded by the
-Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
-Energy Modeling (UMEM) project. 
+% \subsection{Acknowledgments}
+% The authors would like to acknowledge the ETH Z\"urich Campus Facilities
+% Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
+% Thoma for their assistance in this project. This research was funded by the
+% Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
+% Energy Modeling (UMEM) project. 
 % The authors would also like to acknowledge

### 2017-07-07 latex_thirdsubmission_corrected/UMEM_CoSim.tex
Made second revision changes

--- 2017-06-13 latex_corrected/UMEM_CoSim.tex
@@
 $^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
-Daren Thomas\textsuperscript{b},
+Daren Thomas\textsuperscript{a},
 J\'er\^ome K\"ampf\textsuperscript{c},
-and Arno Schlueter\textsuperscript{b}\\
+and Arno Schlueter\textsuperscript{a}\\
 \vspace{6pt}
-\textsuperscript{a}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
-\textsuperscript{b}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
+\textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
+\textsuperscript{b}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
 \textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
@@
 The co-simulation of both urban and building-level models leverages the advantages of both platforms. 
-It better accounts for the localized effects of surrounding buildings, geography and climate conditions while maintaining high-fidelity building systems representation.
-This paper describes the co-simulation process of the building and urban scale models of two university campuses in Switzerland using EnergyPlus and CitySim.
+It better accounts for the localized effects of surrounding buildings, geography and climate conditions 
+while maintaining high-fidelity building systems representation. This paper describes the co-simulation process 
+of the building and urban-scale models of two university campuses in Switzerland using EnergyPlus and CitySim. 
 In the first case study, on-site measured performance data is compared to the co-simulation results. 
-The second case study examines the results of the two engines.
-The results show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on heating use as compared to solo simulations.The co-simulation process was able to better model realistic conditions for heating, but not cooling in one case study.
-It was able to substantially reduce the discrepancies in prediction between the engines in the other study.
-
-    % The co-simulation of both urban and building-level models provides the means to model 
-    % collections of buildings in ways that leverage the advantages of both platforms. It accounts better 
-    % for the localized effects of surrounding buildings, geography and climate conditions 
-    % while maintaining a high-fidelity building systems representation.
-    % This paper describes the co-simulation process of the building and urban
-    % scale models of two campuses of higher education buildings in Switzerland.
-    % The campuses are modeled at both the building level, using the EnergyPlus
-    % simulation engine, and at the urban scale using the CitySim engine. A co-
-    % simulation framework is used to execute simulations from both engines
-    % concurrently with an exchange of information to leverage the various
-    % strengths of each. In the first case study, on-site weather and measured
-    % performance data are then compared to the output from two modeling
-    % scenarios: building-scale simulation using EnergyPlus and co-simulation of
-    % the engines.  The co-simulation process was able to better model realistic conditions for heating, but not cooling in one case study and was able to 
-    % highly reduce the discrepancies in prediction between the engines in the other study.
-     % Challenges encountered with the urban scale
-    % calibration and the strengths and weaknesses of the developed process are
-    % discussed.
-    % A partial calibration process is implemented to reconcile the
-    % simulations with the measured data of a targeted office building on
-    % campus. In the second case study, the co-simulation results are compared
-    % to the CitySim simulation engine.
-
-    % A co-simulation framework is used to execute simulations from both engines concurrently with an exchange of information to leverage the various strengths of each.
-
-    % The results show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and
-    % -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on
-    % heating consumption as compared to solo simulations of each of the engines.
+The second case study examines the results of the two engines. The results show that coupling of EnergyPlus with 
+CitySim resulted in a -15.5\% and -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on heating 
+use as compared to solo simulations.The co-simulation process was able to better model realistic conditions for 
+heating, but not cooling in one case study. It was able to substantially reduce the discrepancies in prediction between the engines in the other study.
 \end{abstract}
@@
 
-Urban scale building performance simulation is a process that empowers the
+Urban-scale building performance simulation is a process that empowers the
 analysis and optimization of cities. Urban populations are growing around the
@@
 \citep{united_nations_world_2014}. Expansions of entire districts and even cities
-is not an uncommon phenomenon, especially in East Asia and Africa. Urban scale
+is not an uncommon phenomenon, especially in East Asia and Africa. Urban-scale
 modeling is in the midst of an intense focus on the research community with
@@
 Building performance simulation is a mature domain of research relative to
-urban scale efforts. The use of whole building simulation engines originated
+urban-scale efforts. The use of whole building simulation engines originated
 in the 1960's with the US government's development of the BLAST and DOE-2
@@
 results in certain deficiencies concerning modeling various phenomena.
-For example, urban scale simulation highly simplifies the building systems and
+For example, urban-scale simulation highly simplifies the building systems and
 internal load models, thus making a retrofit analysis at the systems level
@@
 The current
-effort seeks to couple building and urban scale simulation to address the deficiencies of the individual engines. The research in
+effort seeks to couple building and urban-scale simulation to address the deficiencies 
+of the individual engines. The research in
 this paper is part of a larger coupling effort in which various engines are
 connected and co-simulated to create a more comprehensive analysis of the
-urban scale \citep{dorer_modelling_2013,allegrini_influence_2012}. The target is the
+urban-scale \citep{dorer_modelling_2013,allegrini_influence_2012}. The target is the
 computational interface between the building energy model, using EnergyPlus,
@@
 Building Information Model (BIM) for the creation of both building and
-urban-scale performance models for a real-world campus of buildings. Next, we week to 
-co-simulate the urban and building scale models through concurrent information exchange.
+urban-scale performance models for a real-world campus of buildings. Next, we co-simulate 
+the urban and building scale models through concurrent information exchange.
 Finally, we implement a simplified calibration procedure for the first scenario by 
@@
 through a modified weather file to quantify the influences of urban localized weather effects
-on whole building simulation \citep{bueno_combining_2011} and urban weather generation
-\citep{bueno_urban_2013}.
+on whole building simulation \citep{bueno_combining_2011}.
 
@@
 
-The number of timesteps per hour for both CitySim and EnergyPlus is set to one per hour. 
+The number of timesteps for both CitySim and EnergyPlus is set to one per hour. 
 The frequency of data exchanges is set to once per timestep. No data averaging over time 
@@
  \hline
-Zone & Occupation & Fraction of the maximum occupation\\&& (0.0-1.0) overrides the EnergyPlus occupation schedule\\&&  with the CitySim stochastic schedule. \\
+Zone & Occupation & Fraction of the maximum occupation\\&& (0.0-1.0) overrides the EnergyPlus 
+occupation schedule\\&&  with the CitySim stochastic schedule. \\
 \botrule
@@
 
-\subsection{long-wave radiation exchange}
+\subsection{Long-wave radiation exchange}
 \label{lwradiation}
-long-wave radiation exchange in the urban scale environment is coupled in the
+Long-wave radiation exchange in the urban-scale environment is coupled in the
 co-simulation process. It requires the development of a set of
@@
 and to account for differences in the methods by which each engine calculates
-this value. A detailed description of long-wave Radiation (LWR) variable
+this value. A detailed description of Long-wave Radiation (LWR) variable
 exchange and approximation is found in a previously published study
@@
   \includegraphics[width=1.0\textwidth]{figures/LWRCalc_Combined_V3}
-  \caption{Comparison of the LWR components between a) Solo EnergyPlus and b) Coupled CitySim/EnergyPlus configuration \citep{miller_long_2015}
+  \caption{Comparison of the LWR components between a) Solo EnergyPlus and b) Coupled 
+  CitySim/EnergyPlus configuration \citep{miller_long_2015}
   \label{combinedLWR}}
@@
 \subsection{Simplified calibration}
-In the first case study, one aspect of this analysis is the comparison of the actual measured performance of the target building on campus with the
-simulation results of the co-simulation. A simplified calibration procedure is
+In the first case study, one aspect of this analysis is the comparison of the actual 
+measured performance of the target building on campus with the 
+results of the co-simulation. A simplified calibration procedure is
 adapted from previous research to compare the measured heating and cooling
@@
 performance reconciliation of 18 buildings that were built according to the
-LEED Canada protocol and were under review of actualized performance. This
+LEED Canada protocol and were under review of actual performance. This
 protocol is unique in its analysis process to uncover design model
 deficiencies in a step-wise manner, utilizing the most readily available
-knowledge first and working towards equilibrium between measured and
-simulated. There is an appropriate balance between the effort of implementation and value
+knowledge first and working towards equilibrium between measurement and
+simulation. There is an appropriate balance between the effort of implementation and value
 generated through the calibration process.
-
-% The following steps are the general procedure applied to the targeted buildings:
-
-% \begin{enumerate}
-%   \item Using the local weather conditions for the simulation period
-%   \item Update simulation based on custom lighting schedules and power densities extracted from the measured data
-%   \item Update simulation based on custom plug load schedules and power densities extracted from the measured data
-%   \item Account for \emph{unregulated} building loads such as experimental equipment and process loads
-% \end{enumerate}
 
@@
  cafeterias, data centers and other types of similar areas. The campus has a
- centralized energy management system (EMS) that contains 807 energy and water measurement points from heating, cooling, electricity, city gas, domestic hot water, gray water, and general water consumption.
+ centralized energy management system (EMS) that contains 807 energy and water measurement 
+ points from heating, cooling, electricity, city gas, domestic hot water, gray water, and general water consumption.
 
@@
 the simplified calibration procedures. The measured datasets were screened and
-aggregated into typical usage profiles to be used for the lighting, plug-
-loads, and HVAC equipment availability schedules and power densities. Figure
+aggregated into typical usage profiles to be used for the lighting, plug loads, and HVAC equipment availability schedules and power densities. Figure
 \ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical
@@
 and 29.4\% for heating. These metrics fall within the +/-10\% NMBE and +/-30\%
-CVRSME used in this case study for calibration. A total of 37 calibration iterations were undertaken to modulate the simulation results to within these criteria. The
+CVRSME used in this case study for calibration. A total of 37 calibration iterations were undertaken 
+to modulate the simulation results to within these criteria. The
 goal of calibration, in this case, is to just bring the models to within a
@@
 \subsection{EnergyPlus co-simulation results}
-For cooling, a discrepancy can be seen between co-
-simulation and solo EnergyPlus. Co-simulation decreases the predicted cooling energy by 15.5\%, as seen in Figure
+For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus. 
+Co-simulation decreases the predicted cooling energy by 15.5\%, as seen in Figure
 \ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
@@
 
-% These performance differences due to co-simulation are compared to a
-% theoretical single-zone case study in which there was a 15-30\% increase in
-% heating energy and a 4-11\% decrease in cooling energy \citep{Miller:2015vk}.
-% The results from this case study are less extreme on the heating side and more
-% on the cooling side than the theoretical case study.
-
 When comparing the solo and co-simulated models to the measured data, it is noticed that 
-cooling energy is over-predicted by the solo simulation by 4\%, while co-simulation under-predicted 
-by 11.1\%. This discrepancy is likely due to a loss in long-wave radiation in the co-simulation to the surrounding buildings, thus reducing the overall 
+cooling energy is over-predicted by the solo simulation by 4\%, while 
+co-simulation under-predicted 
+by 11.1\%. This discrepancy is likely due to a loss in long-wave 
+radiation in the co-simulation to the surrounding buildings, thus reducing the overall 
 cooling load.
@@
 For heating energy, co-simulation was able to bring the predicted value to within 2\% of 
-the measured value for the year, an improvement as compared to the solo simulation, which was 8.5\% less than the measured value. This situation is also 
-likely due to the long-wave radiation loss to surrounding buildings, thus increasing the overall heating load.
+the measured value for the year, an improvement as compared to the solo simulation, 
+which was 8.5\% less than the measured value. This situation is also 
+likely due to the long-wave radiation loss to surrounding buildings, 
+thus increasing the overall heating load.
 
@@
 hotel. As a public space, this ensemble is organized around the central plaza as
-seen in Figure \ref{fig:quartier_nord_1}). With a particularly strong visual and formal identity, the SwissTech
+seen in Figure \ref{fig:quartier_nord_1}). With a particularly 
+strong visual and formal identity, the SwissTech
 Convention Centre (STCC) is clearly the key protagonist.  Designed as a
 Minergie building, it includes modern energy conversion
-technologies to reduce its energy consumption. The focus of the co-simulation
+technologies to reduce its energy consumption \citep{beyeler_minergie:_2009}. The focus of the co-simulation
 is realized on the STCC, simulated with the nearby buildings for housing,
-retail and service areas \citep{beyeler_minergie:_2009}.
+retail and service areas.
 
@@
 The corresponding CitySim model was created by exporting a DXF file from
-EnergyPlus for the whole of Quartier Nord, and importing it into the Graphical User Interface of CitySim.
+EnergyPlus for the whole of Quartier Nord, and importing 
+it into the Graphical User Interface of CitySim.
 Physical characteristics of the building were added to complete the CitySim
@@
 
-% \subsection{CitySim co-simulation results}
-
-% When focusing solely on CitySim, a 26.9\% decrease in heating energy is
-% observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}. A 49.1\%
-% decrease in heating energy is observed, as seen in Figure
-% \ref{fig:qn_citysim_cosimvssolo_heating}. These results align with the
-% previous comparison of EnergyPlus and CitySim engines. The substantial
-% differences between solo and co-simulation in these cases is a result of
-% EnergyPlus transferring the heating and cooling load values at each time step. \noteCM{Jerome -- I need some help
-% interpreting these results -- you mentioned that there is an expected delta
-% between citysim and energyplus in previous studies. Can you help elaborate on
-% that?}
-
-% \begin{figure}[H]
-% \centering
-% \includegraphics[scale=0.55]{figures/QN_CitySim_Cooling}
-% \caption{Quartier Nord CitySim Co-Simulation vs. Solo for Cooling}
-% \label{fig:qn_citysim_cosimvssolo_cooling}
-% \end{figure}
-
-% \begin{figure}[H]
-% \centering
-% \includegraphics[scale=0.55]{figures/QN_CitySim_Heating}
-% \caption{Quartier Nord CitySim Co-Simulation vs. Solo for Heating}
-% \label{fig:qn_citysim_cosimvssolo_heating}
-% \end{figure}
-
 \section{Discussion}
 Two campus case studies were presented in this paper to showcase a unique process of extracting model meta-data, conversion of those data into input files for two separate simulation engines, and the solo
-and co-simulation process of those engines on two real-world case studies.
-The analysis of the results shows that for the first case study, co-simulation can achieve values closer to measured reality for heating, but not cooling.
-These results are unique to this case study and simply show that the co-simulation process may be helpful for heating only
-in this particular instance. A limitation of this study is that we only analyze a single building against measured data in this
+and co-simulation process of those engines. The analysis of the results shows that for the first case study, co-simulation can achieve values closer to measured reality for heating, but not cooling. 
+These results are unique to this case study and simply show that the co-simulation process may be helpful for heating only.
+A limitation of this study is that we only analyze a single building against measured data in this
 context. In the second case study, significant discrepancies are found between the CitySim and EnergyPlus engines which were corrected using the co-simulation process.
-% This section will outline 
-% the advantages and disadvantages of undertaking this process with respect to factors such as 
-% usability for various applications, simulation speed and resources, and an overview of the tools 
-% involved in the process.
-
-% Advantages of a co-simulation process between EnergyPlus and CitySim were uncovered through
-% this study.
 
@@
 engines can enhance the modeling of large-scale urban agglomerations.
-% This paper has outlined two such scenarios in which the building-focused EnergyPlus
-% simulation engine is coupled and co-simulated with the urban-scale CitySim
-% engine.
 
@@
 \section{Conclusion}
-This paper outlines the implementation of a fully automated workflow
+This paper outlines the implementation of a fully automated work flow
 process that extracts geometry information at the
@@
 simplified theoretical scenarios in the past, and the key innovation with this
-work is in implementation on actual case study campuses and targeted
-buildings. The results illustrate that the differences between the co-
-simulation and solo environments are within range of previous theoretical
+work is in implementation on actual case-study campuses and targeted
+buildings. The results illustrate that the differences between the co-simulation 
+and solo environments are within range of previous theoretical
 models. More reliable results of the magnitude of differences between the
@@
 retrofit scenarios or urban-scale energy systems research. More implementations would 
-also test the feasibility of using co-simulation for retrofit analysis, urban planning studies, and
+also test the feasibility of using co-simulation for systems analysis, urban planning studies, and
 cooling and heating system optimization.
@@
 Energy Modeling (UMEM) project.
-% The authors would also like to acknowledge
- % Emanuel Thoma for his work in developing the geometric models.% %
- % \noteDT{We also
-% want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}
 

### 2017-07-07 thirdsubmission/6_ThirdSubmission_SourceFile.tex
Made second revision changes

--- 2017-07-07 latex_thirdsubmission_corrected/UMEM_CoSim.tex
@@
 
-\author{Clayton Miller\textsuperscript{a,b}%
-$^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
-Daren Thomas\textsuperscript{a},
-J\'er\^ome K\"ampf\textsuperscript{c},
-and Arno Schlueter\textsuperscript{a}\\
-\vspace{6pt}
-\textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
-\textsuperscript{b}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
-\textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
-}
+% \author{Clayton Miller\textsuperscript{a,b}%
+% $^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
+% Daren Thomas\textsuperscript{a},
+% J\'er\^ome K\"ampf\textsuperscript{c},
+% and Arno Schlueter\textsuperscript{a}\\
+% \vspace{6pt}
+% \textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
+% \textsuperscript{b}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
+% \textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
+% }
 
@@
 
-\subsection{Acknowledgments}
-The authors would like to acknowledge the ETH Z\"urich Campus Facilities
-Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
-Thoma for their assistance in this project. This research was funded by the
-Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
-Energy Modeling (UMEM) project.
+% \subsection{Acknowledgments}
+% The authors would like to acknowledge the ETH Z\"urich Campus Facilities
+% Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
+% Thoma for their assistance in this project. This research was funded by the
+% Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
+% Energy Modeling (UMEM) project.
 

### 2017-07-20 zfinalsubmission/FinalDraft-UMEM_CoSim.tex
final touches to paper

--- 2017-07-07 latex_thirdsubmission_corrected/UMEM_CoSim.tex
@@
 \end{keywords}
-
-\linenumbers
 
@@
 has compared the results of a building and urban-scale co-simulation procedure
-to measured data from a real-world campus.% \noteDT{:)}
+to measured data from a real-world campus.
 
@@
 of neighborhoods and university campuses was published that includes
-strategic aspects of coupling different %\noteDT{did you mean: "strategic"?}b
+strategic aspects of coupling different 
 types of models \citep{srebric_building_2015}. EnergyPlus has been coupled with ENVI-
